### 2013-04-17 paper1.tex
first commit

\documentclass[useAMS,usenatbib]{mn2e}                                  
%
%\def\del#1{{\bf  [deleted text] }} \def\new#1{{\bf #1}} \def\remark#1{{\bf  [remark: #1]}}
%\def\del#1{} \def\new#1{#1} \def\remark#1{}

\def\del#1{{}}
%\def\del#1{{\bf (DELETED TEXT)}}
\def\C#1{{\bf #1}}
%\def\C#1{#1}

%\newcommand{\rmn}{\mathrm}
\newcommand{\CR}{\mathrm{CR}}
\newcommand{\expval}[1]{\left\langle #1 \right\rangle}
\newcommand{\RA}[3]{#1$^{\mathrm{h}}$#2$^{\mathrm{m}}$#3$^{\mathrm{s}}$}
\newcommand{\Dec}[3]{#1$^{\circ}$#2\arcmin#3\arcsec}
\newcommand{\dps}{\displaystyle}
\newcommand{\eps}{\varepsilon}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\vel}{\upsilon}
%
\usepackage{graphicx}
\usepackage{natbib}
%
\usepackage{txfonts}

\voffset-0.5in

%MNRAS
\title[A Phenomenological Model for the Intra-Cluster Medium]{A Phenomenological Model for the Intra-Cluster Medium that matches X-ray and Sunyaev-Zel'dovich observations}
\author[F. Zandanel, C. Pfrommer and F. Prada]{
Fabio Zandanel$^{1,2 *}$, Christoph Pfrommer$^{3 \dagger}$ and Francisco Prada$^{4,5,1 \S}$\\
$^{1}$Instituto de Astrof\'{\i}sica de Andaluc\'{\i}a (CSIC), Glorieta de la Astronom\'{\i}a, E-18080 Granada, Spain\\
$^{2}$now at GRAPPA Institute, University of Amsterdam, Science Park 904, 1098XH Amsterdam, Netherlands\\
$^{3}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany\\
$^{4}$Campus of International Excellence UAM+CSIC, Cantoblanco, E-28049 Madrid, Spain\\
$^{5}$Instituto de F\'{\i}sica Te\'orica, (UAM/CSIC), Universidad Aut\'onoma de Madrid, Cantoblanco, E-28049 Madrid, Spain}
\begin{document}

\date{Accepted XXX. Received XXX; in original from XXX}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2012}

\maketitle

\label{firstpage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  ...
  We build a mock galaxy cluster catalog from the large MultiDark $N$-body $\Lambda$CDM 
  simulation by adopting a phenomenological gas density model for each cluster based on X-ray
  measurements that matches Sunyaev-Zel'dovich and X-ray scaling relations and
  luminosity function. 
  ...
  We make our cosmologically complete multi-frequency mock catalogs for 
  the (non-)thermal cluster emission at different redshifts publicly and freely available on-line
  through the MultiDark database.
\end{abstract}

\begin{keywords}
  Galaxies: clusters: intracluster medium - X-rays: galaxies: clusters - astronomical data bases: catalogues
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:1}

\begingroup
\let\thefootnote\relax\footnotetext{* f.zandanel@uva.nl}
\let\thefootnote\relax\footnotetext{$\dagger$ christoph.pfrommer@h-its.org}
\let\thefootnote\relax\footnotetext{$\S$ fprada@iaa.es}
\endgroup

{\bf Introduction...}

%
%dark matter (DM)  
%

{\bf Our original motivation to build such a mock catalog is to predict the 
non-thermal emission at radio and gamma-ray frequencies of a cosmological 
complete sample of galaxy clusters. This is presented in a companion 
paper (REF, hereafter Paper~2).
The two basic ingredients of the two works are an $N$-body, \emph{DM-only}
cosmological simulation that we use in constructing our complete cluster sample,
and the (non-)thermal emission model. Here, we use the MultiDark simulation that
will be described in Section~\ref{sec:2}, along with our final cluster sample. As described 
in Paper~2, for any given cluster, the necessary ingredients for the non-thermal emission 
model are mass, temperature, and gas density distribution. We assign to
each cluster in that simulation a gas density profile that is phenomenologically
constructed from state-of-art X-ray observations, as will be shown in
Section~\ref{sec:3}. In Section~4 and 5, we will show that this approach can successfully
reproduce the known X-ray cluster characteristics, such as the X-ray luminosity
function (XLF), the luminosity-mass relation, $L_{\rmn{X}}- M$, and the
$Y_{\rmn{X}}-M$ relation, where $Y_{\rmn{X}}=M_\rmn{gas}k_{\rmn{B}}T$ with an
X-ray-derived gas mass $M_{\rmn{gas}}$ and temperature $T$
\citep{2006ApJ...650..128K}. Moreover, we compare our $Y_{\rmn{SZ}}-M$ relation
with SZ-derived measurements. Only if our model matches available cluster data
on the gas properties, we can safely use it in Paper~2.} In this work, the cluster mass $M_{\Delta}$ 
and radius $R_{\Delta}$ are defined with respect to a density that is $\Delta=200$ or 
$\Delta=500$ times the \emph{critical} density of the Universe. We adopt density 
parameters of $\Omega_{\rmn{m}}=0.3$, $\Omega_{\Lambda}=0.7$ and today's 
Hubble constant of $H_0 = 100 \times h_{70}$~km~s$^{-1}$~Mpc$^{-1}$ where $h_{70} = 0.7$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{MultiDark simulation and final cluster sample}
\label{sec:2}
The MultiDark simulation used in this work is described in detail in \cite{2011arXiv1104.5130P}.  
It is an $N$-body cosmological simulation done with
the Adaptive-Refinement-Tree (ART) code \citep{1997ApJS..111...73K} of
$2048^3$ particles within a ($1000$~Mpc~$h^{-1}$)$^3$ cube. The latest WMAP5 and
WMAP7 cosmological parameters were used. This simulation is particularly well
suited for our purpose because of its large number of clusters.

We use the MultiDark halo catalog from its on-line database,\footnote{www.multidark.org.} 
constructed with the Bound Density Maxima algorithm \citep{1997astro.ph.12217K}.  
We will mainly use $M_{500}$ and $R_{500}$ for comparison with existing observational works.  
We use the technique described in \cite{2003ApJ...584..702H} to convert $M_{200}$ and
$R_{200}$ provided by the MultiDark halo catalog to $M_{500}$ and $R_{500}$.  In
creating our cluster sample we only select distinct halos, i.e., those halos that
are not sub-halos of any other halo, which by definition are not galaxy clusters.

Additionally, we assume that the main emission mechanism in the ICM is thermal
bremsstrahlung, which is true only above a particle energy of approximately
$2.6$~keV \citep{1988xrec.book.....S}. Below this
energy, there could be other important contributions to the emission,
e.g., from atomic lines. Therefore, we impose a mass cut of
$M_{200}\geq1\times10^{14}$~$h^{-1}$~M$_{\odot}\approx1.4\times10^{14}$~$h_{70}^{-1}$~M$_{\odot}$
which ensures $k_{\rmn{B}}T \gtrsim 2.6$~keV, assuming the $M_{500} - T_{\rmn{ci}}$ relation
of \cite{2010MNRAS.406.1773M}.

{\bf In Paper~2, we present predictions for the LOFAR radio observatory\footnote{www.lofar.org} 
which is expected to detect diffuse radio emission in clusters up to redshift $z \approx 1$ (e.g.,
\citealp{2010A&A...509A..68C,2012JApA..tmp...34R}).} 
Thus, we make use of different simulation snapshots up to $z=1$. 
{\bf The extrapolation of our model beyond this redshift is rather uncertain as it is based
on observations at low(er) redshift.}
In Table~\ref{tab:z}, we show the total cluster number in our final cluster sample at different redshifts.

\begin{table} 
\begin{center}
\caption{Number of halos in the final cluster sample}
\medskip
\begin{tabular}{cc}
\hline
\phantom{\Big|}
redshift $z$ & number of halos \\
\hline\\[-0.5em]
 0.0~~ &  13763\\
 0.1~~ &  12398\\
 0.2~~ &  10783\\ 
 0.4~~ &   ~~7789\\ 
 0.61  &  ~~5187\\ 
 0.78  &  ~~3372\\ 
 1.0~~ &  ~~1803\\[0.5em]
\hline
\end{tabular}
\label{tab:z}
\end{center}
\footnotesize{Note. We show the number of halos in our MultiDark snapshots at redshift $z$ for $M_{200}\geq1\times10^{14}$~$h^{-1}$~M$_{\odot}\approx1.4\times10^{14}$~$h_{70}^{-1}$~M$_{\odot}$. }
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Gas density modeling}
\label{sec:3}

We decided to use a \emph{phenomenological} approach and to construct the gas
density profiles directly from X-ray observations. A suitable X-ray sample that
provides the needed information is the \emph{Representative XMM-Newton Cluster
  Structure Survey} (REXCESS) sample \citep{2008A&A...487..431C,
  2009A&A...498..361P}. It is a sample of 31 galaxy clusters of different
dynamical states at redshifts $0.06<z<0.18$ with detailed information on the
de-projected electron density profiles \citep{2008A&A...487..431C}. In
Fig.~\ref{fig:gas_profiles}, we show the 31 electron density profiles of the
REXCESS sample color-coded by CCCs and NCCCs.

In order to obtain an electron density profile that we will attach to our
simulated clusters, we use a generalized Navarro-Frank-White (GNFW) profile,
\begin{equation}
n_{\rmn{e}}(x) = \frac{n_{0}}{x^{\beta}\left[1+x^{\alpha}\right]^{\frac{\delta-\beta}{\alpha}}},
\label{eq:gnfw}
\end{equation}
where $x=R/R_{\rmn{c}}$ and $R_{\rmn{c}}$ is the cluster core radius. To reduce
the dimensionality of our fit, we fix representative values of $R_{\rmn{c}} =
0.2\, R_{500}$, $\alpha = 1$ and $\delta = 2.5$. We fit the radial density
profiles of the REXCESS sample in log-log space, separating them in the two
categories of NCCCs and CCCs as shown in Fig.~\ref{fig:gas_profiles}.  We
obtain $n_{\rmn{0,NCCC}} = 1.02\times10^{-2}$~$h_{70}^{1/2}$~cm$^{-3}$,
$n_{\rmn{0,CCC}} = 8.32\times10^{-3}$~$h_{70}^{1/2}$~cm$^{-3}$,
$\beta_{\rmn{NCCC}} = -0.093$, and $\beta_{\rmn{CCC}} = 0.592$. The resulting
fits are shown in blue and red for the NCCC and CCC population, respectively.

The next step is to introduce a mass-scaling in order to apply our GNFW profiles
to all our clusters. We adopt the gas mass fraction-mass scaling,
$f_{\rmn{gas},500}-M_{500}$ of \cite{2009ApJ...693.1142S} (and adopt their equation~(8)). We can
express $f_{\rmn{gas},500}$ in the following way:
\begin{equation}
f_{\rmn{gas},500} = \frac{M_{\rmn{gas},500}}{M_{500}}  = \frac{\int_{0}^{R_{500}} \rho_{\rmn{gas}} \rmn{d}V}{M_{500}}
\label{eq:m500}
\end{equation}
with $\rho_{\rmn{gas}}(R) = \rho_{\rmn{gas}} = n_{\rmn{e}} m_{\rmn{p}} / ( X_{\rmn{H}}X_{\rmn{e}} )$ where
$m_{\rmn{p}}$ is the proton mass, $X_{\rmn{H}} = 0.76$ is the primordial hydrogen
mass fraction and $X_{\rmn{e}} = 1.157$ the ratio of electron-to-hydrogen number
densities in the fully ionized ICM \citep{1988xrec.book.....S}. For each cluster
$i$ of our sample, we then define a \emph{mass-scaled} gas profile as
$\rho_{\rmn{gas},i}=C_{i} \,\rho_{\rmn{gas}}$ with:
\begin{eqnarray}
%C_{i}  =  (0.0616\pm(0.0060g_{1}))  h_{73}^{-1.5}  \left(\frac{M_{500,i}}{10^{13} h_{73}^{-1} \rmn{M_{\odot}}}\right)^{0.135\pm(0.030g_{2})} \nonumber \\
C_{i}  & = &  (0.0656\pm(0.0064g_{1})) \, h_{70}^{-1.5}  \nonumber \\
 & \times & \left(\frac{M_{500,i}}{1.04 \times 10^{13} h_{70}^{-1} \rmn{M_{\odot}}}\right)^{0.135\pm(0.030g_{2})} \frac{M_{500,i}}{\int_{0}^{R_{500,i}} \rho_{\rmn{gas}} \rmn{d}V}
\label{eq:gas_scaling}
\end{eqnarray}
where $g_{1}$ and $g_{2}$ are random Gaussian number which we use in order to
simulate the natural scatter of the gas profiles.\footnote{The values
  $0.0064$ and $0.03$ quoted in equation~(\ref{eq:gas_scaling}) do not represent
  the proper scatter of the $f_{\rmn{gas},500}-M_{500}$ relation but reflect the
  parameter errors and we rescaled the numerical values to a Hubble constant of
  $h_{70}$ used in this work.}

\begin{figure} 
\centering
\includegraphics[width=0.5\textwidth]{figures/gas_profiles.eps}
\caption{Electron density profiles of the 31 clusters in the REXCESS sample. Grey and black lines represent NCCCs and CCCs, respectively. The blue and red lines represent our GNFW mean profile for the NCCCs and CCCs, respectively.}
\label{fig:gas_profiles}
\end{figure}

Hence, for each cluster in our sample we obtain a gas density profile
$\rho_{\rmn{gas},i}$ that obeys the observed $f_{gas,500}-M_{500}$ relation and
is uniquely determined by its DM mass $M_{500,i}$ and by the property of being a
NCCC or CCC. We assign the latter property to every halo depending on its
merging history. In particular, we make use of the offset parameter
$X_{\rmn{off}}$ computed for the MultiDark halo catalog. This is defined as the
distance from the halo center to the center of mass in units of the virial
radius. This parameter assesses the dynamical state of the cluster and whether
the halo experienced a recent merger or not. Current observations reveal a ratio
of NCCCs and CCCs of about $50\%$ (e.g., \citealp{2007A&A...466..805C,
  2009MNRAS.395..764S}). Since there is a correlation between merging clusters
and NCCCs, we use the median of the $X_{\rmn{off}}$ distribution to separate our
sample into CCCs and NCCCs (with NCCCs defined to be those halos with the larger
dynamical offsets). Clearly, this is an over-simplification, and future X-ray
surveys will have to determine this property also as a function of redshift.

\begin{figure*} 
\centering
\includegraphics[width=0.33\textwidth]{figures/lx_m.eps}
\includegraphics[width=0.33\textwidth]{figures/yx_m.eps}
\includegraphics[width=0.33\textwidth]{figures/sz_m.eps}
\caption{X-ray and SZ scaling relations. Grey triangles show the MultiDark
  sample (limited to the mass range covered by observations), the black line is
  the corresponding scaling relation, and the blue line is the
  observational result. The black crosses represent the median values of the
  quantity in question for a given mass bin (indicated by horizontal error
  bars), and the vertical error bars represent the standard deviation within a
  bin.  \emph{Left.} We compare the bolometric X-ray luminosity-to-mass
  relation, $L_{\rmn{bol}}-M_{500}$, at $z=0.2$ to the observational sample by
  \protect\cite{2010MNRAS.406.1773M} with a median of $z \approx 0.2$. \emph{Center.}
  $Y_{\rmn{X}}-M_{500}$ scaling relation of our model in comparison to the
  observational sample by \protect\cite{2010MNRAS.406.1773M}. \emph{Right.}
  $Y_{\rmn{SZ}}-M_{500}$ scaling relation at $z=0.16$ in comparison
  to the observational sample by the \protect\cite{2013arXiv1303.5080P} with a median
  redshift of about $0.15$. The bottom panels show the relative difference to
  the observational scaling relations.}
\label{fig:X_LM}
\end{figure*}

We also account for redshift evolution of the gas profiles. While our NCCC and
CCC gas profiles as derived from the REXCESS cluster sample are merely used to
define a profile shape, the normalization of the gas profiles is set by the
observational $f_{\rmn{gas},500}-M_{500}$ relation \citep{2009ApJ...693.1142S}.
The 43 clusters used in \cite{2009ApJ...693.1142S} have redshifts $0.012 < z <
0.12$ with a \emph{median} of $z \approx 0.04$. Thus, our phenomenological gas
profile is representative of the cluster population at $z\approx0$. To extend this
profile to high-$z$, we include a \emph{self-similar} scaling of the gas density
as $\rho_{\rmn{gas}}(z) = E(z)^{2} \rho_{\rmn{gas}}(z=0)$, where $E(z)^{2} =
\Omega_{\rmn{m}} (1+z)^{3} + \Omega_{{\Lambda}}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{X-ray and SZ scaling relations}
\label{sec:4}

In order to check whether our phenomenologically derived gas profiles reproduce
the observations, we calculate the bolometric thermal bremsstrahlung
luminosity $L_{\rmn{bol}}$ as in \cite{1988xrec.book.....S}\footnote{We check
  our procedure by fitting each of the 31 REXCESS clusters with
  equation~(\ref{eq:gnfw}) and calculating $L_{\rmn{bol}}$ with the measured gas
  temperature of each cluster. As a result, we fall short of the observed
  luminosity by a mean (median) of about $21\%$ ($20\%$). This is reasonable
  considering that we do not permit the parameters $R_{\rmn{c}}$, $\alpha$ and
  $\delta$ to vary between different objects. Additionally, we neglect atomic
  line emission which may give a noticeable contribution, in particularly for
  low-mass clusters and in the cluster outskirts of larger systems.}  and
compare our sample result with the observed $L_{\rmn{bol}} - M_{500}$ relation
and XLF.\footnote{The mean (median) difference at $z=0$ between
  $L_{\rmn{bol}}$ within $R_{200}$ or within $R_{500}$ is $\approx 5\%$ ($\approx
  7\%$). While $L_{\rmn{bol}}$ refers to the quantity calculated within
  $R_{500}$, we note that the XLF for luminosities calculated within $R_{200}$
  will be barely changed.}

To assign a temperature to our model clusters (that is needed for calculating
$L_{\rmn{bol}}$ and $Y_{\rmn{X}}$), we adopt the $T-M_{500}$ relation by
\cite{2010MNRAS.406.1773M},
\begin{equation}
\log_{10} \left( \frac{k_{\rmn{B}}T_{\rmn{ci}}}{\rmn{keV}} \right) = 
A + B~\log_{10} \left( \frac{E(z) M_{500}}{10^{15} h_{70}^{-1} \rmn{M_{\odot}}} \right)
\label{eq:temp}
\end{equation}
where $A=0.91$, $B=0.46$, and $T_{\rmn{ci}}$ is the cluster temperature
\emph{not} centrally excised
(\citealp{2010MNRAS.406.1773M}). \cite{2010MNRAS.406.1773M} report a scatter of
$\sigma_{\rmn{yx}} = 0.06,$\footnote{Scatter is calculated as $\sigma_{\rmn{yx}}
  = \sqrt{ \left\{ \Sigma_{i=1}^{N} [Y_{i}-(A+B~X_{i})]^{2}\right\} / N-1}$
  where the sum extends over the data points $X_{i}, Y_{i}$, and $A$ and $B$ are
  the fit parameters.} which we apply to our sample using Gaussian deviates.

In the left panel of Fig.~\ref{fig:X_LM}, we show how our model
$L_{\rmn{bol}}-M_{500}$ relation compares with observations by
\cite{2010MNRAS.406.1773M} (\emph{all} data, see their Table~7). Their sample is
composed of 238 clusters at $0.02<z<0.46$ with a median of $z \approx 0.2$ and
self-consistently takes into account all selection effects, covariances,
systematic uncertainties and the cluster mass function
\citep{2010MNRAS.406.1759M}.  For this reason, we compare the
\cite{2010MNRAS.406.1773M} data to our model at $z=0.2$, and limit the
comparison to the mass range covered by the observations. Overall, there is
reassuring agreement between our phenomenological model and the data, which
probe our model most closely on scales around the cluster core radii (which is
where the contribution to $L_{\rmn{X}}$ per logarithmic interval in radius, $\dd
L_{\rmn{X}}/\dd\log r \propto r^3 n_{\rm{gas}}^2(r) \sqrt{k_{\rmn{B}}T}$,
approximately attains its maximum).  In Table~\ref{tab:LMfits}, we show our
model $L_{\rmn{bol}}-M_{500}$ scaling relation and its scatter for different
redshifts. We find that the scatter of our samples at all redshifts are Gaussian
distributed with a standard deviation of $\sigma_{yx} \approx 0.18$ that matches
the observational results of \cite{2010MNRAS.406.1773M}, which report a scatter
of $\sigma_{yx} = 0.185$.

In the middle panel of Fig.~\ref{fig:X_LM}, we compare the
$Y_{\rmn{X}}-M_{500}$ relation of our sample to observational data
\citep{2010MNRAS.406.1773M}. The model agrees nicely at the high-mass end, but
underpredicts the observed scaling at low masses by about $20\%$ (at the
1-$\sigma$ level). This is the same level of deviation from the data as in the
case of $L_{\rmn{X}}$, which is more significant due to the smaller scatter in
the $Y_{\rmn{X}}$ relation. The differential contribution to the thermal energy
per logarithmic interval in radius (and hence to the integrated Compton-$y$
parameter) is given by $\dd Y /\dd\log r \propto r^3 P_{\rmn{th}}(r)$, with the
thermal gas pressure $P_{\rmn{th}}=n_{\rmn{gas}}k_{\rmn{B}}T$. It peaks at
scales slightly smaller than $R_{500}$ with 1-$\sigma$ contributions extending
out to $3\,R_{500}$ \citep{2010ApJ...725...91B}. Hence, the observational
scaling constrains our model on those large scales, quite complementary to the
X-ray luminosity. The deviations at small masses either indicates different
assumptions about $f_{\rmn{gas}}$, the gas temperature, or different selection
effects of either observational sample that we use for model calibration and
comparison.  \cite{2010MNRAS.406.1773M} determine their masses by adopting a
constant value for $f_{\rmn{gas}}$, in contrast to our approach which adopts the
observed $f_{\rmn{gas},500}-M_{500}$ relation given by
\cite{2009ApJ...693.1142S}. Additionally, we adopt the
\cite{2010MNRAS.406.1773M} \emph{centrally included} temperature throughout all
our work, while \cite{2010MNRAS.406.1773M} use the \emph{centrally excised}
temperature to calculate $Y_{\rmn{X}}$. This assumption also impacts the scatter
of the $Y_{\rmn{X}}-M$ relation. In fact, using the \emph{centrally included}
temperature, we found a scatter of $\sigma_{yx} \approx 0.11$ (see
Table~\ref{tab:YXfits} where our $Y_{\rmn{X}}$ scaling relations are reported),
significantly higher than the value of $\sigma_{yx} = 0.052$ found by
\cite{2010MNRAS.406.1773M}.

In the right panel of Fig.~\ref{fig:X_LM}, we compare the
$Y_{\rmn{SZ}}-M_{500}$ relation in our model (calculated as in equation~(3) of
\citealp{2011arXiv1109.3709B}) with the observed scaling relation by the
\cite{2013arXiv1303.5080P}. Their sample contains clusters up to $z \approx
0.45$ and has a median of $z \approx 0.15$; hence, we compare the data to our
relation at the MultiDark snapshot $z=0.16$ (that contains 11419 clusters above
our mass cut) which however is not used throughout the rest of the work. Our
model reproduces the data remarkably well, except for the high-mass end where
our simulations have a weaker constraining power due to the smaller box size in
comparison to the survey volume of {\em Planck}.  We find a scatter of
$\sigma_{yx} \approx 0.11$ which compares well with the \emph{Planck} result of
$\sigma_{yx} \approx 0.1$. In Table~\ref{tab:YSZfits}, we report our SZ scaling
relations for different redshifts.

\begin{table} 
\begin{center}
\caption{$L_{\rmn{bol}}-M_{500}$ scaling relations.}
\medskip
\begin{tabular}{cccc}
\hline
\phantom{\Big|}
redshift $z$ & $A$ & $B$ & $\sigma_{yx}$ \\
\hline \\[-0.5em]
 0      & $-21.41\pm0.11$ & $1.50\pm0.01$ & 0.179\\
 0.1   & $-21.30\pm0.12$ & $1.50\pm0.01$ & 0.179\\
 0.2   & $-21.50\pm0.13$ & $1.51\pm0.01$ & 0.178\\ 
 0.4   & $-21.13\pm0.17$ & $1.49\pm0.01$ & 0.178\\ 
 0.61 & $-21.59\pm0.22$ & $1.53\pm0.01$ & 0.177\\ 
 0.78 & $-20.73\pm0.29$ & $1.48\pm0.02$ & 0.177\\ 
 1      & $-20.45\pm0.42$ & $1.46\pm0.03$ & 0.177\\[0.5em]
\hline
\end{tabular}
\label{tab:LMfits}
\end{center}
\footnotesize{Note. Scaling relations are reported in the form of $\log_{10}~(L_{\rmn{bol}}~/~E(z)~h_{70}^{-2}~10^{44}~\rmn{erg~s}^{-1})=A+B~\log_{10}~(E(z)~M_{500}~/~h_{70}^{-1}~\rmn{M_{\odot}})$. The relation scatter $\sigma_{yx}$ is also shown.}
\end{table}

\begin{table} 
\begin{center}
\caption{$Y_{\rmn{X}, 500}-M_{500}$ scaling relations.}
\medskip
\begin{tabular}{cccc}
\hline
\phantom{\Big|}
redshift $z$ & $A$ & $B$ & $\sigma_{yx}$ \\
\hline\\[-0.5em]
 0      & $-9.18\pm0.07$ & $1.61\pm0.01$ & 0.109\\
 0.1   & $-8.85\pm0.07$ & $1.59\pm0.01$ & 0.109\\
 0.2   & $-8.82\pm0.08$ & $1.59\pm0.01$ & 0.109\\ 
 0.4   & $-8.79\pm0.10$ & $1.59\pm0.01$ & 0.108\\ 
 0.61 & $-8.65\pm0.14$ & $1.59\pm0.01$ & 0.109\\ 
 0.78 & $-8.36\pm0.18$ & $1.57\pm0.01$ & 0.109\\ 
 1      & $-8.28\pm0.26$ & $1.57\pm0.02$ & 0.109\\[0.5em]  
\hline
\end{tabular}
\label{tab:YXfits}
\end{center}
\footnotesize{Note. Scaling relations are reported in the form of $\log_{10}~(E(z)~Y_{\rmn{X},500}~/~h_{70}^{-2.5}~\rmn{M_{\odot}}~\rmn{keV})=A+B~\log_{10}~(E(z)~M_{500}~/~h_{70}^{-1}~\rmn{M_{\odot}})$. The relation scatter $\sigma_{yx}$ is also shown.}
\end{table}

\begin{table} 
\begin{center}
\caption{$Y_{\rmn{SZ}, 500}-M_{500}$ scaling relations.}
\medskip
\begin{tabular}{cccc}
\hline
\phantom{\Big|}
redshift $z$ & $A$ & $B$ & $\sigma_{yx}$ \\
\hline\\[-0.5em]
 0      & $-27.93\pm0.07$ & $1.60\pm0.01$ & 0.109\\
 0.1   & $-27.74\pm0.07$ & $1.59\pm0.01$ & 0.109\\
 0.16 & $-27.76\pm0.08$ & $1.59\pm0.01$ & 0.109\\
 0.2   & $-27.65\pm0.08$ & $1.59\pm0.01$ & 0.109\\ 
 0.4   & $-27.57\pm0.10$ & $1.59\pm0.01$ & 0.108\\ 
 0.61 & $-27.50\pm0.13$ & $1.59\pm0.01$ & 0.109\\ 
 0.78 & $-27.15\pm0.18$ & $1.58\pm0.01$ & 0.109\\ 
 1      & $-27.01\pm0.26$ & $1.58\pm0.02$ & 0.109\\[0.5em] 
\hline
\end{tabular}
\label{tab:YSZfits}
\end{center}
\footnotesize{Note. Scaling relations are reported in the form of $\log_{10}~(E(z)^{-2/3}~Y_{\rmn{SZ},500}~/~h_{70}^{-2.5}~\rmn{Mpc}^{2})=A+B~\log_{10}~(M_{500}~/~h_{70}^{-1}~\rmn{M_{\odot}})$. The relation scatter $\sigma_{yx}$ is also shown.}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{X-ray luminosity function}
\label{sec:5}

Studies of the XLF got out of fashion during the last years due to the
difficulties of using the X-ray luminosity for cosmological purposes. The X-ray
emissivity scales with the square of the gas density, which makes it subject to
density variations and clumping. This implies large scatter that causes a large
Malmquist bias and underlines the necessity of careful mock surveys that need to
address all systematics.

Nevertheless, it provides a complementary check for our model. To this end, we
use the \emph{ROSAT} brightest cluster sample (BCS) XLF
\citep{1997ApJ...479L.101E}, which is in good agreement with results from the
\emph{ROSAT} ESO Flux-Limited X-ray (REFLEX; \citealp{2002ApJ...566...93B}) and
HIFLUGCS \citep{2002ApJ...567..716R}.  Note that the XLF is fully determined by
the mass function and the $L_{\rmn{X}}-M_{500}$ relation after taking into
account the observational biases. This means that applying the Malmquist and
Eddington-bias-corrected $L_{\rmn{X}}-M_{500}$ relation by
\cite{2010MNRAS.406.1773M} directly to the MultiDark mass function and
accounting for the observational scatter in $L_{\rmn{X}}-M_{500}$ should yield
an unbiased XLF. We show the resulting bolometric and soft-band ($0.1-2.4$~keV)
XLF in Fig.~\ref{fig:XLF} and compare those to the corresponding BCS XLFs and
to our model predictions. Note that there is only the Schechter fit available
for the BCS bolometric XLF.  While the soft-band XLF by
\cite{2010MNRAS.406.1773M} agrees well with the BCS data points, it deviates
from the corresponding Schechter fit at low luminosities. This is also true in
the bolometric band, where the XLFs of \cite{2010MNRAS.406.1773M} and our model
agree well, but deviate from the BCS Schechter fit at low luminosities. This may
be an artifact due to the use of Schechter fit instead of the data points or may
point to incompleteness of the BCS sample. Note that the Poissonian errors of
the XLF obtained from the MultiDark simulation are a lower limit as we are
neglecting the uncertainty due to cosmic variance.  Studies of the XLF will
become again an important topic with the upcoming launch of the \emph{e}ROSITA
satellite (e.g., \citealp{2011MSAIS..17..159C}) and further studies in this
direction are desirable. For these reasons, we do not show XLF predictions at
other redshifts, leaving this for a future study.

\begin{figure} 
\centering
\includegraphics[width=0.48\textwidth]{figures/xlf.eps}
\caption{Bolometric and soft-band ($0.1-2.4$~keV) XLFs. Shown are the soft-band
  data points, the soft-band and bolometric Schechter fits of the BCS sample of
  \protect\cite{1997ApJ...479L.101E}, which has a median of $z \approx 0.08$.  While the
  soft-band XLF, which was obtained applying the \protect\cite{2010MNRAS.406.1773M}
  $L_{\rmn{X}}-M_{500}$ relation to the MultiDark $z = 0.1$ snapshot, compares
  well with the BCS data points, it deviates from the corresponding Schechter
  fit. We also show the bolometric XLF of \protect\cite{2010MNRAS.406.1773M} and
  bolometric XLF of our model at $z=0.1$. The XLFs are calculated in equally
  log-spaced mass bins; the error bars represent the Poissonian errors. Note
  that we limit the comparison to the luminosity range covered by our sample,
  where we cut the lowest part because in that range the XLF rapidly drops due
  to the imposed mass cut.}
\label{fig:XLF}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{sec:6}

{\bf Discussion...}

{\bf We build a complete cosmological sample of galaxy clusters from the MultiDark 
$N$-body simulation with redshifts ranging from $z = 0$ to 1. We construct a 
\emph{phenomenological} model for the cluster-gas distribution. This is characterized 
by X-ray-inferred (CCC and NCCC) gas profiles (taken from the REXCESS sample) 
and a cluster-mass-dependent gas fraction. We assign such a (cluster mass-dependent) 
gas density profile to each DM halo in our sample and sort it into the NCCC/CCC populations 
according to a dynamical disturbance parameter that is calculated from the DM distribution.
With this model, we obtain a cosmologically complete mock catalog of galaxy
clusters that matches the observed $L_{\rmn{X, bol}}$-to-$M_{500}$,
$Y_{\rmn{X}}$-to-$M_{500}$, and $Y_{\rmn{SZ}}$-to-$M_{500}$ relations, as well
as the X-ray luminosity function. We apply it in the companion Paper~2 to 
predict the radio and gamma-ray emission of our sample.

Eventually, we provide a cosmologically complete multi-frequency mock catalog for the (non-)thermal 
cluster emission at different redshifts. We make these catalogs publicly and freely available 
on-line through the MultiDark database (www.multidark.org). Those contain the quantities
$\rho_{\rmn{gas}}$, $L_{\rmn{X, bol}}$, $Y_{\rmn{X}}$, $Y_{\rmn{SZ}}$, $L_{120~\rmn{MHz}}$, 
$L_{1.4~\rmn{GHz}}$, $L_{>100~\rmn{MeV}}$ and $L_{>100~\rmn{GeV}}$ (among many others). 
We hope that the community can make valuable use of these catalogues in synergy with the future 
radio, X-ray and gamma-ray data.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgments}
We thank Anders Pinzke for many useful discussions. 
%We thank Lawrence Rudnick
%and Shea Brown for a reanalysis of their
%352~MHz radio map of Coma, and for useful discussions. We thank Matteo
%Murgia for kindly providing the radio surface brightness profiles of Ophiuchucs
%and Abell~2163 that have been recomputed with respect to the Reiprich \&
%B\"{o}ringher (2002) cluster positions, and Wolfgang Reich for providing the
%1.4~GHz radio map of Coma.  
We also thank Harald Ebeling, Stefan Gottl{\"o}berg,
Anatoly Klypin, Andrey Kravtsov, Adam Mantz, Frazer Pearce, Miguel-Angel Perez
Torres, Huub R{\"o}ttgering, Jos\'e Alberto Rubi\~no, and Gustavo Yepes, for the
useful discussions and advices. Finally, we thank the MultiDark database
people, in particular Adrian Partl and Kristin Riebe. 
F.Z.{\ }acknowledges the CSIC financial support as a JAE-Predoc grant of the 
program ``Junta para la Ampliaci\'on de Estudios'' co-financed by the FSE. 
F.Z.{\ }acknowledges the hospitality of the Leiden Observatory during his stay.
F.Z.{\ }and F.P.{\ } thank the support of the Spanish MICINN's Consolider-Ingenio 2010 Programme under
grant MultiDark CSD2009-00064. C.P.{\ }gratefully acknowledges financial support
of the Klaus Tschira Foundation. The MultiDark Database used in this paper and
the web application providing online access to it were constructed as part of
the activities of the German Astrophysical Virtual Observatory as result of a
collaboration between the Leibniz-Institute for Astrophysics Potsdam (AIP) and
the Spanish MultiDark Consolider Project CSD2009-00064. The Bolshoi and
MultiDark simulations were run on the NASA's Pleiades supercomputer at the NASA
Ames Research Center.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{mn2e}
\bibliography{bib_file}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\label{lastpage}

\end{document}

### 2013-04-17 paper1.tex
small change

@@
 \citealp{2011arXiv1109.3709B}) with the observed scaling relation by the
-\cite{2013arXiv1303.5080P}. Their sample contains clusters up to $z \approx
-0.45$ and has a median of $z \approx 0.15$; hence, we compare the data to our
+\cite{2013arXiv1303.5080P}. {\bf We compare with the result obtained from the \emph{Planck} Cosmo 
+sample with Malmquist bias correction (see their Table~A.1).} Their sample contains clusters 
+up to $z \approx 0.45$ and has a median of $z \approx 0.15$; hence, we compare the data to our
 relation at the MultiDark snapshot $z=0.16$ (that contains 11419 clusters above
@@
 $\sigma_{yx} \approx 0.11$ which compares well with the \emph{Planck} result of
-$\sigma_{yx} \approx 0.1$. In Table~\ref{tab:YSZfits}, we report our SZ scaling
+$\sigma_{yx} \approx 0.08$. In Table~\ref{tab:YSZfits}, we report our SZ scaling
 relations for different redshifts.

### 2013-07-03 paper1.tex
New SZ Scaling Relation

@@
   observational sample by \protect\cite{2010MNRAS.406.1773M}. \emph{Right.}
-  $Y_{\rmn{SZ}}-M_{500}$ scaling relation at $z=0.16$ in comparison
-  to the observational sample by the \protect\cite{2013arXiv1303.5080P} with a median
-  redshift of about $0.15$. The bottom panels show the relative difference to
+  $Y_{\rmn{SZ}}-M_{500}$ scaling relation at $z=0.18$ in comparison
+  to the observational sample by the \protect\cite{2013arXiv1303.5080P} with a 
+  median redshift of $0.18$. The bottom panels show the relative difference to
   the observational scaling relations.}
@@
 \citealp{2011arXiv1109.3709B}) with the observed scaling relation by the
-\cite{2013arXiv1303.5080P}. {\bf We compare with the result obtained from the \emph{Planck} Cosmo 
-sample with Malmquist bias correction (see their Table~A.1).} Their sample contains clusters 
-up to $z \approx 0.45$ and has a median of $z \approx 0.15$; hence, we compare the data to our
-relation at the MultiDark snapshot $z=0.16$ (that contains 11419 clusters above
-our mass cut) which however is not used throughout the rest of the work. Our
+\cite{2013arXiv1303.5080P}. {\bf We compare with the result obtained from the 
+\emph{Planck} Cosmo sample with Malmquist bias correction (see their Table~A.1),
+which has a median redshift of $0.18$. Hence, we compare the data to our relation 
+at the MultiDark snapshot $z=0.18$ (that contains 11105 clusters 
+above our mass cut) which however is not used throughout the rest of the work}. Our
 model reproduces the data remarkably well, except for the high-mass end where
@@
  0.1   & $-27.74\pm0.07$ & $1.59\pm0.01$ & 0.109\\
- 0.16 & $-27.76\pm0.08$ & $1.59\pm0.01$ & 0.109\\
+ 0.18 & $-27.73\pm0.08$ & $1.59\pm0.01$ & 0.109\\
  0.2   & $-27.65\pm0.08$ & $1.59\pm0.01$ & 0.109\\ 

### 2013-08-22 paper1.tex
last Fabio version

@@
 
-\voffset-0.5in
+%\voffset-0.5in
 
@@
 $\Delta=500$ times the \emph{critical} density of the Universe. We adopt density 
-parameters of $\Omega_{\rmn{m}}=0.3$, $\Omega_{\Lambda}=0.7$ and today's 
+parameters of $\Omega_{\rmn{m}}=0.27$, $\Omega_{\Lambda}=0.73$ and today's 
 Hubble constant of $H_0 = 100 \times h_{70}$~km~s$^{-1}$~Mpc$^{-1}$ where $h_{70} = 0.7$.
@@
 The MultiDark simulation used in this work is described in detail in \cite{2011arXiv1104.5130P}.  
-It is an $N$-body cosmological simulation done with
-the Adaptive-Refinement-Tree (ART) code \citep{1997ApJS..111...73K} of
-$2048^3$ particles within a ($1000$~Mpc~$h^{-1}$)$^3$ cube. The latest WMAP5 and
-WMAP7 cosmological parameters were used. This simulation is particularly well
-suited for our purpose because of its large number of clusters.
+It is an $N$-body cosmological simulation done with the Adaptive-Refinement-Tree (ART) 
+code \citep{1997ApJS..111...73K} of $2048^3$ particles within a ($1000$~Mpc~$h^{-1}$)$^3$ 
+cube. The adopted cosmological parameters are $\Omega_{\rmn{m}}=0.27$, $\Omega_{\Lambda}=0.73$,
+$\Omega_\rmn{b}=0.0469$, $n_\rmn{s}=0.95$, $h=0.7$ and $\sigma_8=0.82$. This simulation is 
+particularly well suited for our purpose because of its large 
+number of high-mass objects, i.e., galaxy clusters.
 
@@
 
-{\bf In Paper~2, we present predictions for the LOFAR radio observatory\footnote{www.lofar.org} 
+{\bf In Paper~2, we present predictions for the LOFAR radio observatory
 which is expected to detect diffuse radio emission in clusters up to redshift $z \approx 1$ (e.g.,
-\citealp{2010A&A...509A..68C,2012JApA..tmp...34R}).} 
+\citealp{2012JApA..tmp...34R}).} 
 Thus, we make use of different simulation snapshots up to $z=1$. 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{figures/gas_profiles.eps}
+\includegraphics[width=0.48\textwidth]{figures/gas_profiles.eps}
 \caption{Electron density profiles of the 31 clusters in the REXCESS sample.
@@
 \centering
-\includegraphics[width=0.33\textwidth]{figures/lx_m.eps}
-\includegraphics[width=0.33\textwidth]{figures/yx_m.eps}
-\includegraphics[width=0.33\textwidth]{figures/sz_m.eps}
-\caption{X-ray and SZ scaling relations. Grey triangles show the MultiDark
+\includegraphics[width=0.48\textwidth]{figures/lx_m.eps}
+\includegraphics[width=0.48\textwidth]{figures/yx_m.eps}
+%\includegraphics[width=0.33\textwidth]{figures/sz_m.eps}
+\caption{X-ray scaling relations. Grey triangles show the MultiDark
   sample (limited to the mass range covered by observations), the black line is
@@
   relation, $L_{\rmn{bol}}-M_{500}$, at $z=0.2$ to the observational sample by
-  \protect\cite{2010MNRAS.406.1773M} with a median of $z \approx 0.2$. \emph{Center.}
-  $Y_{\rmn{X}}-M_{500}$ scaling relation of our model in comparison to the
-  observational sample by \protect\cite{2010MNRAS.406.1773M}. \emph{Right.}
-  $Y_{\rmn{SZ}}-M_{500}$ scaling relation at $z=0.18$ in comparison
-  to the observational sample by the \protect\cite{2013arXiv1303.5080P} with a 
-  median redshift of $0.18$. The bottom panels show the relative difference to
-  the observational scaling relations.}
+  \protect\cite{2010MNRAS.406.1773M} with a median of $z \approx 0.2$. 
+  \emph{Right.} $Y_{\rmn{X}}-M_{500}$ scaling relation of our model in comparison to the
+  observational sample by \protect\cite{2010MNRAS.406.1773M}.} 
+  %\emph{Right.} $Y_{\rmn{SZ}}-M_{500}$ scaling relation at $z=0.2$ in comparison
+  %to the observational sample by the \protect\cite{2013arXiv1303.5080P} with a 
+  %median redshift of about $0.18$. The bottom panels show the relative difference to
+  %the observational scaling relations.}
 \label{fig:X_LM}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{X-ray and SZ scaling relations}
+\section{X-ray scaling relations and luminosity function}
 \label{sec:4}
@@
 
-In the middle panel of Fig.~\ref{fig:X_LM}, we compare the
+In the right panel of Fig.~\ref{fig:X_LM}, we compare the
 $Y_{\rmn{X}}-M_{500}$ relation of our sample to observational data
@@
 \cite{2010MNRAS.406.1773M}.
-
-In the right panel of Fig.~\ref{fig:X_LM}, we compare the
-$Y_{\rmn{SZ}}-M_{500}$ relation in our model (calculated as in equation~(3) of
-\citealp{2011arXiv1109.3709B}) with the observed scaling relation by the
-\cite{2013arXiv1303.5080P}. {\bf We compare with the result obtained from the 
-\emph{Planck} Cosmo sample with Malmquist bias correction (see their Table~A.1),
-which has a median redshift of $0.18$. Hence, we compare the data to our relation 
-at the MultiDark snapshot $z=0.18$ (that contains 11105 clusters 
-above our mass cut) which however is not used throughout the rest of the work}. Our
-model reproduces the data remarkably well, except for the high-mass end where
-our simulations have a weaker constraining power due to the smaller box size in
-comparison to the survey volume of {\em Planck}.  We find a scatter of
-$\sigma_{yx} \approx 0.11$ which compares well with the \emph{Planck} result of
-$\sigma_{yx} \approx 0.08$. In Table~\ref{tab:YSZfits}, we report our SZ scaling
-relations for different redshifts.
 
@@
 
-\begin{table} 
-\begin{center}
-\caption{$Y_{\rmn{SZ}, 500}-M_{500}$ scaling relations.}
-\medskip
-\begin{tabular}{cccc}
-\hline
-\phantom{\Big|}
-redshift $z$ & $A$ & $B$ & $\sigma_{yx}$ \\
-\hline\\[-0.5em]
- 0      & $-27.93\pm0.07$ & $1.60\pm0.01$ & 0.109\\
- 0.1   & $-27.74\pm0.07$ & $1.59\pm0.01$ & 0.109\\
- 0.18 & $-27.73\pm0.08$ & $1.59\pm0.01$ & 0.109\\
- 0.2   & $-27.65\pm0.08$ & $1.59\pm0.01$ & 0.109\\ 
- 0.4   & $-27.57\pm0.10$ & $1.59\pm0.01$ & 0.108\\ 
- 0.61 & $-27.50\pm0.13$ & $1.59\pm0.01$ & 0.109\\ 
- 0.78 & $-27.15\pm0.18$ & $1.58\pm0.01$ & 0.109\\ 
- 1      & $-27.01\pm0.26$ & $1.58\pm0.02$ & 0.109\\[0.5em] 
-\hline
-\end{tabular}
-\label{tab:YSZfits}
-\end{center}
-\footnotesize{Note.
-Scaling relations are reported in the form of $\log_{10}~(E(z)^{-2/3}~Y_{\rmn{SZ},500}~/~h_{70}^{-2.5}~\rmn{Mpc}^{2})=A+B~\log_{10}~(M_{500}~/~h_{70}^{-1}~\rmn{M_{\odot}})$.
-The relation scatter $\sigma_{yx}$ is also shown.}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{X-ray luminosity function}
-\label{sec:5}
-
+\subsection{X-ray Luminosity Function}
 Studies of the XLF got out of fashion during the last years due to the
@@
 address all systematics.
+
+\begin{figure} 
+\centering
+\includegraphics[width=0.48\textwidth]{figures/xlf.eps}
+\caption{Bolometric and soft-band ($0.1-2.4$~keV) XLFs. Shown are the soft-band
+  data points, the soft-band and bolometric Schechter fits of the BCS sample of
+  \protect\cite{1997ApJ...479L.101E}, which has a median of $z \approx 0.08$.  While the
+  soft-band XLF, which was obtained applying the \protect\cite{2010MNRAS.406.1773M}
+  $L_{\rmn{X}}-M_{500}$ relation to the MultiDark $z = 0.1$ snapshot, compares
+  well with the BCS data points, it deviates from the corresponding Schechter
+  fit. We also show the bolometric XLF of \protect\cite{2010MNRAS.406.1773M} and
+  bolometric XLF of our model at $z=0.1$. The XLFs are calculated in equally
+  log-spaced mass bins; the error bars represent the Poissonian errors. Note
+  that we limit the comparison to the luminosity range covered by our sample,
+  where we cut the lowest part because in that range the XLF rapidly drops due
+  to the imposed mass cut.}
+\label{fig:XLF}
+\end{figure}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{SZ scaling relations}
+\label{sec:5}
+In the right panel of Fig.~\ref{fig:X_LM}, we compare the
+$Y_{\rmn{SZ}}-M_{500}$ relation in our model (calculated as in equation~(3) of
+\citealp{2011arXiv1109.3709B}) with the observed scaling relation by the
+\cite{2013arXiv1303.5080P}. {\bf We compare with the result obtained from the 
+\emph{Planck} COSMO sample with Malmquist bias correction (see their Table~A.1),
+which has a median redshift of $0.18$. Hence, we compare the data to our relation 
+at the MultiDark snapshot $z=0.2$}. Our model reproduces the data remarkably well, except 
+for the high-mass end where our simulations have a weaker constraining power due to the 
+smaller box size in comparison to the survey volume of {\em Planck}. We find a scatter of
+$\sigma_{yx} \approx 0.11$ which compares well with the \emph{Planck} result of
+$\sigma_{yx} \approx 0.08$. In Table~\ref{tab:YSZfits}, we report our SZ scaling
+relations for different redshifts.
+
 \begin{figure} 
 \centering
-\includegraphics[width=0.48\textwidth]{figures/xlf.eps}
-\caption{Bolometric and soft-band ($0.1-2.4$~keV) XLFs. Shown are the soft-band
-  data points, the soft-band and bolometric Schechter fits of the BCS sample of
-  \protect\cite{1997ApJ...479L.101E}, which has a median of $z \approx 0.08$.  While the
-  soft-band XLF, which was obtained applying the \protect\cite{2010MNRAS.406.1773M}
-  $L_{\rmn{X}}-M_{500}$ relation to the MultiDark $z = 0.1$ snapshot, compares
-  well with the BCS data points, it deviates from the corresponding Schechter
-  fit. We also show the bolometric XLF of \protect\cite{2010MNRAS.406.1773M} and
-  bolometric XLF of our model at $z=0.1$. The XLFs are calculated in equally
-  log-spaced mass bins; the error bars represent the Poissonian errors. Note
-  that we limit the comparison to the luminosity range covered by our sample,
-  where we cut the lowest part because in that range the XLF rapidly drops due
-  to the imposed mass cut.}
-\label{fig:XLF}
+\includegraphics[width=0.48\textwidth]{figures/sz_m.eps}
+\caption{SZ scaling relations. Grey triangles show the MultiDark
+  sample (limited to the mass range covered by observations), the black line is
+  the corresponding scaling relation, and the blue line is the
+  observational result. The black crosses represent the median values of the
+  quantity in question for a given mass bin (indicated by horizontal error
+  bars), and the vertical error bars represent the standard deviation within a
+  bin.  \emph{Left.} We compare the bolometric X-ray luminosity-to-mass
+  relation, $L_{\rmn{bol}}-M_{500}$, at $z=0.2$ to the observational sample by
+  \protect\cite{2010MNRAS.406.1773M} with a median of $z \approx 0.2$. 
+  \emph{Right.} $Y_{\rmn{X}}-M_{500}$ scaling relation of our model in comparison to the
+  observational sample by \protect\cite{2010MNRAS.406.1773M}. 
+  \emph{Left.} $Y_{\rmn{SZ}}-M_{500}$ scaling relation at $z=0.2$ in comparison
+  to the observational sample by the \protect\cite{2013arXiv1303.5080P} with a 
+  median redshift of about $0.18$. The bottom panels show the relative difference to
+  the observational scaling relations.}
+\label{fig:SZ_M}
 \end{figure}
+
+\begin{figure*} 
+\centering
+\includegraphics[width=0.48\textwidth]{figures/sz_m_SPT.eps}
+\includegraphics[width=0.48\textwidth]{figures/sz_m_ACT.eps}
+\caption{SZ scaling relations. Grey triangles show the MultiDark
+  sample (limited to the mass range covered by observations), the black line is
+  the corresponding scaling relation, and the blue line is the
+  observational result. The black crosses represent the median values of the
+  quantity in question for a given mass bin (indicated by horizontal error
+  bars), and the vertical error bars represent the standard deviation within a
+  bin.  \emph{Left.} We compare the bolometric X-ray luminosity-to-mass
+  relation, $L_{\rmn{bol}}-M_{500}$, at $z=0.2$ to the observational sample by
+  \protect\cite{2010MNRAS.406.1773M} with a median of $z \approx 0.2$. 
+  \emph{Right.} $Y_{\rmn{X}}-M_{500}$ scaling relation of our model in comparison to the
+  observational sample by \protect\cite{2010MNRAS.406.1773M}. 
+  \emph{Left.} $Y_{\rmn{SZ}}-M_{500}$ scaling relation at $z=0.2$ in comparison
+  to the observational sample by the \protect\cite{2013arXiv1303.5080P} with a 
+  median redshift of about $0.18$. The bottom panels show the relative difference to
+  the observational scaling relations.}
+\label{fig:SZ_M_1}
+\end{figure*}
+
+\begin{table} 
+\begin{center}
+\caption{$Y_{\rmn{SZ}, 500}-M_{500}$ scaling relations.}
+\medskip
+\begin{tabular}{cccc}
+\hline
+\phantom{\Big|}
+redshift $z$ & $A$ & $B$ & $\sigma_{yx}$ \\
+\hline\\[-0.5em]
+ 0      & $-27.93\pm0.07$ & $1.60\pm0.01$ & 0.109\\
+ 0.1   & $-27.74\pm0.07$ & $1.59\pm0.01$ & 0.109\\
+ 0.18 & $-27.73\pm0.08$ & $1.59\pm0.01$ & 0.109\\
+ 0.2   & $-27.65\pm0.08$ & $1.59\pm0.01$ & 0.109\\ 
+ 0.4   & $-27.57\pm0.10$ & $1.59\pm0.01$ & 0.108\\ 
+ 0.61 & $-27.50\pm0.13$ & $1.59\pm0.01$ & 0.109\\ 
+ 0.78 & $-27.15\pm0.18$ & $1.58\pm0.01$ & 0.109\\ 
+ 1      & $-27.01\pm0.26$ & $1.58\pm0.02$ & 0.109\\[0.5em] 
+\hline
+\end{tabular}
+\label{tab:YSZfits}
+\end{center}
+\footnotesize{Note.
+Scaling relations are reported in the form of $\log_{10}~(E(z)^{-2/3}~Y_{\rmn{SZ},500}~/~h_{70}^{-2.5}~\rmn{Mpc}^{2})=A+B~\log_{10}~(M_{500}~/~h_{70}^{-1}~\rmn{M_{\odot}})$.
+The relation scatter $\sigma_{yx}$ is also shown.}
+\end{table}
+
+{\bf We additionally compare our $Y_{\rmn{SZ}}$ to the results from the South Pole Telescope (SPT) 
+and Atacama Cosmology Telescope (ACT) surveys.
+We select a subsample of SPT clusters from \cite{2013ApJ...763..127R}, formed by the
+115 objects with confirmed redshift and signal-to-noise above 5, which has a median
+redshift of 0.56 with rms of 0.27. \cite{2013ApJ...763..127R} provide $Y_{\rmn{SZ}}$ 
+within an aperture of $1'$, corresponding to a median radius of $0.2$~h$_{70}^{-1}$~Mpc 
+at $z = 0.56$, which we use as aperture to calculate $Y_{\rmn{SZ, SPT}}$ in our MultiDark sample.
+
+In the left panel of Fig.~\ref{fig:SZ_M_1}, we compare the SPT cluster subsample to our 
+scaling relation at the three different MutliDark snapshots of $z = 0.4$, $0.61$ 
+and $0.78$. We color-coded the SPT clusters in order to show that the SPT 
+selection function is nearly redshift-independent. The fact that the angular size of galaxy clusters 
+decreases with redshift is an advantage for SPT due to its small beam, in fact, higher-redshift clusters 
+are less confused by primary CMB fluctuations. This effect is inverse for \emph{Planck} due to its
+larger beam. We can conclude that while our $Y_{\rmn{SZ}}-M_{500}$ scaling relation 
+compare fairly well to the median SPT cluster population, the SPT sample has a too
+large scatter to be well represented by single MultiDark snapshots.
+
+In the right panel of Fig.~\ref{fig:SZ_M_1}, we compare our scaling relation to
+the ACT sample overlapping with the Sloan Digital Sky Survey stripe 82 
+(\citealp{2013JCAP...07..008H}; we use the quantities inferred from the
+universal pressure profile scaling relation).
+The sample has a median redshift of 0.58 with rms of 0.28.
+\cite{2013JCAP...07..008H} provides $Y_{\rmn{SZ}}$ within $R_{500}$ which
+median, $0.42$~h$_{70}^{-1}$~Mpc, is, however, almost half of ours at the
+MultiDark snapshot $z=0.61$. Therefore, we use an aperture of $0.42$~h$_{70}^{-1}$~Mpc
+to calculate our $Y_{\rmn{SZ, ACT}}$. Also in this case we can conclude
+that our mock sample reproduce fairly well the median observational sample. 
+Note, however, the very different scatter of SPT and ACT samples.}
 
@@
 \section*{Acknowledgments}
-We thank Anders Pinzke for many useful discussions. 
-%We thank Lawrence Rudnick
-%and Shea Brown for a reanalysis of their
-%352~MHz radio map of Coma, and for useful discussions. We thank Matteo
-%Murgia for kindly providing the radio surface brightness profiles of Ophiuchucs
-%and Abell~2163 that have been recomputed with respect to the Reiprich \&
-%B\"{o}ringher (2002) cluster positions, and Wolfgang Reich for providing the
-%1.4~GHz radio map of Coma.  
-We also thank Harald Ebeling, Stefan Gottl{\"o}berg,
-Anatoly Klypin, Andrey Kravtsov, Adam Mantz, Frazer Pearce, Miguel-Angel Perez
-Torres, Huub R{\"o}ttgering, Jos\'e Alberto Rubi\~no, and Gustavo Yepes, for the
-useful discussions and advices. Finally, we thank the MultiDark database
-people, in particular Adrian Partl and Kristin Riebe. 
+We thank Anders Pinzke for many useful discussions. We also thank Harald Ebeling, 
+Stefan Gottl{\"o}berg, Anatoly Klypin, Andrey Kravtsov, Adam Mantz, Frazer Pearce, 
+Jos\'e Alberto Rubi\~no, and Gustavo Yepes, for the useful discussions and advices. 
+Finally, we thank the MultiDark database people, in particular Adrian Partl and Kristin Riebe. 
 F.Z.{\ }acknowledges the CSIC financial support as a JAE-Predoc grant of the 

### 2013-09-20 paper1.tex
Last Fabio Version

@@
 \begin{abstract}
-  ...
-  We build a mock galaxy cluster catalog from the large MultiDark $N$-body $\Lambda$CDM 
-  simulation by adopting a phenomenological gas density model for each cluster based on X-ray
-  measurements that matches Sunyaev-Zel'dovich and X-ray scaling relations and
-  luminosity function. 
-  ...
-  We make our cosmologically complete multi-frequency mock catalogs for 
-  the (non-)thermal cluster emission at different redshifts publicly and freely available on-line
-  through the MultiDark database.
+  {\bf We construct a phenomenological gas density model for the intra-cluster medium
+  based on X-ray inferred densities for cool-core and non cool-core clusters, and a 
+  cluster-mass-dependent gas fraction. We then build a mock galaxy cluster 
+  catalog from the large MultiDark $N$-body $\Lambda$CDM simulation by assigning
+  such a (mass-dependent) gas density profile to each dark matter halo in our sample, 
+  which is sorted into cool-core and non cool-core clusters according to a dynamical 
+  disturbance parameter. Our gas density model permits to match the observed 
+  Sunyaev-Zel'dovich and X-ray scaling relations and luminosity function. Therefore,
+  it can be reliable applied to make predictions for present and future instruments. 
+  We apply our catalogs to calculate non-thermal radio and gamma-ray emission of galaxy 
+  clusters in a companion paper. Eventually, we make our cosmologically complete multi-frequency 
+  mock catalogs for the (non-)thermal cluster emission at different redshifts publicly and freely 
+  available on-line through the MultiDark database.}
 \end{abstract}
@@
 \let\thefootnote\relax\footnotetext{$\dagger$ christoph.pfrommer@h-its.org}
-\let\thefootnote\relax\footnotetext{$\S$ fprada@iaa.es}
+\let\thefootnote\relax\footnotetext{$\S$ fprada@iaa.es\\}
 \endgroup
 
-{\bf Introduction...}
+{\bf The study of the (non-)thermal emission in galaxy clusters provides
+important information on structure formation process and on 
+fundamental characteristics of our Universe. This field is at a 
+crucial point of its development thanks to the very low sensitivity of present and future-generation 
+instruments such as LOFAR\footnote{www.lofar.org}, \emph{e}ROSITA\footnote{www.mpe.mpg.de/eROSITA}, 
+ASTRO-H\footnote{astro-h.isas.jaxa.jp} and CTA\footnote{www.cta-observatory.org}, to name but a few. 
+Therefore, it is important to provide prospects for future surveys and
+to understand in which way they can improve our current knowledge.
+To this end, a complete cosmological mock sample of galaxy
+clusters is needed. This can be realized either using analytical 
+expressions for the cluster mass function (e.g., \citealp{2001MNRAS.321..372J}) or cosmological cluster 
+simulations. In this work, we make use of the recent MultiDark $N$-body
+simulation (\citealp{2011arXiv1104.5130P}; www.multidark.org).
 
-%
-%dark matter (DM)  
-%
+Our main motivation to build such a mock catalog has been to predict the 
+non-thermal emission at radio frequencies of a cosmological 
+complete sample of galaxy clusters. This is presented in a companion 
+paper (\citealp{paper2}; hereafter Paper~II). As described in Paper~II, for 
+any given cluster, fundamental ingredients for the non-thermal emission 
+model are the mass and gas density distribution. The MultiDark 
+simulation used here is a $N$-body, \emph{dark matter (DM)-only} simulation and, 
+therefore, does not contain any information on the intra-cluster medium (ICM) gas  
+distribution. A cosmological complete sample of clusters can 
+only be obtained from $N$-body simulations as hydrodynamical
+simulations of such large volumes are computationally too expensive.
+Therefore, we need a method to determine the ICM properties
+of any given cluster from its total mass.
 
-{\bf Our original motivation to build such a mock catalog is to predict the 
-non-thermal emission at radio and gamma-ray frequencies of a cosmological 
-complete sample of galaxy clusters. This is presented in a companion 
-paper (REF, hereafter Paper~2).
-The two basic ingredients of the two works are an $N$-body, \emph{DM-only}
-cosmological simulation that we use in constructing our complete cluster sample,
-and the (non-)thermal emission model. Here, we use the MultiDark simulation that
-will be described in Section~\ref{sec:2}, along with our final cluster sample. As described 
-in Paper~2, for any given cluster, the necessary ingredients for the non-thermal emission 
-model are mass, temperature, and gas density distribution. We assign to
-each cluster in that simulation a gas density profile that is phenomenologically
-constructed from state-of-art X-ray observations, as will be shown in
-Section~\ref{sec:3}. In Section~4 and 5, we will show that this approach can successfully
-reproduce the known X-ray cluster characteristics, such as the X-ray luminosity
-function (XLF), the luminosity-mass relation, $L_{\rmn{X}}- M$, and the
-$Y_{\rmn{X}}-M$ relation, where $Y_{\rmn{X}}=M_\rmn{gas}k_{\rmn{B}}T$ with an
-X-ray-derived gas mass $M_{\rmn{gas}}$ and temperature $T$
-\citep{2006ApJ...650..128K}. Moreover, we compare our $Y_{\rmn{SZ}}-M$ relation
-with SZ-derived measurements. Only if our model matches available cluster data
-on the gas properties, we can safely use it in Paper~2.} In this work, the cluster mass $M_{\Delta}$ 
-and radius $R_{\Delta}$ are defined with respect to a density that is $\Delta=200$ or 
-$\Delta=500$ times the \emph{critical} density of the Universe. We adopt density 
-parameters of $\Omega_{\rmn{m}}=0.27$, $\Omega_{\Lambda}=0.73$ and today's 
-Hubble constant of $H_0 = 100 \times h_{70}$~km~s$^{-1}$~Mpc$^{-1}$ where $h_{70} = 0.7$.
+The simplest approach is to assume that clusters are self-similar with 
+the thermal properties determined by their mass \citep{1986MNRAS.222..323K}.
+However, X-ray observations showed that clusters are extremely 
+complex systems. In fact, we know that self-similarity is broken, especially at 
+low-mass scales (see \citealp{2005RvMP...77..207V} for a review).
+The study of the thermodynamical condition of clusters is crucial 
+to understand how self-similarity is broken. One possible solution 
+is, for example, energy feedback from active galactic nuclei (e.g.,
+\citealp{2013arXiv1303.5443P}).
+
+In order to build a cluster sample with realistic ICM densities, we 
+adopt a \emph{phenomenological} approach and construct our density 
+profiles from X-ray observations. We then compare the characteristics of 
+the clusters in our mock sample to observational results. We study the X-ray 
+luminosity function (XLF), the luminosity-mass relation, $L_{\rmn{X}}- M$, and 
+the $Y_{\rmn{X}}-M$ relation, where $Y_{\rmn{X}}=M_\rmn{gas}k_{\rmn{B}}T$ 
+with an X-ray-derived gas mass $M_{\rmn{gas}}$ and temperature $T$
+\citep{2006ApJ...650..128K}. Moreover, we consider the thermal 
+Sunyaev-Zel’dovich (SZ) effect and compare our $Y_{\rmn{SZ}}-M$ 
+relation with recent SZ-derived measurements. Only if our model matches
+available cluster data on the gas properties, we can safely use it in Paper~II
+and be sure that we will obtain realistic predictions.
+The final result is a complete cosmological cluster mock catalog, at
+different redshifts, containing information on the DM and ICM properties 
+of each object, together with its (non-)thermal emission at different 
+frequencies. This mock catalog reproduces existing observations
+and is useful in making predictions for future surveys.
+
+In next Section~\ref{sec:2}, we introduce the MultiDark simulation
+along with our final cluster sample. We assign to each of our clusters  
+the phenomenologically constructed gas density profile in 
+Section~\ref{sec:3}. In Sections~\ref{sec:4} and 
+\ref{sec:5}, we show that this approach can successfully reproduce 
+the known X-ray and SZ cluster characteristics. We present the
+resulting mock cluster catalogs in Section~\ref{sec:6}, and eventually 
+summarize our conclusions in Section~\ref{sec:7}.
+In this work, the cluster mass $M_{\Delta}$ and radius $R_{\Delta}$ are defined 
+with respect to a density that is $\Delta=200$ or $\Delta=500$ times the \emph{critical} 
+density of the Universe. We adopt density parameters of $\Omega_{\rmn{m}}=0.3$, 
+$\Omega_{\Lambda}=0.7$ and today's Hubble constant of 
+$H_0 = 100 \times h_{70}$~km~s$^{-1}$~Mpc$^{-1}$ where $h_{70} = 0.7$.
+}
 
@@
 code \citep{1997ApJS..111...73K} of $2048^3$ particles within a ($1000$~Mpc~$h^{-1}$)$^3$ 
-cube. The adopted cosmological parameters are $\Omega_{\rmn{m}}=0.27$, $\Omega_{\Lambda}=0.73$,
-$\Omega_\rmn{b}=0.0469$, $n_\rmn{s}=0.95$, $h=0.7$ and $\sigma_8=0.82$. This simulation is 
+cube. {\bf The adopted cosmological parameters are $\Omega_{\rmn{m}}=0.27$, $\Omega_{\Lambda}=0.73$,
+$\Omega_\rmn{b}=0.0469$, $n_\rmn{s}=0.95$, $h=0.7$ and $\sigma_8=0.82$.} This simulation is 
 particularly well suited for our purpose because of its large 
@@
 
-We use the MultiDark halo catalog from its on-line database,\footnote{www.multidark.org.} 
-constructed with the Bound Density Maxima algorithm \citep{1997astro.ph.12217K}.  
+We use the MultiDark halo catalog from its on-line database,\footnote{www.multidark.org} 
+constructed with the Bound Density Maxima (BDM) algorithm \citep{1997astro.ph.12217K}.  
 We will mainly use $M_{500}$ and $R_{500}$ for comparison with existing observational works.  
@@
 
-{\bf In Paper~2, we present predictions for the LOFAR radio observatory
+{\bf In Paper~II, we present predictions for the LOFAR radio observatory
 which is expected to detect diffuse radio emission in clusters up to redshift $z \approx 1$ (e.g.,
-\citealp{2012JApA..tmp...34R}).} 
-Thus, we make use of different simulation snapshots up to $z=1$. 
+\citealp{2012JApA..tmp...34R}).} Thus, we make use of different simulation snapshots up to $z=1$. 
 {\bf The extrapolation of our model beyond this redshift is rather uncertain as it is based
-on observations at low(er) redshift.}
-In Table~\ref{tab:z}, we show the total cluster number in our final cluster sample at different redshifts.
+on observations at low(er) redshift.} In Table~\ref{tab:z}, we show the total cluster number in 
+our final cluster sample at different redshifts.
 
@@
 Fig.~\ref{fig:gas_profiles}, we show the 31 electron density profiles of the
-REXCESS sample color-coded by CCCs and NCCCs.
+REXCESS sample color-coded by non cool-core clusters (NCCCs) and 
+cool-core clusters (CCCs).
 
@@
 \includegraphics[width=0.48\textwidth]{figures/gas_profiles.eps}
-\caption{Electron density profiles of the 31 clusters in the REXCESS sample.
-Grey and black lines represent NCCCs and CCCs, respectively.
-The blue and red lines represent our GNFW mean profile for the NCCCs and CCCs, respectively.}
+\caption{Electron density profiles of the 31 clusters in the REXCESS sample. Grey and black lines represent 
+NCCCs and CCCs, respectively. The blue and red lines represent our GNFW mean profile for the NCCCs and CCCs, respectively.}
 \label{fig:gas_profiles}
@@
 %\includegraphics[width=0.33\textwidth]{figures/sz_m.eps}
-\caption{X-ray scaling relations. Grey triangles show the MultiDark
+\caption{{\bf X-ray scaling relations. Grey triangles show the MultiDark
   sample (limited to the mass range covered by observations), the black line is
@@
   \emph{Right.} $Y_{\rmn{X}}-M_{500}$ scaling relation of our model in comparison to the
-  observational sample by \protect\cite{2010MNRAS.406.1773M}.} 
+  observational sample by \protect\cite{2010MNRAS.406.1773M}.}} 
   %\emph{Right.} $Y_{\rmn{SZ}}-M_{500}$ scaling relation at $z=0.2$ in comparison
@@
 \cite{2013arXiv1303.5080P}. {\bf We compare with the result obtained from the 
-\emph{Planck} COSMO sample with Malmquist bias correction (see their Table~A.1),
+\emph{Planck} COSMO sample with Malmquist bias correction,
 which has a median redshift of $0.18$. Hence, we compare the data to our relation 
@@
 \includegraphics[width=0.48\textwidth]{figures/sz_m.eps}
-\caption{SZ scaling relations. Grey triangles show the MultiDark
-  sample (limited to the mass range covered by observations), the black line is
-  the corresponding scaling relation, and the blue line is the
-  observational result. The black crosses represent the median values of the
-  quantity in question for a given mass bin (indicated by horizontal error
-  bars), and the vertical error bars represent the standard deviation within a
-  bin.  \emph{Left.} We compare the bolometric X-ray luminosity-to-mass
-  relation, $L_{\rmn{bol}}-M_{500}$, at $z=0.2$ to the observational sample by
-  \protect\cite{2010MNRAS.406.1773M} with a median of $z \approx 0.2$. 
-  \emph{Right.} $Y_{\rmn{X}}-M_{500}$ scaling relation of our model in comparison to the
-  observational sample by \protect\cite{2010MNRAS.406.1773M}. 
-  \emph{Left.} $Y_{\rmn{SZ}}-M_{500}$ scaling relation at $z=0.2$ in comparison
-  to the observational sample by the \protect\cite{2013arXiv1303.5080P} with a 
-  median redshift of about $0.18$. The bottom panels show the relative difference to
-  the observational scaling relations.}
+\caption{{\bf SZ scaling relation of our sample at $z=0.2$ in comparison to the observational 
+  sample by \protect\cite{2013arXiv1303.5080P} with a median redshift of about $0.18$.
+  Grey triangles show the MultiDark sample (limited to the mass range covered by observations), 
+  the black line is the corresponding scaling relation, and the blue line is the observational result. 
+  The black crosses represent the $Y_{\rmn{SZ}}$ median values of our sample for a given mass bin (indicated by 
+  horizontal error bars), and the vertical error bars represent the standard deviation within a
+  bin. The bottom panels show the relative difference to the observational scaling relations.}}
 \label{fig:SZ_M}
@@
 \includegraphics[width=0.48\textwidth]{figures/sz_m_ACT.eps}
-\caption{SZ scaling relations. Grey triangles show the MultiDark
-  sample (limited to the mass range covered by observations), the black line is
-  the corresponding scaling relation, and the blue line is the
-  observational result. The black crosses represent the median values of the
-  quantity in question for a given mass bin (indicated by horizontal error
-  bars), and the vertical error bars represent the standard deviation within a
-  bin.  \emph{Left.} We compare the bolometric X-ray luminosity-to-mass
-  relation, $L_{\rmn{bol}}-M_{500}$, at $z=0.2$ to the observational sample by
-  \protect\cite{2010MNRAS.406.1773M} with a median of $z \approx 0.2$. 
-  \emph{Right.} $Y_{\rmn{X}}-M_{500}$ scaling relation of our model in comparison to the
-  observational sample by \protect\cite{2010MNRAS.406.1773M}. 
-  \emph{Left.} $Y_{\rmn{SZ}}-M_{500}$ scaling relation at $z=0.2$ in comparison
-  to the observational sample by the \protect\cite{2013arXiv1303.5080P} with a 
-  median redshift of about $0.18$. The bottom panels show the relative difference to
-  the observational scaling relations.}
+\caption{{\bf SZ scaling relation of our sample at $z=0.61$ compared with the SPT and ACT results. 
+  Triangles show the MultiDark sample (limited to the mass range covered by observations) 
+  while the crosses represent the observational result. \emph{Left.} Comparison with the 
+  SPT sample \protect\citep{2013ApJ...763..127R} color-coded by redshift. 
+  $Y_{\rmn{SZ, SPT}}$ is given within an aperture of  $0.2$~h$_{70}^{-1}$~Mpc.
+  \emph{Right.} Comparison with the ACT sample \protect\citep{2013JCAP...07..008H} color-coded 
+  by redshift. $Y_{\rmn{SZ, ACT}}$ is given within an aperture of $0.42$~h$_{70}^{-1}$~Mpc.}}
 \label{fig:SZ_M_1}
@@
 
-{\bf We additionally compare our $Y_{\rmn{SZ}}$ to the results from the South Pole Telescope (SPT) 
-and Atacama Cosmology Telescope (ACT) surveys.
-We select a subsample of SPT clusters from \cite{2013ApJ...763..127R}, formed by the
-115 objects with confirmed redshift and signal-to-noise above 5, which has a median
-redshift of 0.56 with rms of 0.27. \cite{2013ApJ...763..127R} provide $Y_{\rmn{SZ}}$ 
+{\bf We additionally compare our $Y_{\rmn{SZ}}$ to the results from the South Pole 
+Telescope (SPT) and Atacama Cosmology Telescope (ACT) surveys.
+We select a subsample of SPT clusters from \cite{2013ApJ...763..127R} by taking
+only objects with confirmed redshift and signal-to-noise $\ge 5$. The resulting sample 
+consists of 115 clusters with a median redshift of 0.56 and rms 0.27. Note the much larger 
+scatter in redshift of the SPT sample with respect to the \emph{Planck} one that has 
+a rms of 0.11. \cite{2013ApJ...763..127R} provide $Y_{\rmn{SZ}}$ 
 within an aperture of $1'$, corresponding to a median radius of $0.2$~h$_{70}^{-1}$~Mpc 
@@
 
-In the left panel of Fig.~\ref{fig:SZ_M_1}, we compare the SPT cluster subsample to our 
-scaling relation at the three different MutliDark snapshots of $z = 0.4$, $0.61$ 
-and $0.78$. We color-coded the SPT clusters in order to show that the SPT 
+In the left panel of Fig.~\ref{fig:SZ_M_1}, we compare the SPT cluster sample to our 
+scaling relation at $z = 0.61$. We color-coded the SPT clusters in order to show that the SPT 
 selection function is nearly redshift-independent. The fact that the angular size of galaxy clusters 
 decreases with redshift is an advantage for SPT due to its small beam, in fact, higher-redshift clusters 
-are less confused by primary CMB fluctuations. This effect is inverse for \emph{Planck} due to its
-larger beam. We can conclude that while our $Y_{\rmn{SZ}}-M_{500}$ scaling relation 
-compare fairly well to the median SPT cluster population, the SPT sample has a too
+are less confused by primary CMB fluctuations \citep{2013ApJ...763..127R}. This effect is inverse 
+for \emph{Planck} due to its larger beam. We can conclude that while our $Y_{\rmn{SZ}}-M_{500}$ 
+scaling relation compare well to the median SPT cluster population, the SPT sample has a too
 large scatter to be well represented by single MultiDark snapshots.
@@
 the ACT sample overlapping with the Sloan Digital Sky Survey stripe 82 
-(\citealp{2013JCAP...07..008H}; we use the quantities inferred from the
-universal pressure profile scaling relation).
-The sample has a median redshift of 0.58 with rms of 0.28.
-\cite{2013JCAP...07..008H} provides $Y_{\rmn{SZ}}$ within $R_{500}$ which
-median, $0.42$~h$_{70}^{-1}$~Mpc, is, however, almost half of ours at the
+\citep{2013JCAP...07..008H}. This sample has a median redshift of 0.58 with rms 
+of 0.28. \cite{2013JCAP...07..008H} provides $Y_{\rmn{SZ}}$ within $R_{500}$, which
+median, $0.42$~h$_{70}^{-1}$~Mpc, is almost half of ours at the
 MultiDark snapshot $z=0.61$. Therefore, we use an aperture of $0.42$~h$_{70}^{-1}$~Mpc
-to calculate our $Y_{\rmn{SZ, ACT}}$. Also in this case we can conclude
-that our mock sample reproduce fairly well the median observational sample. 
-Note, however, the very different scatter of SPT and ACT samples.}
+to calculate our $Y_{\rmn{SZ, ACT}}$. 
+The fact that our $R_{500}$ does not compare well with the ACT values, while it does with 
+\emph{Planck}, may be explained as follows. We adopt the ACT measurements derived from 
+the 148~GHz data assuming that the cluster pressure is described by the universal 
+profile of \cite{2010A&A...517A..92A}. In contrast, \cite{2013arXiv1303.5080P}
+derived $R_{500}$ from X-ray measurements of $M_{500}$, similarly to
+our approach of constructing gas densities from an X-ray sample of clusters.
+
+Summarizing, our SZ scaling relations compare very well to the result from
+the \emph{Planck} collaboration. However, the comparison with the SPT and 
+ACT samples is not as straightforward due to the different selection function 
+of these telescopes with respect to \emph{Planck}, which results in a much
+more (redshift) non-homogenous sample. Nevertheless, our mock clusters 
+can reproduce well the median SPT and ACT populations. A more detailed
+comparison would need the generation of light-cone mock catalogs,
+including instrumental effects, which is beyond the scope of this 
+work.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Multi-frequency Mock Catalogs}
+\label{sec:6}
+
+{\bf As a final product of this work, we construct cosmological complete mock catalogs of galaxy clusters, at the different redshifts of 
+Table~\ref{tab:z}, for $M_{200}\geq1\times10^{14}$~$h^{-1}$~M$_{\odot}\approx1.4\times10^{14}$~$h_{70}^{-1}$~M$_{\odot}$.
+We make these catalogs publicly available through the MultiDark database 
+(www.multidark.org) where we will also post possible updates.
+
+Our catalogs contain all the information regarding the DM properties of each object as 
+given by the corresponding original MultiDark BDM halo catalogs. Additionally, we include the
+following information:
+
+\begin{itemize}
+\item $M_{500}$ and $R_{500}$ calculated from $M_{200}$ and $R_{200}$ of the BDM catalogs with the \cite{2003ApJ...584..702H} method,
+\item the ICM X-ray temperature assigned via the $T_{\rmn{ci}}-M_{500}$ relation by \cite{2010MNRAS.406.1773M},
+\item a state flag identifying the cluster as NCCC or CCC as described in Section~\ref{sec:3},
+\item the central gas density $\rho_{\rmn{gas},0}$ with which the full ICM radial profile can be calculated as in Section~\ref{sec:3},
+\item the bolometric X-ray thermal bremsstrahlung luminosity $L_{\rmn{X, bol}}$ within $R_{500}$,
+\item the $Y_{\rmn{X}}$ and $Y_{\rmn{SZ}}$ parameters within $R_{500}$.
+\end{itemize}
+
+In Paper~II, we present a model to calculate the possible radio and gamma-ray emission of 
+clusters as result of the cosmic-ray (CR) proton-proton interactions with the ICM. We refer
+to that paper for all the details. However, we want to point out that our mock catalogs include also:
+
+\begin{itemize}
+\item a state flag identifying whether a given object is a radio-loud or a radio-quiet cluster, 
+\item the CR-to-thermal pressure averaged over the cluster volume within $R_{500}$,
+\item the synchrotron radio luminosity, within $R_{500}$, at 120~MHz and 1.4~GHz,
+\item the gamma-ray luminosity, within $R_{500}$, above 100~MeV and 100~GeV.
+\end{itemize}
+
+We warn, however, that our mock catalogs are not appropriate for all purposes. In fact, they are 
+representations of the average cluster population. While they are very useful as baseline for new 
+simulations, to test new observations, and for the non-thermal modeling of clusters, they are not 
+appropriate to perform detailed cosmology studies. A carefully modeling of the response function 
+of the considered instrument would be needed for such a purpose, together with the generation of 
+light-cone mock catalogs. Nevertheless, for flux-complete surveys, our mock catalogs are
+certainly good tools to test against models. Finally, keep also in mind that our approach is based on 
+X-ray observations of clusters at low redshift \citep{2008A&A...487..431C,2009ApJ...693.1142S}, 
+and, for simplicity, we adopted a self-similar redshift evolution.
+}
 
@@
 \section{Conclusions}
-\label{sec:6}
-
-{\bf Discussion...}
+\label{sec:7}
 
@@
 according to a dynamical disturbance parameter that is calculated from the DM distribution.
-With this model, we obtain a cosmologically complete mock catalog of galaxy
-clusters that matches the observed $L_{\rmn{X, bol}}$-to-$M_{500}$,
-$Y_{\rmn{X}}$-to-$M_{500}$, and $Y_{\rmn{SZ}}$-to-$M_{500}$ relations, as well
-as the X-ray luminosity function. We apply it in the companion Paper~2 to 
-predict the radio and gamma-ray emission of our sample.
+We obtain cosmologically complete mock catalogs of galaxy clusters that matches the 
+observed $L_{\rmn{X, bol}}$-to-$M_{500}$, $Y_{\rmn{X}}$-to-$M_{500}$, and 
+$Y_{\rmn{SZ}}$-to-$M_{500}$ relations, as well as the X-ray luminosity function. 
+In the companion Paper~II, we additionally calculate the possible radio and gamma-ray 
+emission coming from the CR hadronic interactions with the ICM in the clusters.
 
@@
 cluster emission at different redshifts. We make these catalogs publicly and freely available 
-on-line through the MultiDark database (www.multidark.org). Those contain the quantities
-$\rho_{\rmn{gas}}$, $L_{\rmn{X, bol}}$, $Y_{\rmn{X}}$, $Y_{\rmn{SZ}}$, $L_{120~\rmn{MHz}}$, 
-$L_{1.4~\rmn{GHz}}$, $L_{>100~\rmn{MeV}}$ and $L_{>100~\rmn{GeV}}$ (among many others). 
-We hope that the community can make valuable use of these catalogues in synergy with the future 
-radio, X-ray and gamma-ray data.}
+on-line through the MultiDark database (www.multidark.org). We warn that these catalogs
+are not appropriate for detailed cosmological studies in their (present) published form as 
+carefully modeling of the response function of the considered instrument would be needed 
+for such a purpose, together with the generation of light-cone mock catalogs. Note also that 
+our approach is based on X-ray observations at low redshift, and we adopted a self-similar redshift 
+evolution. Nevertheless, our mock catalogs are good representations of the average cluster population,
+and we hope that the  community can make valuable use of these catalogs in synergy with the future radio, 
+X-ray and gamma-ray data.}
 
@@
 \section*{Acknowledgments}
-We thank Anders Pinzke for many useful discussions. We also thank Harald Ebeling, 
-Stefan Gottl{\"o}berg, Anatoly Klypin, Andrey Kravtsov, Adam Mantz, Frazer Pearce, 
-Jos\'e Alberto Rubi\~no, and Gustavo Yepes, for the useful discussions and advices. 
-Finally, we thank the MultiDark database people, in particular Adrian Partl and Kristin Riebe. 
+We thank Harald Ebeling, Stefan Gottl{\"o}berg, Anatoly Klypin, Andrey Kravtsov, Adam Mantz, 
+Frazer Pearce, Jos\'e Alberto Rubi\~no, and Gustavo Yepes, for the useful discussions and advices. 
+We also thank the MultiDark database people, in particular Adrian Partl and Kristin Riebe. 
 F.Z.{\ }acknowledges the CSIC financial support as a JAE-Predoc grant of the 

### 2013-09-23 paper1.tex
added X-ray subsections

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{X-ray scaling relations and luminosity function}
+\section{X-ray  observables}
 \label{sec:4}
 
-In order to check whether our phenomenologically derived gas profiles reproduce
-the observations, we calculate the bolometric thermal bremsstrahlung
-luminosity $L_{\rmn{bol}}$ as in \cite{1988xrec.book.....S}\footnote{We check
-  our procedure by fitting each of the 31 REXCESS clusters with
+So far, we used a well-observed representative sample of X-ray clusters
+(REXCESS) that was supplemented by X-ray data on gas mass fractions to construct
+our phenomenological gas model.  Here, we will test how our cluster mock data
+compares to various X-ray inferred observables. Those include the observed
+$L_{\rmn{bol}} - M_{500}$ relation, the $Y_X - M_{500}$ relation, and the
+XLF.
+
+\subsection{Scaling Relations}
+
+First, we calculate the bolometric thermal bremsstrahlung luminosity
+$L_{\rmn{bol}}$ following \cite{1988xrec.book.....S}.\footnote{We check our
+  procedure by fitting each of the 31 REXCESS clusters with
   equation~(\ref{eq:gnfw}) and calculating $L_{\rmn{bol}}$ with the measured gas
@@
   line emission which may give a noticeable contribution, in particularly for
-  low-mass clusters and in the cluster outskirts of larger systems.}  and
-compare our sample result with the observed $L_{\rmn{bol}} - M_{500}$ relation
-and XLF.\footnote{The mean (median) difference at $z=0$ between
-  $L_{\rmn{bol}}$ within $R_{200}$ or within $R_{500}$ is $\approx 5\%$ ($\approx
-  7\%$). While $L_{\rmn{bol}}$ refers to the quantity calculated within
-  $R_{500}$, we note that the XLF for luminosities calculated within $R_{200}$
-  will be barely changed.}
-
-To assign a temperature to our model clusters (that is needed for calculating
+  low-mass clusters and in the cluster outskirts of larger systems.}  To assign
+a temperature to our model clusters (that is needed for calculating
 $L_{\rmn{bol}}$ and $Y_{\rmn{X}}$), we adopt the $T-M_{500}$ relation by
@@
 
-\subsection{X-ray Luminosity Function}
+\subsection{Luminosity Functions}
 Studies of the XLF got out of fashion during the last years due to the
@@
 emissivity scales with the square of the gas density, which makes it subject to
-density variations and clumping. This implies large scatter that causes a large
-Malmquist bias and underlines the necessity of careful mock surveys that need to
-address all systematics.
+density variations and clumping.\footnote{The mean (median) difference at $z=0$
+  between $L_{\rmn{bol}}$ within $R_{200}$ or within $R_{500}$ is $\approx 5\%$
+  ($\approx 7\%$). While $L_{\rmn{bol}}$ refers to the quantity calculated
+  within $R_{500}$, we note that the XLF for luminosities calculated within
+  $R_{200}$ will be barely changed.} This implies large scatter that causes a
+large Malmquist bias and underlines the necessity of careful mock surveys that
+need to address all systematics.
 

### 2013-09-24 paper1.tex
abstract rewritten

@@
 \author[F. Zandanel, C. Pfrommer and F. Prada]{
-Fabio Zandanel$^{1,2 *}$, Christoph Pfrommer$^{3 \dagger}$ and Francisco Prada$^{4,5,1 \S}$\\
+Fabio Zandanel$^{1,2 *}$, Christoph Pfrommer$^{3}$ and Francisco Prada$^{4,5,1}$\\
 $^{1}$Instituto de Astrof\'{\i}sica de Andaluc\'{\i}a (CSIC), Glorieta de la Astronom\'{\i}a, E-18080 Granada, Spain\\
@@
 \begin{abstract}
-  {\bf We construct a phenomenological gas density model for the intra-cluster medium
-  based on X-ray inferred densities for cool-core and non cool-core clusters, and a 
-  cluster-mass-dependent gas fraction. We then build a mock galaxy cluster 
-  catalog from the large MultiDark $N$-body $\Lambda$CDM simulation by assigning
-  such a (mass-dependent) gas density profile to each dark matter halo in our sample, 
-  which is sorted into cool-core and non cool-core clusters according to a dynamical 
-  disturbance parameter. Our gas density model permits to match the observed 
-  Sunyaev-Zel'dovich and X-ray scaling relations and luminosity function. Therefore,
-  it can be reliable applied to make predictions for present and future instruments. 
-  We apply our catalogs to calculate non-thermal radio and gamma-ray emission of galaxy 
-  clusters in a companion paper. Eventually, we make our cosmologically complete multi-frequency 
-  mock catalogs for the (non-)thermal cluster emission at different redshifts publicly and freely 
-  available on-line through the MultiDark database.}
+  Cosmological hydrodynamical simulations of galaxy clusters are still
+  challenged to obtain a model for the intracluster medium that matches all
+  aspects of current X-ray and Sunyaev-Zel'dovich observations. To facilitate
+  such comparisons with future simulations and to enable realistic cluster
+  population studies for modeling e.g., non-thermal emission processes, we
+  construct a phenomenological model for the intracluster medium that is based
+  on a representative sample of X-ray clusters. We create a mock galaxy cluster
+  catalog by assigning our gas density model to each cluster halo of the large
+  collisionless $N$-body simulation {\em MultiDark}, which employs a $\Lambda$
+  cold dark matter cosmology. Our clusters are identified with cool-core and non
+  cool-core clusters according to a dynamical disturbance parameter. We
+  demonstrate that our gas model matches the various observed Sunyaev-Zel'dovich
+  and X-ray scaling relations as well as the X-ray luminosity function, thus
+  enabling a reliable mock catalog for present and future instruments.  In a
+  companion paper, we apply our catalogs to calculate non-thermal radio and
+  gamma-ray emission of galaxy clusters. We make our cosmologically complete
+  multi-frequency mock catalogs for the (non-)thermal cluster emission at
+  different redshifts publicly and freely available online through the MultiDark
+  database.
 \end{abstract}
@@
 \let\thefootnote\relax\footnotetext{* f.zandanel@uva.nl}
-\let\thefootnote\relax\footnotetext{$\dagger$ christoph.pfrommer@h-its.org}
-\let\thefootnote\relax\footnotetext{$\S$ fprada@iaa.es\\}
 \endgroup
 
-{\bf The study of the (non-)thermal emission in galaxy clusters provides
+The study of the (non-)thermal emission in galaxy clusters provides
 important information on structure formation process and on 
@@
 $H_0 = 100 \times h_{70}$~km~s$^{-1}$~Mpc$^{-1}$ where $h_{70} = 0.7$.
-}
 

### 2013-09-24 paper1.tex
intro written

@@
 %MNRAS
-\title[A Phenomenological Model for the Intra-Cluster Medium]{A Phenomenological Model for the Intra-Cluster Medium that matches X-ray and Sunyaev-Zel'dovich observations}
+\title[A Phenomenological Model for the Intracluster Medium]{A Phenomenological Model for the Intracluster Medium that matches X-ray and Sunyaev-Zel'dovich observations}
 \author[F. Zandanel, C. Pfrommer and F. Prada]{
-Fabio Zandanel$^{1,2 *}$, Christoph Pfrommer$^{3}$ and Francisco Prada$^{4,5,1}$\\
-$^{1}$Instituto de Astrof\'{\i}sica de Andaluc\'{\i}a (CSIC), Glorieta de la Astronom\'{\i}a, E-18080 Granada, Spain\\
-$^{2}$now at GRAPPA Institute, University of Amsterdam, Science Park 904, 1098XH Amsterdam, Netherlands\\
-$^{3}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany\\
+Fabio Zandanel$^{1,2}$, Christoph Pfrommer$^{3}$ and Francisco Prada$^{4,5,1}$\\
+$^{1}$GRAPPA Institute, University of Amsterdam, Science Park 904, 1098XH Amsterdam, Netherlands, f.zandanel@uva.nl\\
+$^{2}$Instituto de Astrof\'{\i}sica de Andaluc\'{\i}a (CSIC), Glorieta de la Astronom\'{\i}a, E-18080 Granada, Spain\\
+$^{3}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany, christoph.pfrommer@h-its.org\\
 $^{4}$Campus of International Excellence UAM+CSIC, Cantoblanco, E-28049 Madrid, Spain\\
@@
 \begin{abstract}
-  Cosmological hydrodynamical simulations of galaxy clusters are still
-  challenged to obtain a model for the intracluster medium that matches all
+  {\bf Cosmological hydrodynamical simulations of galaxy clusters are still
+    challenged to produce a model for the intracluster medium that matches all
     aspects of current X-ray and Sunyaev-Zel'dovich observations. To facilitate
@@
     construct a phenomenological model for the intracluster medium that is based
-  on a representative sample of X-ray clusters. We create a mock galaxy cluster
-  catalog by assigning our gas density model to each cluster halo of the large
-  collisionless $N$-body simulation {\em MultiDark}, which employs a $\Lambda$
-  cold dark matter cosmology. Our clusters are identified with cool-core and non
-  cool-core clusters according to a dynamical disturbance parameter. We
-  demonstrate that our gas model matches the various observed Sunyaev-Zel'dovich
-  and X-ray scaling relations as well as the X-ray luminosity function, thus
-  enabling a reliable mock catalog for present and future instruments.  In a
-  companion paper, we apply our catalogs to calculate non-thermal radio and
-  gamma-ray emission of galaxy clusters. We make our cosmologically complete
-  multi-frequency mock catalogs for the (non-)thermal cluster emission at
-  different redshifts publicly and freely available online through the MultiDark
-  database.
+    on a representative sample of X-ray clusters. We create a mock galaxy
+    cluster catalog by assigning our gas density model to each cluster halo of
+    the large collisionless $N$-body simulation {\em MultiDark}. Our clusters
+    are identified with cool-core and non cool-core clusters according to a
+    dynamical disturbance parameter. We demonstrate that our gas model matches
+    the various observed Sunyaev-Zel'dovich and X-ray scaling relations as well
+    as the X-ray luminosity function, thus enabling a reliable mock catalog for
+    present and future instruments.  In a companion paper, we apply our catalogs
+    to calculate non-thermal radio and gamma-ray emission of galaxy clusters. We
+    make our cosmologically complete multi-frequency mock catalogs for the
+    (non-)thermal cluster emission at different redshifts publicly and freely
+    available online through the MultiDark database.}
 \end{abstract}
@@
 
-The study of the (non-)thermal emission in galaxy clusters provides
-important information on structure formation process and on 
-fundamental characteristics of our Universe. This field is at a 
-crucial point of its development thanks to the very low sensitivity of present and future-generation 
-instruments such as LOFAR\footnote{www.lofar.org}, \emph{e}ROSITA\footnote{www.mpe.mpg.de/eROSITA}, 
-ASTRO-H\footnote{astro-h.isas.jaxa.jp} and CTA\footnote{www.cta-observatory.org}, to name but a few. 
-Therefore, it is important to provide prospects for future surveys and
-to understand in which way they can improve our current knowledge.
-To this end, a complete cosmological mock sample of galaxy
-clusters is needed. This can be realized either using analytical 
-expressions for the cluster mass function (e.g., \citealp{2001MNRAS.321..372J}) or cosmological cluster 
-simulations. In this work, we make use of the recent MultiDark $N$-body
-simulation (\citealp{2011arXiv1104.5130P}; www.multidark.org).
+{\bf  Galaxy clusters are the rarest and largest gravitationally-collapsed
+objects in the Universe and form at sites of constructive interference of long
+waves in the primordial density fluctuations. Clusters reach radial extends of a
+few Mpc and total masses $M \sim (10^{14} - 10^{15}) M_{\odot}$, of which
+galaxies, hot ($1-10$~keV) gas and dark matter (DM) contribute roughly for 5, 15
+and 80\%, respectively. If the thermal properties of the intracluster medium
+(ICM) were solely determined by the gravity of the DM potential wells, then
+cluster would obey self-similar scaling relations \citep{1986MNRAS.222..323K}.
+However, X-ray observations have demonstrated that self-similarity is broken,
+especially at low-mass scales (see e.g., \citealp{2005RvMP...77..207V} for a
+review). Apparently the energy input from non-gravitational processes associated
+with galaxy formation have a larger influence in smaller systems, i.e., at
+scales of galaxy groups.
 
-Our main motivation to build such a mock catalog has been to predict the 
-non-thermal emission at radio frequencies of a cosmological 
-complete sample of galaxy clusters. This is presented in a companion 
-paper (\citealp{paper2}; hereafter Paper~II). As described in Paper~II, for 
-any given cluster, fundamental ingredients for the non-thermal emission 
-model are the mass and gas density distribution. The MultiDark 
-simulation used here is a $N$-body, \emph{dark matter (DM)-only} simulation and, 
-therefore, does not contain any information on the intra-cluster medium (ICM) gas  
-distribution. A cosmological complete sample of clusters can 
-only be obtained from $N$-body simulations as hydrodynamical
-simulations of such large volumes are computationally too expensive.
-Therefore, we need a method to determine the ICM properties
-of any given cluster from its total mass.
+The central cooling time of the X-ray emitting gas in galaxy clusters and groups
+is bimodally distributed. Approximately half of all systems have radiative
+cooling times of less than 1~Gyr and establish a population of cool core (CC)
+clusters while some others have cooling times that are longer than the age of
+the Universe, forming the non-cool core (NCC) cluster population
+\citep{2009ApJS..182...12C,2010A&A...513A..37H}. Several physical processes have
+been proposed to be responsible for balancing radiative cooling of the
+low-entropy gas at the centers of CCs. In particular the self-regulated nature
+of the proposed feedback and observational correlations between radio activity
+and central entropy (which is a proxy for a small cooling time) have put
+feedback by active galactic nuclei (AGN) into the focus of recent research
+\citep{2007ARA&A..45..117M, 2012NJPh...14e5023M}. The underlying physical
+processes responsible for the heating include dissipation of mechanical heating
+by outflows, lobes, or sound waves from the central AGN
+\citep[e.g.,][]{2001ApJ...554..261C, 2002Natur.418..301B, 2002ApJ...581..223R}
+or cosmic-ray heating: streaming cosmic rays excite Alfv\'en waves on which they
+resonantly scatter \citep{1969ApJ...156..445K}.  Damping of these waves
+transfers cosmic ray energy and momentum to the cooling plasma
+\citep{1991ApJ...377..392L, 2008MNRAS.384..251G, 2011A&A...527A..99E,
+  2013MNRAS.434.2209W}, heating it at a rate that balances radiative cooling on
+average at each radius \citep{2013arXiv1303.5443P}.
 
-The simplest approach is to assume that clusters are self-similar with 
-the thermal properties determined by their mass \citep{1986MNRAS.222..323K}.
-However, X-ray observations showed that clusters are extremely 
-complex systems. In fact, we know that self-similarity is broken, especially at 
-low-mass scales (see \citealp{2005RvMP...77..207V} for a review).
-The study of the thermodynamical condition of clusters is crucial 
-to understand how self-similarity is broken. One possible solution 
-is, for example, energy feedback from active galactic nuclei (e.g.,
-\citealp{2013arXiv1303.5443P}).
+Modeling the formation and evolution of clusters with cosmological
+hydrodynamical simulations has been progressively refined over the last years to
+also include (subresolution models for) AGN feedback
+\citep[e.g.,][]{2007MNRAS.380..877S, 2008MNRAS.387.1403S, 2008ApJ...687L..53P,
+  2012MNRAS.420.2662D, 2012MNRAS.424..190G, 2013MNRAS.428.2366V}. While the
+comparison to data and simulations with AGN feedback improved for integrated
+thermal properties of large cluster samples
+\citep{2012ApJ...758...74B,2012ApJ...758...75B}, there are still notable
+differences for differential quantities such as the pressure profile
+\citep{2013A&A...550A.131P} or the profile of gas mass fractions
+\citep{2012arXiv1209.4082B}. These discrepancies (that have been more dramatic
+in the past without AGN feedback) motivated the development of phenomenological
+models of the ICM \citep[e.g.,][]{2005ApJ...634..964O,
+  2012MNRAS.422..686C}. Here, we construct a simple and purely phenomenological
+model that matches all available X-ray and Sunyaev-Zel'dovich (SZ) data with the
+goal to facilitate comparison of future hydrodynamical simulations, to allow the
+modeling of non-thermal cluster emission over the entire electromagnetic wave
+band, and finally to enable the construction of cluster mock catalogs of the
+(non-)thermal cluster emission of current and future surveys. Such a model for
+the ICM needs to be complementd by a sample of cluster halos, which can either
+be obtained by means of analytical expressions for the cluster mass function
+(e.g., \citealp{2001MNRAS.321..372J}) or cosmological cluster simulations. In
+this work, we make use of the recent collisionless $N$-body simulation {\em
+  MultiDark}, which employs a $\Lambda$ cold dark matter cosmology
+(\citealp{2011arXiv1104.5130P}; www.multidark.org).
 
-In order to build a cluster sample with realistic ICM densities, we 
-adopt a \emph{phenomenological} approach and construct our density 
-profiles from X-ray observations. We then compare the characteristics of 
-the clusters in our mock sample to observational results. We study the X-ray 
-luminosity function (XLF), the luminosity-mass relation, $L_{\rmn{X}}- M$, and 
-the $Y_{\rmn{X}}-M$ relation, where $Y_{\rmn{X}}=M_\rmn{gas}k_{\rmn{B}}T$ 
-with an X-ray-derived gas mass $M_{\rmn{gas}}$ and temperature $T$
-\citep{2006ApJ...650..128K}. Moreover, we consider the thermal 
-Sunyaev-Zel’dovich (SZ) effect and compare our $Y_{\rmn{SZ}}-M$ 
-relation with recent SZ-derived measurements. Only if our model matches
-available cluster data on the gas properties, we can safely use it in Paper~II
-and be sure that we will obtain realistic predictions.
-The final result is a complete cosmological cluster mock catalog, at
-different redshifts, containing information on the DM and ICM properties 
-of each object, together with its (non-)thermal emission at different 
-frequencies. This mock catalog reproduces existing observations
-and is useful in making predictions for future surveys.
+Our \emph{phenomenological} approach uses gas density profiles of a
+representative sample of X-ray clusters, which are complemented by observed
+cluster mass-dependent gas mass fractions. The resulting cluster mock sample are
+then compared to data including the X-ray luminosity function (XLF), the
+luminosity-mass relation, $L_{\rmn{X}}- M$, and the $Y_{\rmn{X}}-M$ relation,
+where $Y_{\rmn{X}}=M_\rmn{gas}k_{\rmn{B}}T$ with an X-ray-derived gas mass
+$M_{\rmn{gas}}$ and temperature $T$ \citep{2006ApJ...650..128K}. We additionally
+compare our $Y_{\rmn{SZ}}-M$ relation to recent SZ-derived measurements.  In a
+companion paper \citep{paper2}, we apply our ICM model to predict the
+non-thermal radio halo emission a cosmological complete sample of galaxy
+clusters, enabling valuable insight into the statistics of radio halos.  On of
+our final data products is a complete cosmological cluster mock catalog, at
+different redshifts, containing information of DM and ICM properties for each
+object, together with its (non-)thermal emission at different frequencies. This
+mock catalog matches existing observations and should serve eminent in making
+predictions for future radio surveys.
 
-In next Section~\ref{sec:2}, we introduce the MultiDark simulation
-along with our final cluster sample. We assign to each of our clusters  
-the phenomenologically constructed gas density profile in 
-Section~\ref{sec:3}. In Sections~\ref{sec:4} and 
-\ref{sec:5}, we show that this approach can successfully reproduce 
-the known X-ray and SZ cluster characteristics. We present the
-resulting mock cluster catalogs in Section~\ref{sec:6}, and eventually 
-summarize our conclusions in Section~\ref{sec:7}.
-In this work, the cluster mass $M_{\Delta}$ and radius $R_{\Delta}$ are defined 
-with respect to a density that is $\Delta=200$ or $\Delta=500$ times the \emph{critical} 
-density of the Universe. We adopt density parameters of $\Omega_{\rmn{m}}=0.3$, 
-$\Omega_{\Lambda}=0.7$ and today's Hubble constant of 
-$H_0 = 100 \times h_{70}$~km~s$^{-1}$~Mpc$^{-1}$ where $h_{70} = 0.7$.
+In Section~\ref{sec:2}, we introduce the MultiDark simulation along with our
+final cluster sample. We assign to each of our clusters the phenomenologically
+constructed gas density profile in Section~\ref{sec:3}. In Sections~\ref{sec:4}
+and \ref{sec:5}, we show that this approach can successfully reproduce the
+observed X-ray and SZ cluster data. We present the resulting mock cluster
+catalogs in Section~\ref{sec:6}, and eventually summarize our conclusions in
+Section~\ref{sec:7}.  In this work, the cluster mass $M_{\Delta}$ and radius
+$R_{\Delta}$ are defined with respect to a density that is $\Delta=200$ or
+$\Delta=500$ times the \emph{critical} density of the Universe. We adopt density
+parameters of $\Omega_{\rmn{m}}=0.3$, $\Omega_{\Lambda}=0.7$ and today's Hubble
+constant of $H_0 = 100 \times h_{70}$~km~s$^{-1}$~Mpc$^{-1}$ where $h_{70} =
+0.7$.}
 
@@
 \end{document}
+
+\del{
+The study of the (non-)thermal emission in galaxy clusters provides
+important information on structure formation process and on 
+fundamental characteristics of our Universe. This field is at a 
+crucial point of its development thanks to the very low sensitivity of present and future-generation 
+instruments such as LOFAR\footnote{www.lofar.org}, \emph{e}ROSITA\footnote{www.mpe.mpg.de/eROSITA}, 
+ASTRO-H\footnote{astro-h.isas.jaxa.jp} and CTA\footnote{www.cta-observatory.org}, to name but a few. 
+Therefore, it is important to provide prospects for future surveys and
+to understand in which way they can improve our current knowledge.
+To this end, a complete cosmological mock sample of galaxy
+clusters is needed. This can be realized either using analytical 
+expressions for the cluster mass function (e.g., \citealp{2001MNRAS.321..372J}) or cosmological cluster 
+simulations. In this work, we make use of the recent MultiDark $N$-body
+simulation (\citealp{2011arXiv1104.5130P}; www.multidark.org).
+%
+Our main motivation to build such a mock catalog has been to predict the 
+non-thermal emission at radio frequencies of a cosmological 
+complete sample of galaxy clusters. This is presented in a companion 
+paper (\citealp{paper2}; hereafter Paper~II). As described in Paper~II, for 
+any given cluster, fundamental ingredients for the non-thermal emission 
+model are the mass and gas density distribution. The MultiDark 
+simulation used here is a $N$-body, \emph{dark matter (DM)-only} simulation and, 
+therefore, does not contain any information on the intra-cluster medium (ICM) gas  
+distribution. A cosmological complete sample of clusters can 
+only be obtained from $N$-body simulations as hydrodynamical
+simulations of such large volumes are computationally too expensive.
+Therefore, we need a method to determine the ICM properties
+of any given cluster from its total mass. 
+}

### 2013-09-25 paper1.tex
typos corrected

@@
 hydrodynamical simulations has been progressively refined over the last years to
-also include (subresolution models for) AGN feedback
+also include (sub-resolution models for) AGN feedback
 \citep[e.g.,][]{2007MNRAS.380..877S, 2008MNRAS.387.1403S, 2008ApJ...687L..53P,
@@
 (non-)thermal cluster emission of current and future surveys. Such a model for
-the ICM needs to be complementd by a sample of cluster halos, which can either
+the ICM needs to be complemented by a sample of cluster halos, which can either
 be obtained by means of analytical expressions for the cluster mass function
@@
 $Y_{\rmn{SZ}}-M_{500}$ relation in our model (calculated as in equation~(3) of
-\citealp{2011arXiv1109.3709B}) with the observed scaling relation by the
+\citealp{2012ApJ...758...74B}) with the observed scaling relation by the
 \cite{2013arXiv1303.5080P}. {\bf We compare with the result obtained from the 
@@
 of these telescopes with respect to \emph{Planck}, which results in a much
-more (redshift) non-homogenous sample. Nevertheless, our mock clusters 
+more (redshift) non-homogeneous sample. Nevertheless, our mock clusters 
 can reproduce well the median SPT and ACT populations. A more detailed

### 2013-09-28 paper1.tex
text corected

@@
 
-%\newcommand{\rmn}{\mathrm}
+\usepackage{graphicx}
+\usepackage{natbib}
+\usepackage{txfonts}
+\usepackage[usenames,dvips]{color}
+\newcommand\qc[1]{{\color{red} \bf #1}}
+
 \newcommand{\CR}{\mathrm{CR}}
@@
 \newcommand{\vel}{\upsilon}
-%
-\usepackage{graphicx}
-\usepackage{natbib}
-%
-\usepackage{txfonts}
 
-%\voffset-0.5in
+%\voffset-0.6in
 
@@
     cluster catalog by assigning our gas density model to each cluster halo of
-    the large collisionless $N$-body simulation {\em MultiDark}. Our clusters
+    the large collisionless $N$-body simulation MultiDark. Our clusters
     are identified with cool-core and non cool-core clusters according to a
@@
 
-\begingroup
-\let\thefootnote\relax\footnotetext{* f.zandanel@uva.nl}
-\endgroup
-
 {\bf Galaxy clusters are the rarest and largest gravitationally-collapsed
   objects in the Universe and form at sites of constructive interference of long
-waves in the primordial density fluctuations. Clusters reach radial extends of a
-few Mpc and total masses $M \sim (10^{14} - 10^{15}) M_{\odot}$, of which
-galaxies, hot ($1-10$~keV) gas and dark matter (DM) contribute roughly for 5, 15
+  waves in the primordial density fluctuations. Clusters reach radial extends of
+  a few Mpc and total masses $M \sim (10^{14} - 10^{15}) M_{\odot}$, of which
+  galaxies, hot ($1-10$~keV) gas and dark matter (DM) contribute roughly 5, 15
   and 80\%, respectively. If the thermal properties of the intracluster medium
-(ICM) were solely determined by the gravity of the DM potential wells, then
-cluster would obey self-similar scaling relations \citep{1986MNRAS.222..323K}.
-However, X-ray observations have demonstrated that self-similarity is broken,
+  (ICM) were solely determined by the gravity of the system, then clusters would
+  obey self-similar scaling relations \citep{1986MNRAS.222..323K}.  However,
+  X-ray observations have demonstrated that self-similarity is broken,
   especially at low-mass scales (see e.g., \citealp{2005RvMP...77..207V} for a
-review). Apparently the energy input from non-gravitational processes associated
-with galaxy formation have a larger influence in smaller systems, i.e., at
-scales of galaxy groups.
+  review). Apparently the energy input from non-gravitational processes
+  associated with galaxy formation have a larger influence in smaller systems,
+  i.e., at scales of galaxy groups.
 
-The central cooling time of the X-ray emitting gas in galaxy clusters and groups
-is bimodally distributed. Approximately half of all systems have radiative
-cooling times of less than 1~Gyr and establish a population of cool core (CC)
-clusters while some others have cooling times that are longer than the age of
-the Universe, forming the non-cool core (NCC) cluster population
-\citep{2009ApJS..182...12C,2010A&A...513A..37H}. Several physical processes have
-been proposed to be responsible for balancing radiative cooling of the
-low-entropy gas at the centers of CCs. In particular the self-regulated nature
-of the proposed feedback and observational correlations between radio activity
-and central entropy (which is a proxy for a small cooling time) have put
-feedback by active galactic nuclei (AGN) into the focus of recent research
-\citep{2007ARA&A..45..117M, 2012NJPh...14e5023M}. The underlying physical
-processes responsible for the heating include dissipation of mechanical heating
-by outflows, lobes, or sound waves from the central AGN
-\citep[e.g.,][]{2001ApJ...554..261C, 2002Natur.418..301B, 2002ApJ...581..223R}
-or cosmic-ray heating: streaming cosmic rays excite Alfv\'en waves on which they
-resonantly scatter \citep{1969ApJ...156..445K}.  Damping of these waves
-transfers cosmic ray energy and momentum to the cooling plasma
-\citep{1991ApJ...377..392L, 2008MNRAS.384..251G, 2011A&A...527A..99E,
-  2013MNRAS.434.2209W}, heating it at a rate that balances radiative cooling on
-average at each radius \citep{2013arXiv1303.5443P}.
+  The central cooling time of the X-ray emitting gas in galaxy clusters and
+  groups is bimodally distributed. Approximately half of all systems have
+  radiative cooling times of less than 1~Gyr and establish a population of cool
+  core clusters (CCC) while others have cooling times that can be longer than
+  the age of the Universe, forming the non-cool core cluster (NCC) population
+  \citep{2009ApJS..182...12C,2010A&A...513A..37H}. Several physical processes
+  have been proposed to be responsible for balancing radiative cooling of the
+  low-entropy gas at the centers of CCCs. In particular feedback by active
+  galactic nuclei (AGN) has come into the focus of recent research
+  \citep{2007ARA&A..45..117M, 2012NJPh...14e5023M} owing to the self-regulated
+  nature of the proposed feedback and observational correlations between radio
+  activity and central entropy (which is a proxy for a small cooling time). The
+  underlying physical processes responsible for the heating include dissipation
+  of mechanical heating by outflows, lobes, or sound waves from the central AGN
+  \citep[e.g.,][]{2001ApJ...554..261C, 2002Natur.418..301B, 2002ApJ...581..223R,
+    2012MNRAS.424..190G} or cosmic-ray heating: streaming cosmic rays excite
+  Alfv\'en waves on which they resonantly scatter \citep{1969ApJ...156..445K}.
+  Damping of these waves transfers cosmic ray energy and momentum to the cooling
+  plasma \citep{1991ApJ...377..392L, 2008MNRAS.384..251G, 2011A&A...527A..99E,
+    2013MNRAS.434.2209W}, heating it at a rate that balances radiative cooling
+  on average at each radius while explaining the observed temperature floor in
+  CCCs by thermal stability of the heating mechanism
+  \citep{2013arXiv1303.5443P}.
 
   Modeling the formation and evolution of clusters with cosmological
-hydrodynamical simulations has been progressively refined over the last years to
-also include (sub-resolution models for) AGN feedback
+  hydrodynamical simulations has been progressively refined over the last years
+  to also include (sub-resolution models for) AGN feedback
   \citep[e.g.,][]{2007MNRAS.380..877S, 2008MNRAS.387.1403S, 2008ApJ...687L..53P,
@@
   \citep{2012arXiv1209.4082B}. These discrepancies (that have been more dramatic
-in the past without AGN feedback) motivated the development of phenomenological
-models of the ICM \citep[e.g.,][]{2005ApJ...634..964O,
-  2012MNRAS.422..686C}. Here, we construct a simple and purely phenomenological
-model that matches all available X-ray and Sunyaev-Zel'dovich (SZ) data with the
-goal to facilitate comparison of future hydrodynamical simulations, to allow the
-modeling of non-thermal cluster emission over the entire electromagnetic wave
-band, and finally to enable the construction of cluster mock catalogs of the
-(non-)thermal cluster emission of current and future surveys. Such a model for
-the ICM needs to be complemented by a sample of cluster halos, which can either
-be obtained by means of analytical expressions for the cluster mass function
-(e.g., \citealp{2001MNRAS.321..372J}) or cosmological cluster simulations. In
-this work, we make use of the recent collisionless $N$-body simulation {\em
-  MultiDark}, which employs a $\Lambda$ cold dark matter cosmology
+  in the past without AGN feedback) motivated the development of
+  phenomenological models of the ICM \citep[e.g.,][]{2005ApJ...634..964O,
+    2012MNRAS.422..686C}. Here, we construct a simple and purely
+  phenomenological model that matches all available X-ray and Sunyaev-Zel'dovich
+  (SZ) data with the goal to facilitate comparison of future hydrodynamical
+  simulations, to allow the modeling of non-thermal cluster emission over the
+  entire electromagnetic wave band, and finally to enable the construction of
+  cluster mock catalogs of the thermal and non-thermal cluster emission (in the
+  radio, hard X-ray, and gamma-ray band) of current and future surveys. Such a
+  model for the ICM needs to be complemented by a sample of cluster halos, which
+  can either be obtained by means of analytical expressions for the cluster mass
+  function (e.g., \citealp{2001MNRAS.321..372J}) or cosmological cluster
+  simulations. In this work, we make use of the recent collisionless $N$-body
+  simulation MultiDark, which employs a $\Lambda$ cold dark matter cosmology
   (\citealp{2011arXiv1104.5130P}; www.multidark.org).
@@
   representative sample of X-ray clusters, which are complemented by observed
-cluster mass-dependent gas mass fractions. The resulting cluster mock sample are
-then compared to data including the X-ray luminosity function (XLF), the
+  cluster mass-dependent gas mass fractions. The resulting cluster mock sample
+  are then compared to data including the X-ray luminosity function (XLF), the
   luminosity-mass relation, $L_{\rmn{X}}- M$, and the $Y_{\rmn{X}}-M$ relation,
   where $Y_{\rmn{X}}=M_\rmn{gas}k_{\rmn{B}}T$ with an X-ray-derived gas mass
-$M_{\rmn{gas}}$ and temperature $T$ \citep{2006ApJ...650..128K}. We additionally
-compare our $Y_{\rmn{SZ}}-M$ relation to recent SZ-derived measurements.  In a
-companion paper \citep{paper2}, we apply our ICM model to predict the
-non-thermal radio halo emission a cosmological complete sample of galaxy
-clusters, enabling valuable insight into the statistics of radio halos.  On of
-our final data products is a complete cosmological cluster mock catalog, at
-different redshifts, containing information of DM and ICM properties for each
-object, together with its (non-)thermal emission at different frequencies. This
-mock catalog matches existing observations and should serve eminent in making
-predictions for future radio surveys.
+  $M_{\rmn{gas}}$ and temperature $T$ \citep{2006ApJ...650..128K}. We
+  additionally compare our $Y_{\rmn{SZ}}-M$ relation to recent SZ data, where
+  $Y_\rmn{SZ}$ denotes the integrated Compton-$y$ parameter.  In a companion
+  paper (\citealp{paper2}; hereafter Paper~II), we apply our ICM model to
+  predict the non-thermal radio halo emission of a cosmological complete sample of
+  galaxy clusters, enabling valuable insight into the statistics of radio halos.
+  One of our final data products is a complete cosmological cluster mock catalog,
+  at different redshifts, containing information of DM and ICM properties for
+  each object, together with its (non-)thermal emission at different
+  frequencies. This mock catalog matches existing observations and should be
+  eminent in making predictions for future radio surveys.
 
   In Section~\ref{sec:2}, we introduce the MultiDark simulation along with our
-final cluster sample. We assign to each of our clusters the phenomenologically
-constructed gas density profile in Section~\ref{sec:3}. In Sections~\ref{sec:4}
-and \ref{sec:5}, we show that this approach can successfully reproduce the
-observed X-ray and SZ cluster data. We present the resulting mock cluster
-catalogs in Section~\ref{sec:6}, and eventually summarize our conclusions in
-Section~\ref{sec:7}.  In this work, the cluster mass $M_{\Delta}$ and radius
-$R_{\Delta}$ are defined with respect to a density that is $\Delta=200$ or
-$\Delta=500$ times the \emph{critical} density of the Universe. We adopt density
-parameters of $\Omega_{\rmn{m}}=0.3$, $\Omega_{\Lambda}=0.7$ and today's Hubble
-constant of $H_0 = 100 \times h_{70}$~km~s$^{-1}$~Mpc$^{-1}$ where $h_{70} =
-0.7$.}
+  final cluster halo sample. We assign to each of our clusters the
+  phenomenologically constructed gas density profile in Section~\ref{sec:3}. In
+  Sections~\ref{sec:4} and \ref{sec:5}, we show that this approach can
+  successfully reproduce the observed X-ray and SZ cluster data. We present the
+  resulting mock cluster catalogs in Section~\ref{sec:6}, and eventually
+  summarize in Section~\ref{sec:7}.  In this work, the cluster mass $M_{\Delta}$
+  and radius $R_{\Delta}$ are defined with respect to a density that is
+  $\Delta=200$ or 500 times the \emph{critical} density of the Universe. We
+  adopt density parameters of $\Omega_{\rmn{m}}=0.3$, $\Omega_{\Lambda}=0.7$ and
+  today's Hubble constant of $H_0 = 100\, h_{70}$~km~s$^{-1}$~Mpc$^{-1}$ where
+  $h_{70} = 0.7$.}
 
@@
 \label{sec:2}
-The MultiDark simulation used in this work is described in detail in \cite{2011arXiv1104.5130P}.  
-It is an $N$-body cosmological simulation done with the Adaptive-Refinement-Tree (ART) 
-code \citep{1997ApJS..111...73K} of $2048^3$ particles within a ($1000$~Mpc~$h^{-1}$)$^3$ 
-cube. {\bf The adopted cosmological parameters are $\Omega_{\rmn{m}}=0.27$, $\Omega_{\Lambda}=0.73$,
-$\Omega_\rmn{b}=0.0469$, $n_\rmn{s}=0.95$, $h=0.7$ and $\sigma_8=0.82$.} This simulation is 
-particularly well suited for our purpose because of its large 
+The MultiDark simulation used in this work is described in detail in
+\cite{2011arXiv1104.5130P}.  It is an $N$-body cosmological simulation done with
+the Adaptive-Refinement-Tree (ART) code \citep{1997ApJS..111...73K} of $2048^3$
+particles within a ($1000\,h^{-1}$~Mpc)$^3$ cube. {\bf The adopted cosmological
+  parameters are $\Omega_{\rmn{m}}=0.27$, $\Omega_{\Lambda}=0.73$,
+  $\Omega_\rmn{b}=0.0469$, $n_\rmn{s}=0.95$, $h=0.7$ and $\sigma_8=0.82$.} This
+simulation is particularly well suited for our purpose because of its large
 number of high-mass objects, i.e., galaxy clusters.
@@
 $M_{200}\geq1\times10^{14}$~$h^{-1}$~M$_{\odot}\approx1.4\times10^{14}$~$h_{70}^{-1}$~M$_{\odot}$
-which ensures $k_{\rmn{B}}T \gtrsim 2.6$~keV, assuming the $M_{500} - T_{\rmn{ci}}$ relation
-of \cite{2010MNRAS.406.1773M}.
+which ensures $k_{\rmn{B}}T \gtrsim 2.6$~keV (assuming the $M_{500} - T_{\rmn{ci}}$ relation
+of \citealt{2010MNRAS.406.1773M}).
 
@@
 
-We decided to use a \emph{phenomenological} approach and to construct the gas
+We decided to use a \emph{phenomenological} approach and construct the gas
 density profiles directly from X-ray observations. A suitable X-ray sample that
-provides the needed information is the \emph{Representative XMM-Newton Cluster
+provides the required information is the \emph{Representative XMM-Newton Cluster
   Structure Survey} (REXCESS) sample \citep{2008A&A...487..431C,
@@
 Fig.~\ref{fig:gas_profiles}, we show the 31 electron density profiles of the
-REXCESS sample color-coded by non cool-core clusters (NCCCs) and 
-cool-core clusters (CCCs).
+REXCESS sample color-coded by NCCCs and CCCs.
 
@@
 The next step is to introduce a mass-scaling in order to apply our GNFW profiles
-to all our clusters. We adopt the gas mass fraction-mass scaling,
-$f_{\rmn{gas},500}-M_{500}$ of \cite{2009ApJ...693.1142S} (and adopt their equation~(8)). We can
-express $f_{\rmn{gas},500}$ in the following way:
+to clusters of all masses. We adopt the gas mass fraction-mass scaling,
+$f_{\rmn{gas},500}-M_{500}$ of \cite{2009ApJ...693.1142S} (and adopt their
+equation~(8)). We can express $f_{\rmn{gas},500}$ in the following way:
 \begin{equation}
@@
 \end{eqnarray}
-where $g_{1}$ and $g_{2}$ are random Gaussian number which we use in order to
+where $g_{1}$ and $g_{2}$ are random Gaussian numbers, which we use in order to
 simulate the natural scatter of the gas profiles.\footnote{The values
@@
 Hence, for each cluster in our sample we obtain a gas density profile
-$\rho_{\rmn{gas},i}$ that obeys the observed $f_{gas,500}-M_{500}$ relation and
-is uniquely determined by its DM mass $M_{500,i}$ and by the property of being a
+$\rho_{\rmn{gas},i}$ that obeys the observed $f_{\rmn{gas},500}-M_{500}$ relation and
+is uniquely determined by its total mass $M_{500,i}$ and by the property of being a
 NCCC or CCC. We assign the latter property to every halo depending on its
@@
 radius. This parameter assesses the dynamical state of the cluster and whether
-the halo experienced a recent merger or not. Current observations reveal a ratio
+the halo has experienced a recent merger or not. Current observations reveal a ratio
 of NCCCs and CCCs of about $50\%$ (e.g., \citealp{2007A&A...466..805C,
@@
 0.12$ with a \emph{median} of $z \approx 0.04$. Thus, our phenomenological gas
-profile is representative of the cluster population at $z\approx0$. To extend this
-profile to high-$z$, we include a \emph{self-similar} scaling of the gas density
-as $\rho_{\rmn{gas}}(z) = E(z)^{2} \rho_{\rmn{gas}}(z=0)$, where $E(z)^{2} =
-\Omega_{\rmn{m}} (1+z)^{3} + \Omega_{{\Lambda}}$.
+profile is representative of the cluster population at $z\approx0$. To extend
+this profile to high-$z$, we adopt a \emph{self-similar} scaling of the gas
+density as $\rho_{\rmn{gas}}(z) = E(z)^{2} \rho_{\rmn{gas}}(z=0)$, where
+$E(z)^{2} = \Omega_{\rmn{m}} (1+z)^{3} + \Omega_{{\Lambda}}$.
 
@@
 our phenomenological gas model.  Here, we will test how our cluster mock data
-compares to various X-ray inferred observables. Those include the observed
-$L_{\rmn{bol}} - M_{500}$ relation, the $Y_X - M_{500}$ relation, and the
-XLF.
+compare to various X-ray inferred observables, which are obtained from different
+cluster samples and from (partially) different X-ray observatories. Those
+include the observed $L_{\rmn{bol}} - M_{500}$ relation, the $Y_X - M_{500}$
+relation, and the XLF.
 
@@
   procedure by fitting each of the 31 REXCESS clusters with
-  equation~(\ref{eq:gnfw}) and calculating $L_{\rmn{bol}}$ with the measured gas
+  equation~(\ref{eq:gnfw}) and calculate $L_{\rmn{bol}}$ using the measured gas
   temperature of each cluster. As a result, we fall short of the observed
-  luminosity by a mean (median) of about $21\%$ ($20\%$). This is reasonable
+  luminosity by a mean (median) of about $21\%$ ($20\%$). This is acceptable
   considering that we do not permit the parameters $R_{\rmn{c}}$, $\alpha$ and
@@
 
-In the right panel of Fig.~\ref{fig:X_LM}, we compare the
-$Y_{\rmn{X}}-M_{500}$ relation of our sample to observational data
-\citep{2010MNRAS.406.1773M}. The model agrees nicely at the high-mass end, but
-underpredicts the observed scaling at low masses by about $20\%$ (at the
-1-$\sigma$ level). This is the same level of deviation from the data as in the
-case of $L_{\rmn{X}}$, which is more significant due to the smaller scatter in
-the $Y_{\rmn{X}}$ relation. The differential contribution to the thermal energy
-per logarithmic interval in radius (and hence to the integrated Compton-$y$
-parameter) is given by $\dd Y /\dd\log r \propto r^3 P_{\rmn{th}}(r)$, with the
-thermal gas pressure $P_{\rmn{th}}=n_{\rmn{gas}}k_{\rmn{B}}T$. It peaks at
-scales slightly smaller than $R_{500}$ with 1-$\sigma$ contributions extending
-out to $3\,R_{500}$ \citep{2010ApJ...725...91B}. Hence, the observational
-scaling constrains our model on those large scales, quite complementary to the
-X-ray luminosity. The deviations at small masses either indicates different
-assumptions about $f_{\rmn{gas}}$, the gas temperature, or different selection
-effects of either observational sample that we use for model calibration and
-comparison.  \cite{2010MNRAS.406.1773M} determine their masses by adopting a
-constant value for $f_{\rmn{gas}}$, in contrast to our approach which adopts the
-observed $f_{\rmn{gas},500}-M_{500}$ relation given by
+In the right panel of Fig.~\ref{fig:X_LM}, we compare the $Y_{\rmn{X}}-M_{500}$
+relation of our sample to observational data \citep{2010MNRAS.406.1773M}. The
+model agrees nicely at the high-mass end, but underpredicts the observed scaling
+at low masses by about $20\%$ (at the 1-$\sigma$ level). This is the same level
+of deviation from the data as in the case of $L_{\rmn{X}}$, which is more
+significant due to the smaller scatter in the $Y_{\rmn{X}}$ relation. The
+differential contribution to the thermal energy per logarithmic interval in
+radius (and hence to the integrated Compton-$y$ parameter) is given by $\dd Y
+/\dd\log r \propto r^3 P_{\rmn{th}}(r)$, with the thermal gas pressure
+$P_{\rmn{th}}=n_{\rmn{gas}}k_{\rmn{B}}T$. It peaks at scales slightly smaller
+than $R_{500}$ with 1-$\sigma$ contributions extending out to $3\,R_{500}$
+\citep{2010ApJ...725...91B}. Hence, the observational scaling constrains our
+model on those large scales, quite complementary to the X-ray luminosity. The
+deviations at small masses either indicate tensions with our assumptions on
+$f_{\rmn{gas}}$, the gas temperature, or different selection effects of either
+observational sample that we use for model calibration and comparison.
+\cite{2010MNRAS.406.1773M} determine their masses by adopting a constant value
+for $f_{\rmn{gas}}$, in contrast to our approach which adopts the observed
+$f_{\rmn{gas},500}-M_{500}$ relation given by
 \cite{2009ApJ...693.1142S}. Additionally, we adopt the
@@
 emissivity scales with the square of the gas density, which makes it subject to
-density variations and clumping.\footnote{The mean (median) difference at $z=0$
-  between $L_{\rmn{bol}}$ within $R_{200}$ or within $R_{500}$ is $\approx 5\%$
-  ($\approx 7\%$). While $L_{\rmn{bol}}$ refers to the quantity calculated
-  within $R_{500}$, we note that the XLF for luminosities calculated within
-  $R_{200}$ will be barely changed.} This implies large scatter that causes a
+density variations and clumping. This implies large scatter that causes a
 large Malmquist bias and underlines the necessity of careful mock surveys that
@@
   data points, the soft-band and bolometric Schechter fits of the BCS sample of
-  \protect\cite{1997ApJ...479L.101E}, which has a median of $z \approx 0.08$.  While the
-  soft-band XLF, which was obtained applying the \protect\cite{2010MNRAS.406.1773M}
-  $L_{\rmn{X}}-M_{500}$ relation to the MultiDark $z = 0.1$ snapshot, compares
-  well with the BCS data points, it deviates from the corresponding Schechter
-  fit. We also show the bolometric XLF of \protect\cite{2010MNRAS.406.1773M} and
-  bolometric XLF of our model at $z=0.1$. The XLFs are calculated in equally
-  log-spaced mass bins; the error bars represent the Poissonian errors. Note
-  that we limit the comparison to the luminosity range covered by our sample,
-  where we cut the lowest part because in that range the XLF rapidly drops due
-  to the imposed mass cut.}
+  \protect\cite{1997ApJ...479L.101E}, which has a median of $z \approx 0.08$.
+  While the soft-band XLF, which was obtained applying the
+  \protect\cite{2010MNRAS.406.1773M} $L_{\rmn{X}}-M_{500}$ relation to the
+  MultiDark $z = 0.1$ snapshot, compares well with the BCS data points, it
+  deviates from the corresponding Schechter fit. We also show the bolometric XLF
+  of \protect\cite{2010MNRAS.406.1773M} and the bolometric XLF of our model at
+  $z=0.1$. The XLFs are calculated in equally log-spaced mass bins; the error
+  bars represent the Poissonian errors. Note that we limit the comparison to the
+  luminosity range covered by our sample.  We impose a low-luminosity cut to
+  avoid a drop in the XLF due to the imposed mass cut.}
 \label{fig:XLF}
@@
 Nevertheless, it provides a complementary check for our model. To this end, we
-use the \emph{ROSAT} brightest cluster sample (BCS) XLF
-\citep{1997ApJ...479L.101E}, which is in good agreement with results from the
-\emph{ROSAT} ESO Flux-Limited X-ray (REFLEX; \citealp{2002ApJ...566...93B}) and
-HIFLUGCS \citep{2002ApJ...567..716R}.  Note that the XLF is fully determined by
-the mass function and the $L_{\rmn{X}}-M_{500}$ relation after taking into
-account the observational biases. This means that applying the Malmquist and
+use the XLF of the \emph{ROSAT} brightest cluster sample
+\citep[BCS][]{1997ApJ...479L.101E}, which is in good agreement with results from
+the \emph{ROSAT} ESO Flux-Limited X-ray (REFLEX; \citealp{2002ApJ...566...93B})
+and HIFLUGCS \citep{2002ApJ...567..716R}.  Note that the XLF is fully determined
+by the mass function and the $L_{\rmn{X}}-M_{500}$ relation after taking into
+account the observational biases.\footnote{The mean (median) difference at $z=0$
+  between $L_{\rmn{bol}}$ within $R_{200}$ or within $R_{500}$ is $\approx 5\%$
+  ($\approx 7\%$). While $L_{\rmn{bol}}$ refers to the quantity calculated
+  within $R_{500}$, we note that the XLF for luminosities calculated within
+  $R_{200}$ will be barely changed.} This means that applying the Malmquist and
 Eddington-bias-corrected $L_{\rmn{X}}-M_{500}$ relation by
@@
 accounting for the observational scatter in $L_{\rmn{X}}-M_{500}$ should yield
-an unbiased XLF. We show the resulting bolometric and soft-band ($0.1-2.4$~keV)
-XLF in Fig.~\ref{fig:XLF} and compare those to the corresponding BCS XLFs and
-to our model predictions. Note that there is only the Schechter fit available
-for the BCS bolometric XLF.  While the soft-band XLF by
-\cite{2010MNRAS.406.1773M} agrees well with the BCS data points, it deviates
-from the corresponding Schechter fit at low luminosities. This is also true in
-the bolometric band, where the XLFs of \cite{2010MNRAS.406.1773M} and our model
-agree well, but deviate from the BCS Schechter fit at low luminosities. This may
-be an artifact due to the use of Schechter fit instead of the data points or may
-point to incompleteness of the BCS sample. Note that the Poissonian errors of
-the XLF obtained from the MultiDark simulation are a lower limit as we are
-neglecting the uncertainty due to cosmic variance.  Studies of the XLF will
-become again an important topic with the upcoming launch of the \emph{e}ROSITA
-satellite (e.g., \citealp{2011MSAIS..17..159C}) and further studies in this
-direction are desirable. For these reasons, we do not show XLF predictions at
-other redshifts, leaving this for a future study.
+an unbiased XLF.
+
+We show the resulting bolometric and soft-band ($0.1-2.4$~keV) XLF in
+Fig.~\ref{fig:XLF} and compare those to the corresponding BCS XLFs and to our
+model predictions. Note that there is only the Schechter fit available for the
+BCS bolometric XLF.  While the soft-band XLF by \cite{2010MNRAS.406.1773M}
+agrees well with the BCS data points, it deviates from the corresponding
+Schechter fit at low luminosities. This is also true in the bolometric band,
+where the XLFs of \cite{2010MNRAS.406.1773M} and our model agree well, but
+deviate from the BCS Schechter fit at low luminosities. This may be an artifact
+due to the use of Schechter fit instead of the data points or may point to
+incompleteness of the BCS sample. Note that the Poissonian errors of the XLF
+obtained from the MultiDark simulation are a lower limit as we are neglecting
+the uncertainty due to cosmic variance.  Studies of the XLF will become again an
+important topic with the upcoming launch of the \emph{e}ROSITA satellite (e.g.,
+\citealp{2011MSAIS..17..159C}) and further studies in this direction are
+desirable. For these reasons, we do not show XLF predictions at other redshifts,
+leaving this for a future study.
 
@@
 \label{sec:5}
-In the right panel of Fig.~\ref{fig:X_LM}, we compare the
-$Y_{\rmn{SZ}}-M_{500}$ relation in our model (calculated as in equation~(3) of
-\citealp{2012ApJ...758...74B}) with the observed scaling relation by the
-\cite{2013arXiv1303.5080P}. {\bf We compare with the result obtained from the 
-\emph{Planck} COSMO sample with Malmquist bias correction,
-which has a median redshift of $0.18$. Hence, we compare the data to our relation 
-at the MultiDark snapshot $z=0.2$}. Our model reproduces the data remarkably well, except 
-for the high-mass end where our simulations have a weaker constraining power due to the 
-smaller box size in comparison to the survey volume of {\em Planck}. We find a scatter of
+In the left panel of Fig.~\ref{fig:SZ_M}, we compare the $Y_{\rmn{SZ}}-M_{500}$
+relation in our model (following \citealp{2012ApJ...758...74B}, equation~3) with
+the observed scaling relation by the \cite{2013arXiv1303.5080P}. {\bf We use the
+  \emph{Planck} COSMO sample, which is Malmquist-bias corrected and has a median
+  redshift of $0.18$. Hence, we compare the data to our $z=0.2$ relation}. Our
+model reproduces the data remarkably well, except for the high-mass end where
+our simulations have a weaker constraining power due to the smaller box size in
+comparison to the survey volume of {\em Planck}. We find a scatter of
 $\sigma_{yx} \approx 0.11$ which compares well with the \emph{Planck} result of
@@
 
-\begin{figure} 
+\begin{figure*} 
 \centering
 \includegraphics[width=0.48\textwidth]{figures/sz_m.eps}
-\caption{{\bf SZ scaling relation of our sample at $z=0.2$ in comparison to the observational 
-  sample by \protect\cite{2013arXiv1303.5080P} with a median redshift of about $0.18$.
-  Grey triangles show the MultiDark sample (limited to the mass range covered by observations), 
-  the black line is the corresponding scaling relation, and the blue line is the observational result. 
-  The black crosses represent the $Y_{\rmn{SZ}}$ median values of our sample for a given mass bin (indicated by 
-  horizontal error bars), and the vertical error bars represent the standard deviation within a
-  bin. The bottom panels show the relative difference to the observational scaling relations.}}
+\includegraphics[width=0.48\textwidth]{figures/sz_m_ACT.eps}
+\caption{{\bf Comparison of our SZ scaling relations (grey triangles) with
+    data. \emph{Left.}  We compare our $Y_{\rmn{SZ}}-M$ relation at $z=0.2$ with
+    the {\em Planck} data \citep{2013arXiv1303.5080P}, which have a median
+    redshift of about $0.18$.  The black crosses represent the $Y_{\rmn{SZ}}$
+    median values of our sample for a given mass bin (indicated by horizontal
+    error bars), and the vertical error bars represent the standard deviation
+    within a bin. The bottom panels show the relative difference to the
+    observational scaling relations. \emph{Right.} We compare our
+    $Y_{\rmn{SZ}}-M$ relation at $z=0.61$ with the ACT sample
+    \protect\citep{2013JCAP...07..008H} color-coded by redshift.}}
 \label{fig:SZ_M}
-\end{figure}
-
-\begin{figure*} 
-\centering
-\includegraphics[width=0.48\textwidth]{figures/sz_m_SPT.eps}
-\includegraphics[width=0.48\textwidth]{figures/sz_m_ACT.eps}
-\caption{{\bf SZ scaling relation of our sample at $z=0.61$ compared with the SPT and ACT results. 
-  Triangles show the MultiDark sample (limited to the mass range covered by observations) 
-  while the crosses represent the observational result. \emph{Left.} Comparison with the 
-  SPT sample \protect\citep{2013ApJ...763..127R} color-coded by redshift. 
-  $Y_{\rmn{SZ, SPT}}$ is given within an aperture of  $0.2$~h$_{70}^{-1}$~Mpc.
-  \emph{Right.} Comparison with the ACT sample \protect\citep{2013JCAP...07..008H} color-coded 
-  by redshift. $Y_{\rmn{SZ, ACT}}$ is given within an aperture of $0.42$~h$_{70}^{-1}$~Mpc.}}
-\label{fig:SZ_M_1}
 \end{figure*}
@@
 
-{\bf We additionally compare our $Y_{\rmn{SZ}}$ to the results from the South Pole 
-Telescope (SPT) and Atacama Cosmology Telescope (ACT) surveys.
-We select a subsample of SPT clusters from \cite{2013ApJ...763..127R} by taking
-only objects with confirmed redshift and signal-to-noise $\ge 5$. The resulting sample 
-consists of 115 clusters with a median redshift of 0.56 and rms 0.27. Note the much larger 
-scatter in redshift of the SPT sample with respect to the \emph{Planck} one that has 
-a rms of 0.11. \cite{2013ApJ...763..127R} provide $Y_{\rmn{SZ}}$ 
-within an aperture of $1'$, corresponding to a median radius of $0.2$~h$_{70}^{-1}$~Mpc 
-at $z = 0.56$, which we use as aperture to calculate $Y_{\rmn{SZ, SPT}}$ in our MultiDark sample.
+{\bf In the right panel of Fig.~\ref{fig:SZ_M}, we compare our scaling relation
+  to the ACT sample overlapping with the Sloan Digital Sky Survey stripe 82
+  \citep{2013JCAP...07..008H}. \qc{Fabio: compare mean and scatter of ACT relation!}
 
-In the left panel of Fig.~\ref{fig:SZ_M_1}, we compare the SPT cluster sample to our 
-scaling relation at $z = 0.61$. We color-coded the SPT clusters in order to show that the SPT 
-selection function is nearly redshift-independent. The fact that the angular size of galaxy clusters 
-decreases with redshift is an advantage for SPT due to its small beam, in fact, higher-redshift clusters 
-are less confused by primary CMB fluctuations \citep{2013ApJ...763..127R}. This effect is inverse 
-for \emph{Planck} due to its larger beam. We can conclude that while our $Y_{\rmn{SZ}}-M_{500}$ 
-scaling relation compare well to the median SPT cluster population, the SPT sample has a too
-large scatter to be well represented by single MultiDark snapshots.
-
-In the right panel of Fig.~\ref{fig:SZ_M_1}, we compare our scaling relation to
-the ACT sample overlapping with the Sloan Digital Sky Survey stripe 82 
-\citep{2013JCAP...07..008H}. This sample has a median redshift of 0.58 with rms 
-of 0.28. \cite{2013JCAP...07..008H} provides $Y_{\rmn{SZ}}$ within $R_{500}$, which
-median, $0.42$~h$_{70}^{-1}$~Mpc, is almost half of ours at the
-MultiDark snapshot $z=0.61$. Therefore, we use an aperture of $0.42$~h$_{70}^{-1}$~Mpc
-to calculate our $Y_{\rmn{SZ, ACT}}$. 
-The fact that our $R_{500}$ does not compare well with the ACT values, while it does with 
-\emph{Planck}, may be explained as follows. We adopt the ACT measurements derived from 
-the 148~GHz data assuming that the cluster pressure is described by the universal 
-profile of \cite{2010A&A...517A..92A}. In contrast, \cite{2013arXiv1303.5080P}
-derived $R_{500}$ from X-ray measurements of $M_{500}$, similarly to
-our approach of constructing gas densities from an X-ray sample of clusters.
-
-Summarizing, our SZ scaling relations compare very well to the result from
-the \emph{Planck} collaboration. However, the comparison with the SPT and 
-ACT samples is not as straightforward due to the different selection function 
-of these telescopes with respect to \emph{Planck}, which results in a much
-more (redshift) non-homogeneous sample. Nevertheless, our mock clusters 
-can reproduce well the median SPT and ACT populations. A more detailed
-comparison would need the generation of light-cone mock catalogs,
-including instrumental effects, which is beyond the scope of this 
-work.}
+  Overall, there is reassuring agreement between our phenomenological model and
+  the SZ data of the \emph{Planck} and ACT collaborations.  }
 
@@
 
-{\bf As a final product of this work, we construct cosmological complete mock catalogs of galaxy clusters, at the different redshifts of 
-Table~\ref{tab:z}, for $M_{200}\geq1\times10^{14}$~$h^{-1}$~M$_{\odot}\approx1.4\times10^{14}$~$h_{70}^{-1}$~M$_{\odot}$.
-We make these catalogs publicly available through the MultiDark database 
-(www.multidark.org) where we will also post possible updates.
+{\bf As a final product of this work, we construct cosmologically complete mock
+  catalogs of galaxy clusters at different redshifts (see Table~\ref{tab:z}) for
+  $M_{200}\geq1\times10^{14}$~$h^{-1}\rmn{M}_{\odot}
+  \approx1.4\times10^{14}$~$h_{70}^{-1}$~M$_{\odot}$.  We make these catalogs
+  publicly available through the MultiDark database (www.multidark.org) where we
+  will also post possible updates.
 
-Our catalogs contain all the information regarding the DM properties of each object as 
-given by the corresponding original MultiDark BDM halo catalogs. Additionally, we include the
-following information:
+  Our catalogs contain all the information regarding the DM properties of each
+  object as given by the corresponding original MultiDark BDM halo
+  catalogs. Additionally, we include the following information:
 
@@
 \item the central gas density $\rho_{\rmn{gas},0}$ with which the full ICM radial profile can be calculated as in Section~\ref{sec:3},
-\item the bolometric X-ray thermal bremsstrahlung luminosity $L_{\rmn{X, bol}}$ within $R_{500}$,
+\item the bolometric X-ray thermal bremsstrahlung luminosity $L_{\rmn{X, bol}}$
+  within $R_{500}$, and
 \item the $Y_{\rmn{X}}$ and $Y_{\rmn{SZ}}$ parameters within $R_{500}$.
@@
 
-In Paper~II, we present a model to calculate the possible radio and gamma-ray emission of 
-clusters as result of the cosmic-ray (CR) proton-proton interactions with the ICM. We refer
-to that paper for all the details. However, we want to point out that our mock catalogs include also:
+In Paper~II, we present a model to calculate the possible radio and gamma-ray
+emission of clusters as result of the cosmic-ray (CR) proton-proton interactions
+with the ICM. We refer to that paper for all the details. However, we want to
+point out that our mock catalogs also include:
 
@@
 \item the CR-to-thermal pressure averaged over the cluster volume within $R_{500}$,
-\item the synchrotron radio luminosity, within $R_{500}$, at 120~MHz and 1.4~GHz,
+\item the hadronic and leptonic components of the synchrotron radio luminosity,
+  within $R_{500}$, at 120~MHz and 1.4~GHz, \qc{[Fabio: we should add the
+    leptonic component to the catalogs.]}
 \item the gamma-ray luminosity, within $R_{500}$, above 100~MeV and 100~GeV.
@@
 
-We warn, however, that our mock catalogs are not appropriate for all purposes. In fact, they are 
-representations of the average cluster population. While they are very useful as baseline for new 
-simulations, to test new observations, and for the non-thermal modeling of clusters, they are not 
-appropriate to perform detailed cosmology studies. A carefully modeling of the response function 
-of the considered instrument would be needed for such a purpose, together with the generation of 
-light-cone mock catalogs. Nevertheless, for flux-complete surveys, our mock catalogs are
-certainly good tools to test against models. Finally, keep also in mind that our approach is based on 
-X-ray observations of clusters at low redshift \citep{2008A&A...487..431C,2009ApJ...693.1142S}, 
-and, for simplicity, we adopted a self-similar redshift evolution.
-}
+We note that our mock catalogs are not appropriate for all purposes because they
+represent the average cluster population. While they are very useful as baseline
+for new simulations, for comparisons to new observational samples, and for
+non-thermal modeling of clusters, they are not appropriate to perform detailed
+cosmology studies. Careful modeling of the response function of the considered
+instrument in combination with light-cone mock catalogs would be required in this
+case. Nevertheless, for volume-complete surveys, our mock catalogs will
+certainly serve as valuable tools.  }
 
@@
 
-{\bf We build a complete cosmological sample of galaxy clusters from the MultiDark 
-$N$-body simulation with redshifts ranging from $z = 0$ to 1. We construct a 
-\emph{phenomenological} model for the cluster-gas distribution. This is characterized 
+{\bf We build a complete cosmological sample of galaxy clusters from the
+  MultiDark $N$-body simulation with redshifts ranging from $z = 0$ to 1 and
+  construct a \emph{phenomenological} model for the ICM. This is characterized
   by X-ray-inferred (CCC and NCCC) gas profiles (taken from the REXCESS sample)
-and a cluster-mass-dependent gas fraction. We assign such a (cluster mass-dependent) 
-gas density profile to each DM halo in our sample and sort it into the NCCC/CCC populations 
-according to a dynamical disturbance parameter that is calculated from the DM distribution.
-We obtain cosmologically complete mock catalogs of galaxy clusters that matches the 
-observed $L_{\rmn{X, bol}}$-to-$M_{500}$, $Y_{\rmn{X}}$-to-$M_{500}$, and 
-$Y_{\rmn{SZ}}$-to-$M_{500}$ relations, as well as the X-ray luminosity function. 
-In the companion Paper~II, we additionally calculate the possible radio and gamma-ray 
-emission coming from the CR hadronic interactions with the ICM in the clusters.
+  and a cluster mass-dependent gas fraction. We assign such a (cluster
+  mass-dependent) gas density profile to each DM halo in our sample and sort it
+  into the NCCC/CCC populations according to a dynamical disturbance parameter
+  that is calculated from the DM distribution.  We obtain cosmologically
+  complete mock catalogs of galaxy clusters that matches the observed
+  $L_{\rmn{X, bol}}-M_{500}$, $Y_{\rmn{X}}-M_{500}$, and $Y_{\rmn{SZ}}-M_{500}$
+  relations, as well as the X-ray luminosity function.  In the companion
+  Paper~II, we additionally present a model for the radio and gamma-ray emission
+  as a result of CR hadronic interactions with the ICM.
 
-Eventually, we provide a cosmologically complete multi-frequency mock catalog for the (non-)thermal 
-cluster emission at different redshifts. We make these catalogs publicly and freely available 
-on-line through the MultiDark database (www.multidark.org). We warn that these catalogs
-are not appropriate for detailed cosmological studies in their (present) published form as 
-carefully modeling of the response function of the considered instrument would be needed 
-for such a purpose, together with the generation of light-cone mock catalogs. Note also that 
-our approach is based on X-ray observations at low redshift, and we adopted a self-similar redshift 
-evolution. Nevertheless, our mock catalogs are good representations of the average cluster population,
-and we hope that the  community can make valuable use of these catalogs in synergy with the future radio, 
-X-ray and gamma-ray data.}
+  We provide a cosmologically complete multi-frequency mock catalog for the
+  (non-)thermal cluster emission at different redshifts. We make these catalogs
+  publicly and freely available on-line through the MultiDark database
+  (www.multidark.org). Our mock catalogs are good representations of the average
+  cluster population. They allow quantitative comparisons of future
+  hydrodynamical simulations, the modeling of non-thermal cluster emission from
+  radio to gamma-rays, and the construction of cluster mock catalogs of the
+  (non-)thermal cluster emission. We emphasize that the catalogs are not suited
+  for detailed cosmological studies in their (present) published form, which do
+  not address any survey response functions nor provide light-cone mock
+  catalogs. However, future surveys should be able to test the underlying assumptions
+  of our modeling approach, which is based on X-ray observations of clusters at
+  low redshift ($z<0.2$) and adopts self-similar redshift evolution for
+  extrapolating to higher redshifts. We hope that the community can make
+  valuable use of these catalogs in synergy with the future radio, X-ray and
+  gamma-ray data.}
 
@@
 \section*{Acknowledgments}
-We thank Harald Ebeling, Stefan Gottl{\"o}berg, Anatoly Klypin, Andrey Kravtsov, Adam Mantz, 
-Frazer Pearce, Jos\'e Alberto Rubi\~no, and Gustavo Yepes, for the useful discussions and advices. 
-We also thank the MultiDark database people, in particular Adrian Partl and Kristin Riebe. 
-F.Z.{\ }acknowledges the CSIC financial support as a JAE-Predoc grant of the 
-program ``Junta para la Ampliaci\'on de Estudios'' co-financed by the FSE. 
-F.Z.{\ }acknowledges the hospitality of the Leiden Observatory during his stay.
-F.Z.{\ }and F.P.{\ } thank the support of the Spanish MICINN's Consolider-Ingenio 2010 Programme under
-grant MultiDark CSD2009-00064. C.P.{\ }gratefully acknowledges financial support
-of the Klaus Tschira Foundation. The MultiDark Database used in this paper and
-the web application providing online access to it were constructed as part of
-the activities of the German Astrophysical Virtual Observatory as result of a
+We thank Harald Ebeling, Stefan Gottl{\"o}berg, Anatoly Klypin, Andrey Kravtsov,
+Adam Mantz, Frazer Pearce, Jos\'e Alberto Rubi\~no, and Gustavo Yepes, for the
+useful discussions. We also thank the MultiDark database people, in particular
+Adrian Partl and Kristin Riebe.  F.Z.{\ }acknowledges the CSIC financial support
+as a JAE-Predoc grant of the program ``Junta para la Ampliaci\'on de Estudios''
+co-financed by the FSE.  F.Z.{\ }acknowledges the hospitality of the Leiden
+Observatory during his stay.  F.Z.{\ }and F.P.{\ } thank the support of the
+Spanish MICINN's Consolider-Ingenio 2010 Programme under grant MultiDark
+CSD2009-00064. C.P.{\ }gratefully acknowledges financial support of the Klaus
+Tschira Foundation. The MultiDark Database used in this paper and the web
+application providing online access to it were constructed as part of the
+activities of the German Astrophysical Virtual Observatory as result of a
 collaboration between the Leibniz-Institute for Astrophysics Potsdam (AIP) and
@@
 of any given cluster from its total mass. 
-}
+%
+ACT SZ:
+This sample has a median redshift of 0.58 with
+  rms of 0.28. \cite{2013JCAP...07..008H} provides $Y_{\rmn{SZ}}$ within
+  $R_{500}$, which median, $0.42$~h$_{70}^{-1}$~Mpc, is almost half of ours at
+  the MultiDark snapshot $z=0.61$. Therefore, we use an aperture of
+  $0.42$~h$_{70}^{-1}$~Mpc to calculate our $Y_{\rmn{SZ, ACT}}$.  The fact that
+  our $R_{500}$ does not compare well with the ACT values, while it does with
+  \emph{Planck}, may be explained as follows. We adopt the ACT measurements
+  derived from the 148~GHz data assuming that the cluster pressure is described
+  by the universal profile of \cite{2010A&A...517A..92A}. In contrast,
+  \cite{2013arXiv1303.5080P} derived $R_{500}$ from X-ray measurements of
+  $M_{500}$, similarly to our approach of constructing gas densities from an
+  X-ray sample of clusters.
+%
+Summarizing, our SZ scaling relations compare very well to the result from
+the \emph{Planck} collaboration. However, the comparison with the SPT and 
+ACT samples is not as straightforward due to the different selection function 
+of these telescopes with respect to \emph{Planck}, which results in a much
+more (redshift) non-homogeneous sample. Nevertheless, our mock clusters 
+can reproduce well the median SPT and ACT populations. A more detailed
+comparison would need the generation of light-cone mock catalogs,
+including instrumental effects, which is beyond the scope of this 
+work.}

### 2013-09-28 paper1.tex
typo corrected

@@
 \author[F. Zandanel, C. Pfrommer and F. Prada]{
-Fabio Zandanel$^{1,2}$, Christoph Pfrommer$^{3}$ and Francisco Prada$^{4,5,1}$\\
+Fabio Zandanel$^{1,2}$, Christoph Pfrommer$^{3}$ and Francisco Prada$^{4,5,2}$\\
 $^{1}$GRAPPA Institute, University of Amsterdam, Science Park 904, 1098XH Amsterdam, Netherlands, f.zandanel@uva.nl\\

### 2013-09-29 paper1.tex
conclusions revised

@@
     cluster catalog by assigning our gas density model to each cluster halo of
-    the large collisionless $N$-body simulation MultiDark. Our clusters
-    are identified with cool-core and non cool-core clusters according to a
+    the large collisionless $N$-body simulation MultiDark. Our clusters are
+    identified with cool-core and non cool-core clusters according to a
     dynamical disturbance parameter. We demonstrate that our gas model matches
@@
     as the X-ray luminosity function, thus enabling a reliable mock catalog for
-    present and future instruments.  In a companion paper, we apply our catalogs
-    to calculate non-thermal radio and gamma-ray emission of galaxy clusters. We
-    make our cosmologically complete multi-frequency mock catalogs for the
-    (non-)thermal cluster emission at different redshifts publicly and freely
-    available online through the MultiDark database.}
+    present surveys and forecasts for future instruments. In a companion paper,
+    we apply our catalogs to calculate non-thermal radio and gamma-ray emission
+    of galaxy clusters. We make our cosmologically complete multi-frequency mock
+    catalogs for the (non-)thermal cluster emission at different redshifts
+    publicly and freely available online through the MultiDark database.}
 \end{abstract}
@@
 
-We note that our mock catalogs are not appropriate for all purposes because they
-represent the average cluster population. While they are very useful as baseline
-for new simulations, for comparisons to new observational samples, and for
-non-thermal modeling of clusters, they are not appropriate to perform detailed
+We note that our mock catalogs are not appropriate for all purposes because the
+density profile shapes that we adopt in our model represent the average cluster
+population of cool-core and non cool-core systems (while we account for scatter
+in the gas mass fractions, i.e., the normalization of the profiles). As such,
+the models are very useful as a baseline for comparisons to new hydrodynamical
+simulations and to new observational samples as well as for non-thermal modeling
+of clusters. On the contrary, they are not appropriate to perform detailed
 cosmology studies. Careful modeling of the response function of the considered
-instrument in combination with light-cone mock catalogs would be required in this
-case. Nevertheless, for volume-complete surveys, our mock catalogs will
+instrument in combination with light-cone mock catalogs would be required in
+this case. Nevertheless, for volume-complete surveys, our mock catalogs will
 certainly serve as valuable tools.  }
@@
   into the NCCC/CCC populations according to a dynamical disturbance parameter
-  that is calculated from the DM distribution.  We obtain cosmologically
-  complete mock catalogs of galaxy clusters that matches the observed
+  that is calculated from the DM distribution. Applying the model to our sample
+  of cluster halos, we obtain volume complete mock catalogs for the
+  thermal (SZ and X-ray) cluster emission. Our mock catalogs match the observed
   $L_{\rmn{X, bol}}-M_{500}$, $Y_{\rmn{X}}-M_{500}$, and $Y_{\rmn{SZ}}-M_{500}$
@@
 
-  We provide a cosmologically complete multi-frequency mock catalog for the
-  (non-)thermal cluster emission at different redshifts. We make these catalogs
+  We provide cosmologically complete multi-frequency mock catalogs for the
+  (non-)thermal cluster emission at different redshifts and make these catalogs
   publicly and freely available on-line through the MultiDark database
-  (www.multidark.org). Our mock catalogs are good representations of the average
-  cluster population. They allow quantitative comparisons of future
-  hydrodynamical simulations, the modeling of non-thermal cluster emission from
-  radio to gamma-rays, and the construction of cluster mock catalogs of the
-  (non-)thermal cluster emission. We emphasize that the catalogs are not suited
+  (www.multidark.org). Our mock catalogs are based on density profile shapes
+  that represent the average cluster population of cool-core and non cool-core
+  systems (while we account for scatter in the gas mass fractions, i.e., the
+  normalization of the profiles). As a result, our model does not fully exploit
+  the true variance across the average profile shapes which may result in a
+  limited variance of thermal cluster observables.  Hence, the mock catalogs
+  will allow quantitative comparisons to future hydrodynamical simulations and
+  forecasts for future surveys.  We emphasize that the catalogs are not suited
   for detailed cosmological studies in their (present) published form, which do
   not address any survey response functions nor provide light-cone mock
-  catalogs. However, future surveys should be able to test the underlying assumptions
-  of our modeling approach, which is based on X-ray observations of clusters at
-  low redshift ($z<0.2$) and adopts self-similar redshift evolution for
-  extrapolating to higher redshifts. We hope that the community can make
+  catalogs. However, future surveys should be able to test the underlying
+  assumptions of our modeling approach, which is based on X-ray observations of
+  clusters at low redshift ($z<0.2$) and adopts self-similar redshift evolution
+  for extrapolating to higher redshifts. We hope that the community can make
   valuable use of these catalogs in synergy with the future radio, X-ray and

### 2013-09-30 paper1.tex
Fabio's changes included

@@
   core clusters (CCC) while others have cooling times that can be longer than
-  the age of the Universe, forming the non-cool core cluster (NCC) population
+  the age of the Universe, forming the non-cool core cluster (NCCC) population
   \citep{2009ApJS..182...12C,2010A&A...513A..37H}. Several physical processes
@@
   each object, together with its (non-)thermal emission at different
-  frequencies. This mock catalog matches existing observations and should be
-  eminent in making predictions for future radio surveys.
+  frequencies.
 
@@
   $\Delta=200$ or 500 times the \emph{critical} density of the Universe. We
-  adopt density parameters of $\Omega_{\rmn{m}}=0.3$, $\Omega_{\Lambda}=0.7$ and
+  adopt density parameters of $\Omega_{\rmn{m}}=0.27$, $\Omega_{\Lambda}=0.73$ and
   today's Hubble constant of $H_0 = 100\, h_{70}$~km~s$^{-1}$~Mpc$^{-1}$ where
@@
 
-So far, we used a well-observed representative sample of X-ray clusters
+{\bf So far, we used a well-observed representative sample of X-ray clusters
 (REXCESS) that was supplemented by X-ray data on gas mass fractions to construct
@@
 include the observed $L_{\rmn{bol}} - M_{500}$ relation, the $Y_X - M_{500}$
-relation, and the XLF.
+relation, and the XLF.}
 
@@
 \item the CR-to-thermal pressure averaged over the cluster volume within $R_{500}$,
-\item the hadronic and leptonic components of the synchrotron radio luminosity,
-  within $R_{500}$, at 120~MHz and 1.4~GHz, \qc{[Fabio: we should add the
-    leptonic component to the catalogs.]}
+\item the radio synchrotron luminosity of secondary electrons that are produced
+  in hadronic CRp-p interactions, within $R_{500}$, at 120~MHz and 1.4~GHz,
 \item the gamma-ray luminosity, within $R_{500}$, above 100~MeV and 100~GeV.
@@
 \section*{Acknowledgments}
-We thank Harald Ebeling, Stefan Gottl{\"o}berg, Anatoly Klypin, Andrey Kravtsov,
-Adam Mantz, Frazer Pearce, Jos\'e Alberto Rubi\~no, and Gustavo Yepes, for the
-useful discussions. We also thank the MultiDark database people, in particular
-Adrian Partl and Kristin Riebe.  F.Z.{\ }acknowledges the CSIC financial support
-as a JAE-Predoc grant of the program ``Junta para la Ampliaci\'on de Estudios''
-co-financed by the FSE.  F.Z.{\ }acknowledges the hospitality of the Leiden
-Observatory during his stay.  F.Z.{\ }and F.P.{\ } thank the support of the
-Spanish MICINN's Consolider-Ingenio 2010 Programme under grant MultiDark
-CSD2009-00064. C.P.{\ }gratefully acknowledges financial support of the Klaus
-Tschira Foundation. The MultiDark Database used in this paper and the web
-application providing online access to it were constructed as part of the
-activities of the German Astrophysical Virtual Observatory as result of a
-collaboration between the Leibniz-Institute for Astrophysics Potsdam (AIP) and
-the Spanish MultiDark Consolider Project CSD2009-00064. The Bolshoi and
+We thank Nick Battaglia, Harald Ebeling, Stefan Gottl{\"o}berg, Anatoly Klypin,
+Andrey Kravtsov, Adam Mantz, Frazer Pearce, Jos\'e Alberto Rubi\~no, and Gustavo
+Yepes, for the useful discussions. We also thank the MultiDark database people,
+in particular Adrian Partl and Kristin Riebe.  F.Z.{\ }acknowledges the CSIC
+financial support as a JAE-Predoc grant of the program ``Junta para la
+Ampliaci\'on de Estudios'' co-financed by the FSE.  F.Z.{\ }acknowledges the
+hospitality of the Leiden Observatory during his stay.  F.Z.{\ }and F.P.{\ }
+thank the support of the Spanish MICINN's Consolider-Ingenio 2010 Programme
+under grant MultiDark CSD2009-00064. C.P.{\ }gratefully acknowledges financial
+support of the Klaus Tschira Foundation. The MultiDark Database used in this
+paper and the web application providing online access to it were constructed as
+part of the activities of the German Astrophysical Virtual Observatory as result
+of a collaboration between the Leibniz-Institute for Astrophysics Potsdam (AIP)
+and the Spanish MultiDark Consolider Project CSD2009-00064. The Bolshoi and
 MultiDark simulations were run on the NASA's Pleiades supercomputer at the NASA

### 2013-10-02 paper1.tex
table
rewrote sections 5 and 7

@@
   galaxies, hot ($1-10$~keV) gas and dark matter (DM) contribute roughly 5, 15
-  and 80\%, respectively. If the thermal properties of the intracluster medium
+  and 80 per cent, respectively. If the thermal properties of the intracluster medium
   (ICM) were solely determined by the gravity of the system, then clusters would
@@
   radio, hard X-ray, and gamma-ray band) of current and future surveys. Such a
-  model for the ICM needs to be complemented by a sample of cluster halos, which
+  model for the ICM needs to be applied to a sample of cluster halos, which
   can either be obtained by means of analytical expressions for the cluster mass
@@
  0.0~~ &  13763\\
+ 0.05 &  13103\\
  0.1~~ &  12398\\
+ 0.16 & 11419\\
  0.2~~ &  10783\\ 
+ 0.27 & ~~9772\\
+ 0.32 & ~~9039\\
+ 0.37 & ~~8197\\
  0.4~~ &   ~~7789\\
+ 0.47 & ~~6957\\
+ 0.53 & ~~6079\\ 
  0.61 &  ~~5187\\ 
+ 0.69 & ~~4288\\
  0.78 &  ~~3372\\ 
+ 0.89 & ~~2575\\
  1.0~~ &  ~~1803\\[0.5em]
@@
 profiles of the REXCESS sample in log-log space, separating them in the two
-categories of NCCCs and CCCs as shown in Fig.~\ref{fig:gas_profiles}.  We
-obtain $n_{\rmn{0,NCCC}} = 1.02\times10^{-2}$~$h_{70}^{1/2}$~cm$^{-3}$,
+categories of NCCCs and CCCs as shown in Fig.~\ref{fig:gas_profiles}.  We obtain
+$n_{\rmn{0,NCCC}} = 1.02\times10^{-2}$~$h_{70}^{1/2}$~cm$^{-3}$,
 $n_{\rmn{0,CCC}} = 8.32\times10^{-3}$~$h_{70}^{1/2}$~cm$^{-3}$,
 $\beta_{\rmn{NCCC}} = -0.093$, and $\beta_{\rmn{CCC}} = 0.592$. The resulting
-fits are shown in blue and red for the NCCC and CCC population, respectively.
+fits are shown in blue and red for the NCCC and CCC population,
+respectively. {\bf As a cautionary remark, we emphasize that our model is only
+  valid within $R_{500}$ and more work would be needed to extrapolate it to
+  larger cluster radii. Those cluster regions are characterized by a steadily
+  increasing level of kinetic-to-thermal pressure support
+  \citep[e.g.,][]{2009ApJ...705.1129L, 2012ApJ...758...74B}, density clumping
+  \citep{2011ApJ...731L..10N, 2012arXiv1209.4082B}, and asphericity and
+  ellipticity of the halo morphologies \citep{2012arXiv1209.4082B}, in
+  particular beyond the virial radius where the filamentary cosmic web connects
+  to the cluster interiors.}
 
@@
 the halo has experienced a recent merger or not. Current observations reveal a ratio
-of NCCCs and CCCs of about $50\%$ (e.g., \citealp{2007A&A...466..805C,
+of NCCCs and CCCs of about 50 per cent (e.g., \citealp{2007A&A...466..805C,
   2009MNRAS.395..764S}). Since there is a correlation between merging clusters
@@
 \subsection{Scaling Relations}
+\label{sec:Xscaling}
 
@@
   temperature of each cluster. As a result, we fall short of the observed
-  luminosity by a mean (median) of about $21\%$ ($20\%$). This is acceptable
-  considering that we do not permit the parameters $R_{\rmn{c}}$, $\alpha$ and
-  $\delta$ to vary between different objects. Additionally, we neglect atomic
-  line emission which may give a noticeable contribution, in particularly for
-  low-mass clusters and in the cluster outskirts of larger systems.}  To assign
-a temperature to our model clusters (that is needed for calculating
-$L_{\rmn{bol}}$ and $Y_{\rmn{X}}$), we adopt the $T-M_{500}$ relation by
-\cite{2010MNRAS.406.1773M},
+  luminosity by a mean (median) of about 21 per cent (20 per cent). This is
+  acceptable considering that we do not permit the parameters $R_{\rmn{c}}$,
+  $\alpha$ and $\delta$ to vary between different objects. Additionally, we
+  neglect atomic line emission which may give a noticeable contribution, in
+  particularly for low-mass clusters and in the cluster outskirts of larger
+  systems.}  To assign a temperature to our model clusters (that is needed for
+calculating $L_{\rmn{bol}}$ and $Y_{\rmn{X}}$), we adopt the $T-M_{500}$
+relation by \cite{2010MNRAS.406.1773M},
 \begin{equation}
@@
 model agrees nicely at the high-mass end, but underpredicts the observed scaling
-at low masses by about $20\%$ (at the 1-$\sigma$ level). This is the same level
+at low masses by about 20 per cent (at the 1-$\sigma$ level). This is the same level
 of deviation from the data as in the case of $L_{\rmn{X}}$, which is more
@@
 account the observational biases.\footnote{The mean (median) difference at $z=0$
-  between $L_{\rmn{bol}}$ within $R_{200}$ or within $R_{500}$ is $\approx 5\%$
-  ($\approx 7\%$). While $L_{\rmn{bol}}$ refers to the quantity calculated
-  within $R_{500}$, we note that the XLF for luminosities calculated within
-  $R_{200}$ will be barely changed.} This means that applying the Malmquist and
-Eddington-bias-corrected $L_{\rmn{X}}-M_{500}$ relation by
+  between $L_{\rmn{bol}}$ within $R_{200}$ or within $R_{500}$ is $\approx 5$
+  per cent ($\approx 7$ per cent). While $L_{\rmn{bol}}$ refers to the quantity
+  calculated within $R_{500}$, we note that the XLF for luminosities calculated
+  within $R_{200}$ will be barely changed.} This means that applying the
+Malmquist and Eddington-bias-corrected $L_{\rmn{X}}-M_{500}$ relation by
 \cite{2010MNRAS.406.1773M} directly to the MultiDark mass function and
@@
 In the left panel of Fig.~\ref{fig:SZ_M}, we compare the $Y_{\rmn{SZ}}-M_{500}$
-relation in our model (following \citealp{2012ApJ...758...74B}, equation~3) with
+relation of our model (following \citealp{2012ApJ...758...74B}, equation~3) with
 the observed scaling relation by the \cite{2013arXiv1303.5080P}. {\bf We use the
   \emph{Planck} COSMO sample, which is Malmquist-bias corrected and has a median
-  redshift of $0.18$. Hence, we compare the data to our $z=0.2$ relation}. Our
-model reproduces the data remarkably well, except for the high-mass end where
-our simulations have a weaker constraining power due to the smaller box size in
-comparison to the survey volume of {\em Planck}. We find a scatter of
-$\sigma_{yx} \approx 0.11$ which compares well with the \emph{Planck} result of
-$\sigma_{yx} \approx 0.08$. In Table~\ref{tab:YSZfits}, we report our SZ scaling
-relations for different redshifts.
+  redshift of $0.18$, and compare this to our $z=0.2$ relation}. Our model
+reproduces the normalization of the scaling relation remarkably well, except for
+the high-mass end where our simulations have a weaker constraining power due to
+the smaller box size in comparison to the survey volume of {\em Planck}.  {\bf
+  However, the slope of our $Y_{\rmn{SZ}}-M_{500}$ relation ($1.59\pm0.01$) is
+  shallower in comparison to the self-similar slope ($5/3$) as well as the
+  observed slope of the \emph{Planck} COSMO sample. We can analytically
+  understand the cluster-mass scaling of our model by considering its
+  mass-dependent quantities, namely $Y_{\rmn{SZ}}\propto M_{500} f_{\rmn{gas}}
+  T \propto M_{500}^{1.595}$. In particular, we can trace back the
+  shallower slope to the adopted temperature scaling of our model
+  ($T\approx T_{\rmn{ci}}\propto M_{500}^{0.46}$), which includes the cluster core region
+  and yields a shallower mass scaling in comparison to the self-similar
+  expectation ($T\propto M_{500}^{2/3}$). The temperature scaling is only
+  partially countered by the scaling of the gas mass fraction with cluster mass,
+  $f_{\rmn{gas}}\propto M_{500}^{0.135}$. To improve upon this, we would have to
+  account for a slightly steeper temperature-mass scaling (e.g., using a
+  centrally excised temperature scaling, see \citealt{2010MNRAS.406.1773M}) in
+  the outer cluster parts that are of relevance for the SZ flux, as explained in
+  Sect.~\ref{sec:Xscaling}. }  We find a scatter of $\sigma_{yx} \approx 0.11$
+which compares well with the \emph{Planck} result of $\sigma_{yx} \approx
+0.08$. In Table~\ref{tab:YSZfits}, we report our SZ scaling relations for
+different redshifts.
 
@@
 \caption{{\bf Comparison of our SZ scaling relations (grey triangles) with
-    data. \emph{Left.}  We compare our $Y_{\rmn{SZ}}-M$ relation at $z=0.2$ with
-    the {\em Planck} data \citep{2013arXiv1303.5080P}, which have a median
-    redshift of about $0.18$.  The black crosses represent the $Y_{\rmn{SZ}}$
-    median values of our sample for a given mass bin (indicated by horizontal
-    error bars), and the vertical error bars represent the standard deviation
-    within a bin. The bottom panels show the relative difference to the
-    observational scaling relations. \emph{Right.} We compare our
-    $Y_{\rmn{SZ}}-M$ relation at $z=0.61$ with the ACT sample
-    \protect\citep{2013JCAP...07..008H} color-coded by redshift.}}
+    data. The bottom panels show the relative difference to the observational
+    scaling relations. \emph{Left.}  We compare our $Y_{\rmn{SZ}}-M$ relation at
+    $z=0.2$ with the {\em Planck} data \citep[blue,][]{2013arXiv1303.5080P},
+    which have a median redshift of about $0.18$.  The black crosses represent
+    the $Y_{\rmn{SZ}}$ median values of our sample for a given mass bin
+    (indicated by horizontal error bars), and the vertical error bars represent
+    the standard deviation within a bin. \emph{Right.} We compare our
+    $Y_{\rmn{SZ}}-M$ relation at $z=0.53$ with the ACT sample
+    \protect\citep[blue,][]{2013JCAP...07..008H} assuming a self-similar
+    redshift evolution.}}
 \label{fig:SZ_M}
@@
   to the ACT sample overlapping with the Sloan Digital Sky Survey stripe 82
-  \citep{2013JCAP...07..008H}. \qc{Fabio: compare mean and scatter of ACT relation!}
-
-  Overall, there is reassuring agreement between our phenomenological model and
-  the SZ data of the \emph{Planck} and ACT collaborations.  }
+  \citep{2013JCAP...07..008H}, which has a median redshift of $z=0.53$. Again,
+  the slope of our modeled scaling relation is somewhat shallower in comparison
+  to the observed slope. Most strikingly, there appears to be a 30 per cent
+  offset of the scaling relations, which could be due to a number of reasons. On
+  the data side, these could include possible selection effects of the different
+  cluster samples or possible biases associated with density clumping and/or
+  non-thermal pressure contributions inherited from the X-ray informed
+  post-processing that was employed by the ACT Collaboration to construct their
+  $Y_{500}$ estimates. However, this could also indicate that our presented
+  model is too simplistic to capture the rich cluster physics and potentially
+  may even signal deviations from the assumed self-similar redshift evolution
+  (since ACT sample probes on average higher redshift and less massive clusters
+  in comparison to the {\em Planck} sample). Overall, there is reasonable
+  agreement between our phenomenological model and the SZ data of the
+  \emph{Planck} and ACT collaborations.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions}
+\section{Discussion and Conclusions}
 \label{sec:7}
@@
   by X-ray-inferred (CCC and NCCC) gas profiles (taken from the REXCESS sample)
-  and a cluster mass-dependent gas fraction. We assign such a (cluster
+  and a cluster mass-dependent gas fraction. Note that our model is calibrated
+  off X-ray observables within $R_{500}$. More work would be needed to
+  extrapolate the model to larger cluster radii that are characterised by an
+  increased complexity, which manifests itself in a larger kinetic-to-thermal
+  pressure support, an increased level of density clumping, as well as cluster
+  asphericity and ellipticity. In our model, we assign a (cluster
   mass-dependent) gas density profile to each DM halo in our sample and sort it
@@
   that is calculated from the DM distribution. Applying the model to our sample
-  of cluster halos, we obtain volume complete mock catalogs for the
-  thermal (SZ and X-ray) cluster emission. Our mock catalogs match the observed
-  $L_{\rmn{X, bol}}-M_{500}$, $Y_{\rmn{X}}-M_{500}$, and $Y_{\rmn{SZ}}-M_{500}$
-  relations, as well as the X-ray luminosity function.  In the companion
-  Paper~II, we additionally present a model for the radio and gamma-ray emission
-  as a result of CR hadronic interactions with the ICM.
+  of cluster halos, we obtain volume complete mock catalogs for the thermal (SZ
+  and X-ray) cluster emission. Our mock catalogs match the observed X-ray
+  luminosity function as well as the $L_{\rmn{X, bol}}-M_{500}$,
+  $Y_{\rmn{X}}-M_{500}$, and $Y_{\rmn{SZ}}-M_{500}$ relations well.
 
-  We provide cosmologically complete multi-frequency mock catalogs for the
-  (non-)thermal cluster emission at different redshifts and make these catalogs
-  publicly and freely available on-line through the MultiDark database
+  However, there are some notable deviations among the different observational
+  scaling relations and our model, which may either point to observational
+  sample selection effects that are not accounted for or missing complexity of
+  our model. This model was specifically constructed to provide a reliable
+  description of the gas density, which necessarily implies a great match of the
+  mock X-ray observables (scaling relations and luminosity functions) as well as
+  the low-redshift and massive cluster sample probed by {\em Planck}. However,
+  we note that our model has a somewhat shallower slope of the
+  $Y_{\rmn{SZ}}-M_{500}$ relation, which implies that the X-ray inferred
+  deviations of self-similarity on small scales become weaker on the larger
+  scales probed through the SZ effect. Moreover, our model overpredicts the
+  normalization of the ACT $Y_{\rmn{SZ}}-M_{500}$ relation (at $z=0.53$) by
+  about 30 per cent. This could either indicate possible selection effects of
+  the different cluster samples or may even signal deviations from the assumed
+  self-similar redshift evolution.
+
+  In the companion Paper~II, we additionally present a model for the radio and
+  gamma-ray emission as a result of hadronic CR interactions with the ICM.  We
+  provide cosmologically complete multi-frequency mock catalogs for the
+  \mbox{(non-)thermal} cluster emission at different redshifts and make these
+  catalogs publicly and freely available on-line through the MultiDark database
   (www.multidark.org). Our mock catalogs are based on density profile shapes
@@
   will allow quantitative comparisons to future hydrodynamical simulations and
-  forecasts for future surveys.  We emphasize that the catalogs are not suited
-  for detailed cosmological studies in their (present) published form, which do
-  not address any survey response functions nor provide light-cone mock
-  catalogs. However, future surveys should be able to test the underlying
-  assumptions of our modeling approach, which is based on X-ray observations of
-  clusters at low redshift ($z<0.2$) and adopts self-similar redshift evolution
-  for extrapolating to higher redshifts. We hope that the community can make
-  valuable use of these catalogs in synergy with the future radio, X-ray and
-  gamma-ray data.}
+  forecasts for future surveys.  We emphasize, however, that the catalogs are
+  not suited for detailed cosmological studies in their (present) published
+  form, which do not address any survey response functions nor provide
+  light-cone mock catalogs. However, future surveys should be able to test the
+  underlying assumptions of our modeling approach, which is based on X-ray
+  observations of clusters at low redshift ($z<0.2$) and adopts self-similar
+  redshift evolution for extrapolating to higher redshifts. We hope that the
+  community can make valuable use of these catalogs in synergy with the future
+  radio, X-ray and gamma-ray data.}
 

### 2013-10-02 paper1.tex
small clean-ups

@@
   mass-dependent) gas density profile to each DM halo in our sample and sort it
-  into the NCCC/CCC populations according to a dynamical disturbance parameter
+  into NCCC/CCC populations according to a dynamical disturbance parameter
   that is calculated from the DM distribution. Applying the model to our sample
-  of cluster halos, we obtain volume complete mock catalogs for the thermal (SZ
+  of cluster halos, we obtain volume-complete mock catalogs for the thermal (SZ
   and X-ray) cluster emission. Our mock catalogs match the observed X-ray
@@
   description of the gas density, which necessarily implies a great match of the
-  mock X-ray observables (scaling relations and luminosity functions) as well as
-  the low-redshift and massive cluster sample probed by {\em Planck}. However,
-  we note that our model has a somewhat shallower slope of the
-  $Y_{\rmn{SZ}}-M_{500}$ relation, which implies that the X-ray inferred
+  resulting mock X-ray observables to data (scaling relations and luminosity
+  functions) as well as to the low-redshift and massive cluster sample probed by
+  {\em Planck}. However, we note that our model has a somewhat shallower slope
+  of the $Y_{\rmn{SZ}}-M_{500}$ relation, which implies that the X-ray inferred
   deviations of self-similarity on small scales become weaker on the larger
@@
   about 30 per cent. This could either indicate possible selection effects of
-  the different cluster samples or may even signal deviations from the assumed
+  the different cluster samples or may even signal a deviation from the assumed
   self-similar redshift evolution.
@@
   (www.multidark.org). Our mock catalogs are based on density profile shapes
-  that represent the average cluster population of cool-core and non cool-core
-  systems (while we account for scatter in the gas mass fractions, i.e., the
-  normalization of the profiles). As a result, our model does not fully exploit
-  the true variance across the average profile shapes which may result in a
-  limited variance of thermal cluster observables.  Hence, the mock catalogs
-  will allow quantitative comparisons to future hydrodynamical simulations and
-  forecasts for future surveys.  We emphasize, however, that the catalogs are
-  not suited for detailed cosmological studies in their (present) published
-  form, which do not address any survey response functions nor provide
+  that represent the {\em average} cluster population of cool-core and non
+  cool-core systems (while we account for scatter in the gas mass fractions,
+  i.e., the normalization of the profiles). As a result, our model does not
+  fully exploit the true variance across the average profile shapes which may
+  result in a limited variance of thermal cluster observables. Nevertheless, the
+  mock catalogs will allow quantitative comparisons to future hydrodynamical
+  simulations and forecasts for future surveys.  We emphasize, however, that the
+  catalogs are not suited for detailed cosmological studies in their (present)
+  published form, which do not address any survey response functions nor provide
   light-cone mock catalogs. However, future surveys should be able to test the

### 2013-10-02 paper1.tex
small clean-ups

@@
 fits are shown in blue and red for the NCCC and CCC population,
-respectively. {\bf As a cautionary remark, we emphasize that our model is only
-  valid within $R_{500}$ and more work would be needed to extrapolate it to
-  larger cluster radii. Those cluster regions are characterized by a steadily
-  increasing level of kinetic-to-thermal pressure support
-  \citep[e.g.,][]{2009ApJ...705.1129L, 2012ApJ...758...74B}, density clumping
-  \citep{2011ApJ...731L..10N, 2012arXiv1209.4082B}, and asphericity and
-  ellipticity of the halo morphologies \citep{2012arXiv1209.4082B}, in
-  particular beyond the virial radius where the filamentary cosmic web connects
-  to the cluster interiors.}
+respectively.
 
@@
 $E(z)^{2} = \Omega_{\rmn{m}} (1+z)^{3} + \Omega_{{\Lambda}}$.
+
+{\bf As a cautionary remark, we emphasize that our model is only valid within
+  $R_{500}$ and more work is needed to extrapolate it to larger cluster
+  radii. Those cluster regions are characterized by a steadily increasing level
+  of kinetic-to-thermal pressure support \citep[e.g.,][]{2009ApJ...705.1129L,
+    2012ApJ...758...74B}, density clumping \citep{2011ApJ...731L..10N,
+    2012arXiv1209.4082B}, and asphericity and ellipticity of the halo
+  morphologies \citep{2012arXiv1209.4082B}, in particular beyond the virial
+  radius where the filamentary cosmic web connects to the cluster interiors.}
 

### 2013-10-03 paper1.tex
last Fabio

@@
   X-ray observations have demonstrated that self-similarity is broken,
-  especially at low-mass scales (see e.g., \citealp{2005RvMP...77..207V} for a
+  especially at low-mass scales (see, e.g., \citealp{2005RvMP...77..207V} for a
   review). Apparently the energy input from non-gravitational processes
@@
   radiative cooling times of less than 1~Gyr and establish a population of cool
-  core clusters (CCC) while others have cooling times that can be longer than
+  core clusters (CCCs) while others have cooling times that can be longer than
   the age of the Universe, forming the non-cool core cluster (NCCC) population
@@
  0.16 & 11419\\
+ 0.18 &  11106\\
  0.2~~ &  10783\\ 
@@
 
-{\bf As a cautionary remark, we emphasize that our model is only valid within
-  $R_{500}$ and more work is needed to extrapolate it to larger cluster
-  radii. Those cluster regions are characterized by a steadily increasing level
+%{\bf As a cautionary remark, we emphasize that our model is only valid within
+%$R_{500}$ and more work is needed to extrapolate it to larger cluster
+%radii, \qc{particularly for the thermal modeling}.
+{\bf As a cautionary remark, \qc{we emphasize that our model is built
+to be valid within $R_{500}$ and more work is needed to extrapolate it to 
+larger cluster radii, particularly for the thermal modeling}.
+Those cluster regions are characterized by a steadily increasing level
 of kinetic-to-thermal pressure support \citep[e.g.,][]{2009ApJ...705.1129L,
@@
 \label{sec:5}
+
+\begin{figure*} 
+\centering
+\includegraphics[width=0.48\textwidth]{figures/sz_m.eps}
+\includegraphics[width=0.48\textwidth]{figures/sz_m_ACT.eps}
+\caption{{\bf Comparison of our SZ scaling relations (grey triangles) with
+    data. The black crosses represent
+    the $Y_{\rmn{SZ}}$ median values of our sample for a given mass bin
+    (indicated by horizontal error bars), and the vertical error bars represent
+    the standard deviation within a bin. 
+    The bottom panels show the relative difference to the observational
+    scaling relations.
+    \emph{Left.}  We compare our $Y_{\rmn{SZ}}-M$ relation at
+    $z=0.18$ with the {\em Planck} data \citep[blue,][]{2013arXiv1303.5080P},
+    which have a median redshift of about $0.18$. \emph{Right.} We compare our
+    $Y_{\rmn{SZ}}-M$ relation at $z=0.53$ with the ACT sample
+    \protect\citep[blue,][]{2013JCAP...07..008H} assuming a self-similar
+    redshift evolution.}}
+\label{fig:SZ_M}
+\end{figure*}
+
 In the left panel of Fig.~\ref{fig:SZ_M}, we compare the $Y_{\rmn{SZ}}-M_{500}$
@@
   \emph{Planck} COSMO sample, which is Malmquist-bias corrected and has a median
-  redshift of $0.18$, and compare this to our $z=0.2$ relation}. Our model
+  redshift of $0.18$, and compare this to our $z=0.18$ relation}. Our model
 reproduces the normalization of the scaling relation remarkably well, except for
@@
 
-\begin{figure*} 
-\centering
-\includegraphics[width=0.48\textwidth]{figures/sz_m.eps}
-\includegraphics[width=0.48\textwidth]{figures/sz_m_ACT.eps}
-\caption{{\bf Comparison of our SZ scaling relations (grey triangles) with
-    data. The bottom panels show the relative difference to the observational
-    scaling relations. \emph{Left.}  We compare our $Y_{\rmn{SZ}}-M$ relation at
-    $z=0.2$ with the {\em Planck} data \citep[blue,][]{2013arXiv1303.5080P},
-    which have a median redshift of about $0.18$.  The black crosses represent
-    the $Y_{\rmn{SZ}}$ median values of our sample for a given mass bin
-    (indicated by horizontal error bars), and the vertical error bars represent
-    the standard deviation within a bin. \emph{Right.} We compare our
-    $Y_{\rmn{SZ}}-M$ relation at $z=0.53$ with the ACT sample
-    \protect\citep[blue,][]{2013JCAP...07..008H} assuming a self-similar
-    redshift evolution.}}
-\label{fig:SZ_M}
-\end{figure*}
-
 \begin{table} 
@@
  0      & $-27.93\pm0.07$ & $1.60\pm0.01$ & 0.109\\
- 0.1   & $-27.74\pm0.07$ & $1.59\pm0.01$ & 0.109\\
- 0.18 & $-27.73\pm0.08$ & $1.59\pm0.01$ & 0.109\\
- 0.2   & $-27.65\pm0.08$ & $1.59\pm0.01$ & 0.109\\ 
- 0.4   & $-27.57\pm0.10$ & $1.59\pm0.01$ & 0.108\\ 
- 0.61 & $-27.50\pm0.13$ & $1.59\pm0.01$ & 0.109\\ 
- 0.78 & $-27.15\pm0.18$ & $1.58\pm0.01$ & 0.109\\ 
- 1      & $-27.01\pm0.26$ & $1.58\pm0.02$ & 0.109\\[0.5em] 
+ 0.1   & $-27.75\pm0.07$ & $1.59\pm0.01$ & 0.109\\
+ 0.18 & $-27.75\pm0.08$ & $1.59\pm0.01$ & 0.109\\
+ 0.2   & $-27.68\pm0.08$ & $1.59\pm0.01$ & 0.109\\ 
+ 0.4   & $-27.62\pm0.10$ & $1.59\pm0.01$ & 0.108\\
+ 0.53 & $-27.67\pm0.11$ & $1.59\pm0.01$ & 0.109\\
+ 0.61 & $-27.59\pm0.13$ & $1.59\pm0.01$ & 0.109\\ 
+ 0.78 & $-27.26\pm0.18$ & $1.58\pm0.01$ & 0.109\\ 
+ 1      & $-27.16\pm0.26$ & $1.58\pm0.02$ & 0.109\\[0.5em] 
 \hline
@@
 {\bf In the right panel of Fig.~\ref{fig:SZ_M}, we compare our scaling relation
-  to the ACT sample overlapping with the Sloan Digital Sky Survey stripe 82
-  \citep{2013JCAP...07..008H}, which has a median redshift of $z=0.53$. Again,
-  the slope of our modeled scaling relation is somewhat shallower in comparison
+  to the \qc{recent Atacama Cosmology Telescope (ACT) sample} \citep{2013JCAP...07..008H}, 
+  which has a median redshift of $z=0.53$. 
+  Again, the slope of our modeled scaling relation is somewhat shallower in comparison
   to the observed slope. Most strikingly, there appears to be a 30 per cent
@@
   post-processing that was employed by the ACT Collaboration to construct their
-  $Y_{500}$ estimates. However, this could also indicate that our presented
+  $Y_{500}$ estimates. This could also indicate that our presented
   model is too simplistic to capture the rich cluster physics and potentially
@@
   (since ACT sample probes on average higher redshift and less massive clusters
-  in comparison to the {\em Planck} sample). Overall, there is reasonable
+  in comparison to the {\em Planck} sample). 
+  \qc{However, note that our scaling relation at $z=0.53$ ($A=-27.67\pm0.11$, $B=1.59\pm0.01$) 
+  is perfectly compatible within the errors with the one derived from the ACT sample 
+  ($A=-28.59\pm2.26$, $B=1.65\pm0.15$).  
+  Therefore, we conclude that overall} there is reasonable
   agreement between our phenomenological model and the SZ data of the
@@
 
-  However, there are some notable deviations among the different observational
+%However, there are some notable deviations among the different observational
+  However, there are \qc{some deviations} among the different observational
   scaling relations and our model, which may either point to observational
@@
   the different cluster samples or may even signal a deviation from the assumed
-  self-similar redshift evolution.
+  self-similar redshift evolution. \qc{Nevertheless, we stress that our scaling relation
+  is still compatible within the errors of the ACT one.}
 
@@
 \end{document}
-
-\del{
-The study of the (non-)thermal emission in galaxy clusters provides
-important information on structure formation process and on 
-fundamental characteristics of our Universe. This field is at a 
-crucial point of its development thanks to the very low sensitivity of present and future-generation 
-instruments such as LOFAR\footnote{www.lofar.org}, \emph{e}ROSITA\footnote{www.mpe.mpg.de/eROSITA}, 
-ASTRO-H\footnote{astro-h.isas.jaxa.jp} and CTA\footnote{www.cta-observatory.org}, to name but a few. 
-Therefore, it is important to provide prospects for future surveys and
-to understand in which way they can improve our current knowledge.
-To this end, a complete cosmological mock sample of galaxy
-clusters is needed. This can be realized either using analytical 
-expressions for the cluster mass function (e.g., \citealp{2001MNRAS.321..372J}) or cosmological cluster 
-simulations. In this work, we make use of the recent MultiDark $N$-body
-simulation (\citealp{2011arXiv1104.5130P}; www.multidark.org).
-%
-Our main motivation to build such a mock catalog has been to predict the 
-non-thermal emission at radio frequencies of a cosmological 
-complete sample of galaxy clusters. This is presented in a companion 
-paper (\citealp{paper2}; hereafter Paper~II). As described in Paper~II, for 
-any given cluster, fundamental ingredients for the non-thermal emission 
-model are the mass and gas density distribution. The MultiDark 
-simulation used here is a $N$-body, \emph{dark matter (DM)-only} simulation and, 
-therefore, does not contain any information on the intra-cluster medium (ICM) gas  
-distribution. A cosmological complete sample of clusters can 
-only be obtained from $N$-body simulations as hydrodynamical
-simulations of such large volumes are computationally too expensive.
-Therefore, we need a method to determine the ICM properties
-of any given cluster from its total mass. 
-%
-ACT SZ:
-This sample has a median redshift of 0.58 with
-  rms of 0.28. \cite{2013JCAP...07..008H} provides $Y_{\rmn{SZ}}$ within
-  $R_{500}$, which median, $0.42$~h$_{70}^{-1}$~Mpc, is almost half of ours at
-  the MultiDark snapshot $z=0.61$. Therefore, we use an aperture of
-  $0.42$~h$_{70}^{-1}$~Mpc to calculate our $Y_{\rmn{SZ, ACT}}$.  The fact that
-  our $R_{500}$ does not compare well with the ACT values, while it does with
-  \emph{Planck}, may be explained as follows. We adopt the ACT measurements
-  derived from the 148~GHz data assuming that the cluster pressure is described
-  by the universal profile of \cite{2010A&A...517A..92A}. In contrast,
-  \cite{2013arXiv1303.5080P} derived $R_{500}$ from X-ray measurements of
-  $M_{500}$, similarly to our approach of constructing gas densities from an
-  X-ray sample of clusters.
-%
-Summarizing, our SZ scaling relations compare very well to the result from
-the \emph{Planck} collaboration. However, the comparison with the SPT and 
-ACT samples is not as straightforward due to the different selection function 
-of these telescopes with respect to \emph{Planck}, which results in a much
-more (redshift) non-homogeneous sample. Nevertheless, our mock clusters 
-can reproduce well the median SPT and ACT populations. A more detailed
-comparison would need the generation of light-cone mock catalogs,
-including instrumental effects, which is beyond the scope of this 
-work.}

### 2013-10-03 paper1.tex
text corrected and dereddened

@@
 
-%{\bf As a cautionary remark, we emphasize that our model is only valid within
-%$R_{500}$ and more work is needed to extrapolate it to larger cluster
-%radii, \qc{particularly for the thermal modeling}.
-{\bf As a cautionary remark, \qc{we emphasize that our model is built
-to be valid within $R_{500}$ and more work is needed to extrapolate it to 
-larger cluster radii, particularly for the thermal modeling}.
-Those cluster regions are characterized by a steadily increasing level
-of kinetic-to-thermal pressure support \citep[e.g.,][]{2009ApJ...705.1129L,
-2012ApJ...758...74B}, density clumping \citep{2011ApJ...731L..10N,
-2012arXiv1209.4082B}, and asphericity and ellipticity of the halo
-morphologies \citep{2012arXiv1209.4082B}, in particular beyond the virial
-radius where the filamentary cosmic web connects to the cluster interiors.}
+{\bf As a cautionary remark, we emphasize that our model has been constructed to
+  be valid within $R_{500}$ and more work is needed to extrapolate it to larger
+  cluster radii, particularly for the thermal cluster emission.  Those cluster
+  regions are characterized by a steadily increasing level of kinetic-to-thermal
+  pressure support \citep[e.g.,][]{2009ApJ...705.1129L, 2012ApJ...758...74B},
+  density clumping \citep{2011ApJ...731L..10N, 2012arXiv1209.4082B}, and
+  asphericity and ellipticity of the halo morphologies
+  \citep{2012arXiv1209.4082B}, in particular beyond the virial radius where the
+  filamentary cosmic web connects to the cluster interiors.}
 
@@
 {\bf In the right panel of Fig.~\ref{fig:SZ_M}, we compare our scaling relation
-  to the \qc{recent Atacama Cosmology Telescope (ACT) sample} \citep{2013JCAP...07..008H}, 
-  which has a median redshift of $z=0.53$. 
-  Again, the slope of our modeled scaling relation is somewhat shallower in comparison
+  to the recent Atacama Cosmology Telescope (ACT) sample
+  \citep{2013JCAP...07..008H}, which has a median redshift of $z=0.53$.  Again,
+  the slope of our modeled scaling relation is somewhat shallower in comparison
   to the observed slope. Most strikingly, there appears to be a 30 per cent
@@
   post-processing that was employed by the ACT Collaboration to construct their
-  $Y_{500}$ estimates. This could also indicate that our presented
-  model is too simplistic to capture the rich cluster physics and potentially
-  may even signal deviations from the assumed self-similar redshift evolution
-  (since ACT sample probes on average higher redshift and less massive clusters
-  in comparison to the {\em Planck} sample). 
-  \qc{However, note that our scaling relation at $z=0.53$ ($A=-27.67\pm0.11$, $B=1.59\pm0.01$) 
-  is perfectly compatible within the errors with the one derived from the ACT sample 
-  ($A=-28.59\pm2.26$, $B=1.65\pm0.15$).  
-  Therefore, we conclude that overall} there is reasonable
+  $Y_{500}$ estimates. This could also indicate that our presented model is too
+  simplistic to capture the rich cluster physics and potentially may even signal
+  deviations from the assumed self-similar redshift evolution (since the ACT
+  sample probes on average higher redshift and less massive clusters in
+  comparison to the {\em Planck} sample).  However, note that our scaling
+  relation at $z=0.53$ ($A=-27.67\pm0.11$, $B=1.59\pm0.01$) is within the
+  uncertainties compatible with that of the ACT sample ($A=-28.59\pm2.26$,
+  $B=1.65\pm0.15$).  Thus, we conclude that overall there is reasonable
   agreement between our phenomenological model and the SZ data of the
@@
 
-%However, there are some notable deviations among the different observational
-  However, there are \qc{some deviations} among the different observational
-  scaling relations and our model, which may either point to observational
-  sample selection effects that are not accounted for or missing complexity of
-  our model. This model was specifically constructed to provide a reliable
+  However, there are some deviations among the different observational scaling
+  relations and our model, which may either point to observational sample
+  selection effects that are not accounted for or missing complexity of our
+  model. This model was specifically constructed to provide a reliable
   description of the gas density, which necessarily implies a great match of the
@@
   normalization of the ACT $Y_{\rmn{SZ}}-M_{500}$ relation (at $z=0.53$) by
-  about 30 per cent. This could either indicate possible selection effects of
-  the different cluster samples or may even signal a deviation from the assumed
-  self-similar redshift evolution. \qc{Nevertheless, we stress that our scaling relation
-  is still compatible within the errors of the ACT one.}
+  about 30 per cent. While this offset is still consistent within the 1-$\sigma$
+  uncertainty intervals of the ACT scaling relation, this could also indicate
+  possible selection effects of the different cluster samples or alternatively
+  even signal a deviation from the assumed self-similar redshift evolution.
 

### 2013-10-05 paper1.tex
very last Fabio

@@
 \documentclass[useAMS,usenatbib]{mn2e}
-%
-%\def\del#1{{\bf  [deleted text] }} \def\new#1{{\bf #1}} \def\remark#1{{\bf  [remark: #1]}}
-%\def\del#1{} \def\new#1{#1} \def\remark#1{}
 
 \def\del#1{{}}
-%\def\del#1{{\bf (DELETED TEXT)}}
 \def\C#1{{\bf #1}}
-%\def\C#1{#1}
 
@@
  0.0~~ &  13763\\
- 0.05 &  13103\\
  0.1~~ &  12398\\
- 0.16 & 11419\\
  0.18 &  11106\\
  0.2~~ &  10783\\ 
- 0.27 & ~~9772\\
- 0.32 & ~~9039\\
- 0.37 & ~~8197\\
  0.4~~ &   ~~7789\\
- 0.47 & ~~6957\\
  0.53 & ~~6079\\ 
  0.61 &  ~~5187\\ 
- 0.69 & ~~4288\\
  0.78 &  ~~3372\\ 
- 0.89 & ~~2575\\
  1.0~~ &  ~~1803\\[0.5em]
@@
 \end{center}
-\footnotesize{Note. We show the number of halos in our MultiDark snapshots at redshift $z$ for $M_{200}\geq1\times10^{14}$~$h^{-1}$~M$_{\odot}\approx1.4\times10^{14}$~$h_{70}^{-1}$~M$_{\odot}$. }
+\footnotesize{Note.
+We show the number of halos in our MultiDark snapshots at redshift $z$ for $M_{200}\geq1\times10^{14}$~$h^{-1}$~M$_{\odot}\approx1.4\times10^{14}$~$h_{70}^{-1}$~M$_{\odot}$.
+{\bf More snapshots can be found online at www.mutlidark.org.}}
 \end{table}
@@
 \begin{eqnarray}
-%C_{i}  =  (0.0616\pm(0.0060g_{1}))  h_{73}^{-1.5}  \left(\frac{M_{500,i}}{10^{13} h_{73}^{-1} \rmn{M_{\odot}}}\right)^{0.135\pm(0.030g_{2})} \nonumber \\
 C_{i}  & = &  (0.0656\pm(0.0064g_{1})) \, h_{70}^{-1.5}  \nonumber \\
@@
 \includegraphics[width=0.48\textwidth]{figures/yx_m.eps}
-%\includegraphics[width=0.33\textwidth]{figures/sz_m.eps}
 \caption{{\bf X-ray scaling relations. Grey triangles show the MultiDark
@@
   observational sample by \protect\cite{2010MNRAS.406.1773M}.}} 
-  %\emph{Right.} $Y_{\rmn{SZ}}-M_{500}$ scaling relation at $z=0.2$ in comparison
-  %to the observational sample by the \protect\cite{2013arXiv1303.5080P} with a 
-  %median redshift of about $0.18$. The bottom panels show the relative difference to
-  %the observational scaling relations.}
 \label{fig:X_LM}
@@
  0.1   & $-21.30\pm0.12$ & $1.50\pm0.01$ & 0.179\\
+ 0.18   & $-21.49\pm0.13$ & $1.51\pm0.01$ & 0.177\\
  0.2   & $-21.50\pm0.13$ & $1.51\pm0.01$ & 0.178\\ 
  0.4   & $-21.13\pm0.17$ & $1.49\pm0.01$ & 0.178\\ 
- 0.61 & $-21.59\pm0.22$ & $1.53\pm0.01$ & 0.177\\ 
+ 0.53   & $-21.45\pm0.19$ & $1.52\pm0.01$ & 0.176\\
+ 0.61 & $-21.60\pm0.22$ & $1.53\pm0.01$ & 0.177\\ 
  0.78 & $-20.73\pm0.29$ & $1.48\pm0.02$ & 0.177\\ 
@@
 \hline\\[-0.5em]
- 0      & $-9.18\pm0.07$ & $1.61\pm0.01$ & 0.109\\
- 0.1   & $-8.85\pm0.07$ & $1.59\pm0.01$ & 0.109\\
- 0.2   & $-8.82\pm0.08$ & $1.59\pm0.01$ & 0.109\\ 
- 0.4   & $-8.79\pm0.10$ & $1.59\pm0.01$ & 0.108\\ 
- 0.61 & $-8.65\pm0.14$ & $1.59\pm0.01$ & 0.109\\ 
- 0.78 & $-8.36\pm0.18$ & $1.57\pm0.01$ & 0.109\\ 
- 1      & $-8.28\pm0.26$ & $1.57\pm0.02$ & 0.109\\[0.5em]  
+ 0      & $-9.09\pm0.07$ & $1.60\pm0.01$ & 0.109\\
+ 0.1   & $-8.90\pm0.07$ & $1.59\pm0.01$ & 0.109\\
+ 0.18   & $-8.90\pm0.08$ & $1.59\pm0.01$ & 0.109\\
+ 0.2   & $-8.83\pm0.08$ & $1.59\pm0.01$ & 0.109\\ 
+ 0.4   & $-8.78\pm0.10$ & $1.59\pm0.01$ & 0.108\\ 
+ 0.53   & $-8.82\pm0.12$ & $1.60\pm0.01$ & 0.108\\ 
+ 0.61 & $-8.74\pm0.14$ & $1.59\pm0.01$ & 0.109\\ 
+ 0.78 & $-8.40\pm0.18$ & $1.58\pm0.01$ & 0.109\\ 
+ 1      & $-8.30\pm0.26$ & $1.58\pm0.02$ & 0.109\\[0.5em]  
 \hline
@@
  0.4   & $-27.62\pm0.10$ & $1.59\pm0.01$ & 0.108\\
- 0.53 & $-27.67\pm0.11$ & $1.59\pm0.01$ & 0.109\\
+ 0.53 & $-27.67\pm0.12$ & $1.60\pm0.01$ & 0.109\\
  0.61 & $-27.59\pm0.13$ & $1.59\pm0.01$ & 0.109\\ 
  0.78 & $-27.26\pm0.18$ & $1.58\pm0.01$ & 0.109\\ 
- 1      & $-27.16\pm0.26$ & $1.58\pm0.02$ & 0.109\\[0.5em] 
+ 1      & $-27.17\pm0.26$ & $1.58\pm0.02$ & 0.109\\[0.5em] 
 \hline
@@
   comparison to the {\em Planck} sample).  However, note that our scaling
-  relation at $z=0.53$ ($A=-27.67\pm0.11$, $B=1.59\pm0.01$) is within the
+  relation at $z=0.53$ ($A=-27.67\pm0.12$, $B=1.60\pm0.01$) is within the
   uncertainties compatible with that of the ACT sample ($A=-28.59\pm2.26$,
@@
   off X-ray observables within $R_{500}$. More work would be needed to
-  extrapolate the model to larger cluster radii that are characterised by an
+  extrapolate the model to larger cluster radii that are characterized by an
   increased complexity, which manifests itself in a larger kinetic-to-thermal

### 2013-10-10 paper1.tex
last

@@
 \author[F. Zandanel, C. Pfrommer and F. Prada]{
-Fabio Zandanel$^{1,2}$, Christoph Pfrommer$^{3}$ and Francisco Prada$^{4,5,2}$\\
-$^{1}$GRAPPA Institute, University of Amsterdam, Science Park 904, 1098XH Amsterdam, Netherlands, f.zandanel@uva.nl\\
-$^{2}$Instituto de Astrof\'{\i}sica de Andaluc\'{\i}a (CSIC), Glorieta de la Astronom\'{\i}a, E-18080 Granada, Spain\\
+Fabio Zandanel$^{1,2}$, Christoph Pfrommer$^{3}$ and Francisco Prada$^{4,5,1}$\\
+$^{1}$Instituto de Astrof\'{\i}sica de Andaluc\'{\i}a (CSIC), Glorieta de la Astronom\'{\i}a, E-18080 Granada, Spain\\
+$^{2}$Now at GRAPPA Institute, University of Amsterdam, Science Park 904, 1098XH Amsterdam, Netherlands, f.zandanel@uva.nl\\
 $^{3}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany, christoph.pfrommer@h-its.org\\
@@
     construct a phenomenological model for the intracluster medium that is based
-    on a representative sample of X-ray clusters. We create a mock galaxy
-    cluster catalog by assigning our gas density model to each cluster halo of
-    the large collisionless $N$-body simulation MultiDark. Our clusters are
-    identified with cool-core and non cool-core clusters according to a
+    on a representative sample of \qc{observed} X-ray clusters. We create a mock galaxy
+    cluster catalog \qc{based on the large collisionless $N$-body simulation MultiDark, by 
+    assigning our gas density model to each dark matter cluster halo.}
+    %by assigning our gas density model to each cluster halo of
+    %the large collisionless $N$-body simulation MultiDark. 
+    Our clusters \qc{are classified as cool-core and non cool-core} according to a
     dynamical disturbance parameter. We demonstrate that our gas model matches
     the various observed Sunyaev-Zel'dovich and X-ray scaling relations as well
-    as the X-ray luminosity function, thus enabling a reliable mock catalog for
-    present surveys and forecasts for future instruments. In a companion paper,
+    as the X-ray luminosity function, thus enabling \qc{to build} a reliable mock catalog for
+    present surveys and forecasts for future \qc{experiments}. In a companion paper,
     we apply our catalogs to calculate non-thermal radio and gamma-ray emission
@@
   radiative cooling times of less than 1~Gyr and establish a population of cool
-  core clusters (CCCs) while others have cooling times that can be longer than
+  core clusters (CCCs)\qc{, while} others have cooling times that can be longer than
   the age of the Universe, forming the non-cool core cluster (NCCC) population
@@
   galactic nuclei (AGN) has come into the focus of recent research
-  \citep{2007ARA&A..45..117M, 2012NJPh...14e5023M} owing to the self-regulated
+  \citep{2007ARA&A..45..117M, 2012NJPh...14e5023M}\qc{, owing} to the self-regulated
   nature of the proposed feedback and observational correlations between radio
@@
     2012MNRAS.420.2662D, 2012MNRAS.424..190G, 2013MNRAS.428.2366V}. While the
-  comparison to data and simulations with AGN feedback improved for integrated
+  \qc{comparison between} data and simulations with AGN feedback improved for integrated
   thermal properties of large cluster samples
@@
   phenomenological model that matches all available X-ray and Sunyaev-Zel'dovich
-  (SZ) data with the goal to facilitate comparison of future hydrodynamical
+  (SZ) data with the goal to facilitate \qc{comparison with} future hydrodynamical
   simulations, to allow the modeling of non-thermal cluster emission over the
-  entire electromagnetic wave band, and finally to enable the construction of
+  entire electromagnetic \qc{wave-band}, and finally to enable the construction of
   cluster mock catalogs of the thermal and non-thermal cluster emission (in the
@@
   can either be obtained by means of analytical expressions for the cluster mass
-  function (e.g., \citealp{2001MNRAS.321..372J}) or cosmological cluster
-  simulations. In this work, we make use of the recent collisionless $N$-body
-  simulation MultiDark, which employs a $\Lambda$ cold dark matter cosmology
-  (\citealp{2011arXiv1104.5130P}; www.multidark.org).
+  function (e.g., \citealp{2001MNRAS.321..372J}) or cosmological
+  simulations. In this work, we make use of the recent \qc{large-volume} $N$-body
+  simulation MultiDark, which employs a \qc{flat $\Lambda$ Cold Dark Matter} cosmology
+  \citep{2011arXiv1104.5130P}.
 
   Our \emph{phenomenological} approach uses gas density profiles of a
-  representative sample of X-ray clusters, which are complemented by observed
-  cluster mass-dependent gas mass fractions. The resulting cluster mock sample
+  representative sample of \qc{observed} X-ray clusters, which are complemented by 
+  \qc{the observed} cluster mass-dependent gas mass fractions. The resulting cluster mock sample
   are then compared to data including the X-ray luminosity function (XLF), the
@@
   paper (\citealp{paper2}; hereafter Paper~II), we apply our ICM model to
-  predict the non-thermal radio halo emission of a cosmological complete sample of
-  galaxy clusters, enabling valuable insight into the statistics of radio halos.
+  predict the non-thermal \qc{radio and gamma-ray} emission of a cosmological complete 
+  sample of galaxy clusters, enabling valuable insight into the statistics of radio halos.
   One of our final data products is a complete cosmological cluster mock catalog,
-  at different redshifts, containing information of DM and ICM properties for
+  at different redshifts, containing information of \qc{the} DM and ICM properties for
   each object, together with its (non-)thermal emission at different
-  frequencies.
+  frequencies. \qc{All the products can be found on-line at the MultiDark 
+  database (\textit{www.multidark.org}).}
 
   In Section~\ref{sec:2}, we introduce the MultiDark simulation along with our
-  final cluster halo sample. We assign to each of our clusters the
+  \qc{selected} cluster halo sample. We assign to each of our clusters the
   phenomenologically constructed gas density profile in Section~\ref{sec:3}. In
@@
 
-We use the MultiDark halo catalog from its on-line database,\footnote{www.multidark.org} 
+We use the MultiDark halo catalog from its on-line database,\footnote{\textit{www.multidark.org}} 
 constructed with the Bound Density Maxima (BDM) algorithm \citep{1997astro.ph.12217K}.  
@@
 {\bf In Paper~II, we present predictions for the LOFAR radio observatory
-which is expected to detect diffuse radio emission in clusters up to redshift $z \approx 1$ (e.g.,
+which \qc{expects} to detect diffuse radio emission in clusters up to redshift $z \approx 1$ (e.g.,
 \citealp{2012JApA..tmp...34R}).} Thus, we make use of different simulation snapshots up to $z=1$. 
@@
 \includegraphics[width=0.48\textwidth]{figures/yx_m.eps}
-\caption{{\bf X-ray scaling relations. Grey triangles show the MultiDark
+\caption{{\bf X-ray \qc{cluster} scaling relations. Grey triangles show the MultiDark
   sample (limited to the mass range covered by observations), the black line is
   the corresponding scaling relation, and the blue line is the
-  observational result. The black crosses represent the median values of the
+  observational result by \protect\cite{2010MNRAS.406.1773M}. 
+  The black crosses represent the median values of the
   quantity in question for a given mass bin (indicated by horizontal error
   bars), and the vertical error bars represent the standard deviation within a
-  bin.  \emph{Left.} We compare the bolometric X-ray luminosity-to-mass
+  bin. The bottom panels show the relative difference to the observational
+    scaling relations. \emph{Left.} We compare the bolometric X-ray luminosity-to-mass
   relation, $L_{\rmn{bol}}-M_{500}$, at $z=0.2$ to the observational sample by
@@
 {\bf So far, we used a well-observed representative sample of X-ray clusters
-(REXCESS) that was supplemented by X-ray data on gas mass fractions to construct
+(REXCESS) that was supplemented \qc{with} X-ray data on gas mass fractions to construct
 our phenomenological gas model.  Here, we will test how our cluster mock data
@@
 \includegraphics[width=0.48\textwidth]{figures/sz_m_ACT.eps}
-\caption{{\bf Comparison of our SZ scaling relations (grey triangles) with
+\caption{{\bf Comparison of our \qc{MultiDark} SZ scaling relations (grey triangles) with
     data. The black crosses represent
@@
 the smaller box size in comparison to the survey volume of {\em Planck}.  {\bf
-  However, the slope of our $Y_{\rmn{SZ}}-M_{500}$ relation ($1.59\pm0.01$) is
+  However, the slope of \qc{the MultiDark} $Y_{\rmn{SZ}}-M_{500}$ relation ($1.59\pm0.01$) is
   shallower in comparison to the self-similar slope ($5/3$) as well as the
@@
   $f_{\rmn{gas}}\propto M_{500}^{0.135}$. To improve upon this, we would have to
-  account for a slightly steeper temperature-mass scaling (e.g., using a
+  account for a slightly steeper temperature-mass scaling \qc{relation} (e.g., using a
   centrally excised temperature scaling, see \citealt{2010MNRAS.406.1773M}) in
@@
   \citep{2013JCAP...07..008H}, which has a median redshift of $z=0.53$.  Again,
-  the slope of our modeled scaling relation is somewhat shallower in comparison
+  the slope of our modeled scaling relation is \qc{slightly} shallower in comparison
   to the observed slope. Most strikingly, there appears to be a 30 per cent
@@
   post-processing that was employed by the ACT Collaboration to construct their
-  $Y_{500}$ estimates. This could also indicate that our presented model is too
-  simplistic to capture the rich cluster physics and potentially may even signal
+  $Y_{500}$ estimates. This could also indicate that our model is too
+  simplistic to capture the rich cluster physics and potentially may even \qc{point to}
   deviations from the assumed self-similar redshift evolution (since the ACT
@@
   \approx1.4\times10^{14}$~$h_{70}^{-1}$~M$_{\odot}$.  We make these catalogs
-  publicly available through the MultiDark database (www.multidark.org) where we
+  publicly available through the MultiDark database \qc{(\textit{www.multidark.org})} where we
   will also post possible updates.
@@
   Our catalogs contain all the information regarding the DM properties of each
-  object as given by the corresponding original MultiDark BDM halo
+  \qc{cluster} as given by the corresponding original MultiDark BDM halo
   catalogs. Additionally, we include the following information:
@@
 \item the ICM X-ray temperature assigned via the $T_{\rmn{ci}}-M_{500}$ relation by \cite{2010MNRAS.406.1773M},
-\item a state flag identifying the cluster as NCCC or CCC as described in Section~\ref{sec:3},
+\item a flag identifying the cluster as NCCC or CCC, as described in Section~\ref{sec:3},
 \item the central gas density $\rho_{\rmn{gas},0}$ with which the full ICM radial profile can be calculated as in Section~\ref{sec:3},
@@
 
-In Paper~II, we present a model to calculate the possible radio and gamma-ray
-emission of clusters as result of the cosmic-ray (CR) proton-proton interactions
+In Paper~II, we present a model \qc{that allow us to compute the possible radio 
+and gamma-ray emission for each cluster in our mock catalog},
+%to calculate the possible radio and gamma-ray emission of clusters 
+as result of the cosmic-ray (CR) proton-proton interactions
 with the ICM. We refer to that paper for all the details. However, we want to
@@
 \begin{itemize}
-\item a state flag identifying whether a given object is a radio-loud or a radio-quiet cluster, 
+\item a flag identifying whether a given object is a radio-loud or a radio-quiet cluster, 
 \item the CR-to-thermal pressure averaged over the cluster volume within $R_{500}$,
@@
 We note that our mock catalogs are not appropriate for all purposes because the
-density profile shapes that we adopt in our model represent the average cluster
+density \qc{profiles} that we adopt in our model represent the average cluster
 population of cool-core and non cool-core systems (while we account for scatter
 in the gas mass fractions, i.e., the normalization of the profiles). As such,
-the models are very useful as a baseline for comparisons to new hydrodynamical
-simulations and to new observational samples as well as for non-thermal modeling
-of clusters. On the contrary, they are not appropriate to perform detailed
+\qc{our mocks} are very useful as a baseline for comparisons to new hydrodynamical
+simulations and to new observational samples\qc{, as} well as for non-thermal modeling
+of clusters. On the contrary, \qc{in the current form they are not} appropriate to perform detailed
 cosmology studies. Careful modeling of the response function of the considered
-instrument in combination with light-cone mock catalogs would be required in
-this case. Nevertheless, for volume-complete surveys, our mock catalogs will
-certainly serve as valuable tools.  }
+instrument, in combination with light-cone mock catalogs, would be required in
+this case. Nevertheless, for \qc{volume-limited cluster samples, our mock catalogs 
+will certainly serve as valuable tools. }
+%volume-complete surveys, our mock catalogs will certainly serve as valuable tools.  }
 
@@
   and a cluster mass-dependent gas fraction. Note that our model is calibrated
-  off X-ray observables within $R_{500}$. More work would be needed to
+  \qc{with} X-ray observables within $R_{500}$. More work would be needed to
   extrapolate the model to larger cluster radii that are characterized by an
@@
   that is calculated from the DM distribution. Applying the model to our sample
-  of cluster halos, we obtain volume-complete mock catalogs for the thermal (SZ
+  of cluster halos, we obtain \qc{volume-limited} mock catalogs for the thermal (SZ
   and X-ray) cluster emission. Our mock catalogs match the observed X-ray
@@
   resulting mock X-ray observables to data (scaling relations and luminosity
-  functions) as well as to the low-redshift and massive cluster sample probed by
-  {\em Planck}. However, we note that our model has a somewhat shallower slope
+  functions)\qc{, as well as} to the low-redshift and massive cluster sample probed by
+  {\em Planck}. However, we note that our model has a \qc{slightly} shallower slope
   of the $Y_{\rmn{SZ}}-M_{500}$ relation, which implies that the X-ray inferred
@@
   possible selection effects of the different cluster samples or alternatively
-  even signal a deviation from the assumed self-similar redshift evolution.
+  \qc{points to} a deviation from the assumed self-similar redshift evolution.
 
@@
   catalogs publicly and freely available on-line through the MultiDark database
-  (www.multidark.org). Our mock catalogs are based on density profile shapes
+  (\textit{www.multidark.org}). Our mock catalogs are based on density \qc{profiles}
   that represent the {\em average} cluster population of cool-core and non
@@
 thank the support of the Spanish MICINN's Consolider-Ingenio 2010 Programme
-under grant MultiDark CSD2009-00064. C.P.{\ }gratefully acknowledges financial
+under grant MultiDark CSD2009-00064, AYA10-21231. C.P.{\ }gratefully acknowledges financial
 support of the Klaus Tschira Foundation. The MultiDark Database used in this
@@
 of a collaboration between the Leibniz-Institute for Astrophysics Potsdam (AIP)
-and the Spanish MultiDark Consolider Project CSD2009-00064. The Bolshoi and
-MultiDark simulations were run on the NASA's Pleiades supercomputer at the NASA
-Ames Research Center.
+and the Spanish MultiDark Consolider Project CSD2009-00064, AYA10-21231. 
+The Bolshoi and MultiDark simulations were run on the NASA's Pleiades supercomputer 
+at the NASA Ames Research Center.
 

### 2013-10-11 paper1.tex
dereddened text

@@
     construct a phenomenological model for the intracluster medium that is based
-    on a representative sample of \qc{observed} X-ray clusters. We create a mock galaxy
-    cluster catalog \qc{based on the large collisionless $N$-body simulation MultiDark, by 
-    assigning our gas density model to each dark matter cluster halo.}
-    %by assigning our gas density model to each cluster halo of
-    %the large collisionless $N$-body simulation MultiDark. 
-    Our clusters \qc{are classified as cool-core and non cool-core} according to a
-    dynamical disturbance parameter. We demonstrate that our gas model matches
-    the various observed Sunyaev-Zel'dovich and X-ray scaling relations as well
-    as the X-ray luminosity function, thus enabling \qc{to build} a reliable mock catalog for
-    present surveys and forecasts for future \qc{experiments}. In a companion paper,
-    we apply our catalogs to calculate non-thermal radio and gamma-ray emission
-    of galaxy clusters. We make our cosmologically complete multi-frequency mock
-    catalogs for the (non-)thermal cluster emission at different redshifts
-    publicly and freely available online through the MultiDark database.}
+    on a representative sample of observed X-ray clusters. We create a mock
+    galaxy cluster catalog based on the large collisionless $N$-body simulation
+    MultiDark, by assigning our gas density model to each dark matter cluster
+    halo.  Our clusters are classified as cool-core and non cool-core according
+    to a dynamical disturbance parameter. We demonstrate that our gas model
+    matches the various observed Sunyaev-Zel'dovich and X-ray scaling relations
+    as well as the X-ray luminosity function, thus enabling to build a reliable
+    mock catalog for present surveys and forecasts for future experiments. In a
+    companion paper, we apply our catalogs to calculate non-thermal radio and
+    gamma-ray emission of galaxy clusters. We make our cosmologically complete
+    multi-frequency mock catalogs for the (non-)thermal cluster emission at
+    different redshifts publicly and freely available online through the
+    MultiDark database.}
 \end{abstract}
@@
   radiative cooling times of less than 1~Gyr and establish a population of cool
-  core clusters (CCCs)\qc{, while} others have cooling times that can be longer than
+  core clusters (CCCs), while others have cooling times that can be longer than
   the age of the Universe, forming the non-cool core cluster (NCCC) population
@@
   galactic nuclei (AGN) has come into the focus of recent research
-  \citep{2007ARA&A..45..117M, 2012NJPh...14e5023M}\qc{, owing} to the self-regulated
+  \citep{2007ARA&A..45..117M, 2012NJPh...14e5023M}, owing to the self-regulated
   nature of the proposed feedback and observational correlations between radio
@@
     2012MNRAS.420.2662D, 2012MNRAS.424..190G, 2013MNRAS.428.2366V}. While the
-  \qc{comparison between} data and simulations with AGN feedback improved for integrated
+  comparison between data and simulations with AGN feedback improved for integrated
   thermal properties of large cluster samples
@@
   phenomenological model that matches all available X-ray and Sunyaev-Zel'dovich
-  (SZ) data with the goal to facilitate \qc{comparison with} future hydrodynamical
+  (SZ) data with the goal to facilitate comparison with future hydrodynamical
   simulations, to allow the modeling of non-thermal cluster emission over the
-  entire electromagnetic \qc{wave-band}, and finally to enable the construction of
+  entire electromagnetic wave-band, and finally to enable the construction of
   cluster mock catalogs of the thermal and non-thermal cluster emission (in the
@@
   function (e.g., \citealp{2001MNRAS.321..372J}) or cosmological
-  simulations. In this work, we make use of the recent \qc{large-volume} $N$-body
-  simulation MultiDark, which employs a \qc{flat $\Lambda$ Cold Dark Matter} cosmology
+  simulations. In this work, we make use of the recent large-volume $N$-body
+  simulation MultiDark, which employs a flat $\Lambda$ Cold Dark Matter cosmology
   \citep{2011arXiv1104.5130P}.
@@
   Our \emph{phenomenological} approach uses gas density profiles of a
-  representative sample of \qc{observed} X-ray clusters, which are complemented by 
-  \qc{the observed} cluster mass-dependent gas mass fractions. The resulting cluster mock sample
-  are then compared to data including the X-ray luminosity function (XLF), the
-  luminosity-mass relation, $L_{\rmn{X}}- M$, and the $Y_{\rmn{X}}-M$ relation,
-  where $Y_{\rmn{X}}=M_\rmn{gas}k_{\rmn{B}}T$ with an X-ray-derived gas mass
-  $M_{\rmn{gas}}$ and temperature $T$ \citep{2006ApJ...650..128K}. We
+  representative sample of observed X-ray clusters, which are complemented by
+  the observed cluster mass-dependent gas mass fractions. The resulting cluster
+  mock sample are then compared to data including the X-ray luminosity function
+  (XLF), the luminosity-mass relation, $L_{\rmn{X}}- M$, and the $Y_{\rmn{X}}-M$
+  relation, where $Y_{\rmn{X}}=M_\rmn{gas}k_{\rmn{B}}T$ with an X-ray-derived
+  gas mass $M_{\rmn{gas}}$ and temperature $T$ \citep{2006ApJ...650..128K}. We
   additionally compare our $Y_{\rmn{SZ}}-M$ relation to recent SZ data, where
@@
   paper (\citealp{paper2}; hereafter Paper~II), we apply our ICM model to
-  predict the non-thermal \qc{radio and gamma-ray} emission of a cosmological complete 
-  sample of galaxy clusters, enabling valuable insight into the statistics of radio halos.
-  One of our final data products is a complete cosmological cluster mock catalog,
-  at different redshifts, containing information of \qc{the} DM and ICM properties for
-  each object, together with its (non-)thermal emission at different
-  frequencies. \qc{All the products can be found on-line at the MultiDark 
-  database (\textit{www.multidark.org}).}
+  predict the non-thermal radio and gamma-ray emission of a cosmological
+  complete sample of galaxy clusters, enabling valuable insight into the
+  statistics of radio halos.  One of our final data products is a complete
+  cosmological cluster mock catalog, at different redshifts, containing
+  information of the DM and ICM properties for each object, together with
+  its (non-)thermal emission at different frequencies. All the products can
+    be found on-line at the MultiDark database (\textit{www.multidark.org}).
 
     In Section~\ref{sec:2}, we introduce the MultiDark simulation along with our
-  \qc{selected} cluster halo sample. We assign to each of our clusters the
-  phenomenologically constructed gas density profile in Section~\ref{sec:3}. In
-  Sections~\ref{sec:4} and \ref{sec:5}, we show that this approach can
-  successfully reproduce the observed X-ray and SZ cluster data. We present the
-  resulting mock cluster catalogs in Section~\ref{sec:6}, and eventually
-  summarize in Section~\ref{sec:7}.  In this work, the cluster mass $M_{\Delta}$
-  and radius $R_{\Delta}$ are defined with respect to a density that is
-  $\Delta=200$ or 500 times the \emph{critical} density of the Universe. We
-  adopt density parameters of $\Omega_{\rmn{m}}=0.27$, $\Omega_{\Lambda}=0.73$ and
-  today's Hubble constant of $H_0 = 100\, h_{70}$~km~s$^{-1}$~Mpc$^{-1}$ where
-  $h_{70} = 0.7$.}
+    selected cluster halo sample. We assign to each of our clusters the
+    phenomenologically constructed gas density profile in
+    Section~\ref{sec:3}. In Sections~\ref{sec:4} and \ref{sec:5}, we show that
+    this approach can successfully reproduce the observed X-ray and SZ cluster
+    data. We present the resulting mock cluster catalogs in Section~\ref{sec:6},
+    and eventually summarize in Section~\ref{sec:7}.  In this work, the cluster
+    mass $M_{\Delta}$ and radius $R_{\Delta}$ are defined with respect to a
+    density that is $\Delta=200$ or 500 times the \emph{critical} density of the
+    Universe. We adopt density parameters of $\Omega_{\rmn{m}}=0.27$,
+    $\Omega_{\Lambda}=0.73$ and today's Hubble constant of $H_0 = 100\,
+    h_{70}$~km~s$^{-1}$~Mpc$^{-1}$ where $h_{70} = 0.7$.}
 
@@
 
-{\bf In Paper~II, we present predictions for the LOFAR radio observatory
-which \qc{expects} to detect diffuse radio emission in clusters up to redshift $z \approx 1$ (e.g.,
-\citealp{2012JApA..tmp...34R}).} Thus, we make use of different simulation snapshots up to $z=1$. 
-{\bf The extrapolation of our model beyond this redshift is rather uncertain as it is based
-on observations at low(er) redshift.} In Table~\ref{tab:z}, we show the total cluster number in 
-our final cluster sample at different redshifts.
+{\bf In Paper~II, we present predictions for the LOFAR radio observatory which
+  expects to detect diffuse radio emission in clusters up to redshift $z \approx
+  1$ (e.g., \citealp{2012JApA..tmp...34R}).} Thus, we make use of different
+simulation snapshots up to $z=1$.  {\bf The extrapolation of our model beyond
+  this redshift is rather uncertain as it is based on observations at low(er)
+  redshift.} In Table~\ref{tab:z}, we show the total cluster number in our final
+cluster sample at different redshifts.
 
@@
 \includegraphics[width=0.48\textwidth]{figures/yx_m.eps}
-\caption{{\bf X-ray \qc{cluster} scaling relations. Grey triangles show the MultiDark
+\caption{{\bf X-ray cluster scaling relations. Grey triangles show the MultiDark
   sample (limited to the mass range covered by observations), the black line is
@@
 {\bf So far, we used a well-observed representative sample of X-ray clusters
-(REXCESS) that was supplemented \qc{with} X-ray data on gas mass fractions to construct
+(REXCESS) that was supplemented with X-ray data on gas mass fractions to construct
 our phenomenological gas model.  Here, we will test how our cluster mock data
@@
 \includegraphics[width=0.48\textwidth]{figures/sz_m_ACT.eps}
-\caption{{\bf Comparison of our \qc{MultiDark} SZ scaling relations (grey triangles) with
-    data. The black crosses represent
-    the $Y_{\rmn{SZ}}$ median values of our sample for a given mass bin
-    (indicated by horizontal error bars), and the vertical error bars represent
-    the standard deviation within a bin. 
-    The bottom panels show the relative difference to the observational
-    scaling relations.
-    \emph{Left.}  We compare our $Y_{\rmn{SZ}}-M$ relation at
+\caption{{\bf Comparison of our MultiDark SZ scaling relations (grey triangles)
+    with data. The black crosses represent the $Y_{\rmn{SZ}}$ median values of
+    our sample for a given mass bin (indicated by horizontal error bars), and
+    the vertical error bars represent the standard deviation within a bin.  The
+    bottom panels show the relative difference to the observational scaling
+    relations.  \emph{Left.}  We compare our $Y_{\rmn{SZ}}-M$ relation at
     $z=0.18$ with the {\em Planck} data \citep[blue,][]{2013arXiv1303.5080P},
@@
 the smaller box size in comparison to the survey volume of {\em Planck}.  {\bf
-  However, the slope of \qc{the MultiDark} $Y_{\rmn{SZ}}-M_{500}$ relation ($1.59\pm0.01$) is
+  However, the slope of the MultiDark $Y_{\rmn{SZ}}-M_{500}$ relation ($1.59\pm0.01$) is
   shallower in comparison to the self-similar slope ($5/3$) as well as the
@@
   $f_{\rmn{gas}}\propto M_{500}^{0.135}$. To improve upon this, we would have to
-  account for a slightly steeper temperature-mass scaling \qc{relation} (e.g., using a
+  account for a slightly steeper temperature-mass scaling relation (e.g., using a
   centrally excised temperature scaling, see \citealt{2010MNRAS.406.1773M}) in
@@
   \citep{2013JCAP...07..008H}, which has a median redshift of $z=0.53$.  Again,
-  the slope of our modeled scaling relation is \qc{slightly} shallower in comparison
+  the slope of our modeled scaling relation is slightly shallower in comparison
   to the observed slope. Most strikingly, there appears to be a 30 per cent
@@
   post-processing that was employed by the ACT Collaboration to construct their
-  $Y_{500}$ estimates. This could also indicate that our model is too
-  simplistic to capture the rich cluster physics and potentially may even \qc{point to}
+  $Y_{500}$ estimates. This could also indicate that our model is too simplistic
+  to capture the rich cluster physics and potentially may even point to
   deviations from the assumed self-similar redshift evolution (since the ACT
@@
   \approx1.4\times10^{14}$~$h_{70}^{-1}$~M$_{\odot}$.  We make these catalogs
-  publicly available through the MultiDark database \qc{(\textit{www.multidark.org})} where we
-  will also post possible updates.
+  publicly available through the MultiDark database (\textit{www.multidark.org})
+  where we will also post possible updates.
 
   Our catalogs contain all the information regarding the DM properties of each
-  \qc{cluster} as given by the corresponding original MultiDark BDM halo
+  cluster as given by the corresponding original MultiDark BDM halo
   catalogs. Additionally, we include the following information:
@@
 
-In Paper~II, we present a model \qc{that allow us to compute the possible radio 
-and gamma-ray emission for each cluster in our mock catalog},
-%to calculate the possible radio and gamma-ray emission of clusters 
-as result of the cosmic-ray (CR) proton-proton interactions
-with the ICM. We refer to that paper for all the details. However, we want to
-point out that our mock catalogs also include:
+In Paper~II, we present a model that allows us to compute the possible radio and
+gamma-ray emission for each cluster in our mock catalog, as result of the
+cosmic-ray (CR) proton-proton interactions with the ICM. We refer to that paper
+for all the details. However, we want to point out that our mock catalogs also
+include:
 
@@
 We note that our mock catalogs are not appropriate for all purposes because the
-density \qc{profiles} that we adopt in our model represent the average cluster
+density profiles that we adopt in our model represent the average cluster
 population of cool-core and non cool-core systems (while we account for scatter
 in the gas mass fractions, i.e., the normalization of the profiles). As such,
-\qc{our mocks} are very useful as a baseline for comparisons to new hydrodynamical
-simulations and to new observational samples\qc{, as} well as for non-thermal modeling
-of clusters. On the contrary, \qc{in the current form they are not} appropriate to perform detailed
-cosmology studies. Careful modeling of the response function of the considered
-instrument, in combination with light-cone mock catalogs, would be required in
-this case. Nevertheless, for \qc{volume-limited cluster samples, our mock catalogs 
-will certainly serve as valuable tools. }
-%volume-complete surveys, our mock catalogs will certainly serve as valuable tools.  }
+our mocks are very useful as a baseline for comparisons to new hydrodynamical
+simulations and to new observational samples, as well as for non-thermal
+modeling of clusters. On the contrary, in the current form they are not
+appropriate to perform detailed cosmology studies. Careful modeling of the
+response function of the considered instrument, in combination with light-cone
+mock catalogs, would be required in this case. Nevertheless, for volume-limited
+cluster samples, our mock catalogs will certainly serve as valuable tools. }
 
@@
   and a cluster mass-dependent gas fraction. Note that our model is calibrated
-  \qc{with} X-ray observables within $R_{500}$. More work would be needed to
+  with X-ray observables within $R_{500}$. More work would be needed to
   extrapolate the model to larger cluster radii that are characterized by an
@@
   that is calculated from the DM distribution. Applying the model to our sample
-  of cluster halos, we obtain \qc{volume-limited} mock catalogs for the thermal (SZ
+  of cluster halos, we obtain volume-limited mock catalogs for the thermal (SZ
   and X-ray) cluster emission. Our mock catalogs match the observed X-ray
@@
   resulting mock X-ray observables to data (scaling relations and luminosity
-  functions)\qc{, as well as} to the low-redshift and massive cluster sample probed by
-  {\em Planck}. However, we note that our model has a \qc{slightly} shallower slope
+  functions), as well as to the low-redshift and massive cluster sample probed by
+  {\em Planck}. However, we note that our model has a slightly shallower slope
   of the $Y_{\rmn{SZ}}-M_{500}$ relation, which implies that the X-ray inferred
@@
   possible selection effects of the different cluster samples or alternatively
-  \qc{points to} a deviation from the assumed self-similar redshift evolution.
+  points to a deviation from the assumed self-similar redshift evolution.
 
@@
   catalogs publicly and freely available on-line through the MultiDark database
-  (\textit{www.multidark.org}). Our mock catalogs are based on density \qc{profiles}
+  (\textit{www.multidark.org}). Our mock catalogs are based on density profiles
   that represent the {\em average} cluster population of cool-core and non

### 2013-10-11 paper1.tex
tosubmit

@@
   relation at $z=0.53$ ($A=-27.67\pm0.12$, $B=1.60\pm0.01$) is within the
-  uncertainties compatible with that of the ACT sample ($A=-28.59\pm2.26$,
+  uncertainties compatible with that of the ACT sample ($A=-28.57\pm2.25$,
   $B=1.65\pm0.15$).  Thus, we conclude that overall there is reasonable
